### 2021-02-25 Manuscript/manuscript.tex
PUB

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Arsclassica Article
% LaTeX Template
% Version 1.1 (1/8/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Lorenzo Pantieri (http://www.lorenzopantieri.net) with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}

\input{structure.tex} % Include the structure.tex file which specified the document structure and layout

\hyphenation{Fortran hy-phen-ation} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR(S)
%----------------------------------------------------------------------------------------

\title{\normalfont\spacedallcaps{The economic consequences of the different attitudes of a policy maker: a combined epidemiological-econometric study}} % The article title

%\subtitle{Subtitle} % Uncomment to display a subtitle

\author{\spacedlowsmallcaps{Marzio De Corato and Giulia Hadjiandrea}} % The article author(s) - author affiliations need to be specified in the AUTHOR AFFILIATIONS block

\date{} % An optional date to appear under the author(s)

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADERS
%----------------------------------------------------------------------------------------

\renewcommand{\sectionmark}[1]{\markright{\spacedlowsmallcaps{#1}}} % The header for all pages (oneside) or for even pages (twoside)
%\renewcommand{\subsectionmark}[1]{\markright{\thesubsection~#1}} % Uncomment when using the twoside option - this modifies the header on odd pages
\lehead{\mbox{\llap{\small\thepage\kern1em\color{halfgray} \vline}\color{halfgray}\hspace{0.5em}\rightmark\hfil}} % The header style

\pagestyle{scrheadings} % Enable the headers specified in this block

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS & LISTS OF FIGURES AND TABLES
%----------------------------------------------------------------------------------------

\maketitle % Print the title/author/date block

%\setcounter{tocdepth}{2} % Set the depth of the table of contents to show sections and subsections only

%\tableofcontents % Print the table of contents

%\listoffigures % Print the list of figures%

%\listoftables % Print the list of tables

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\section*{Abstract} % This section will not appear in the table of contents due to the star (\section*)

Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Removed), we considered a policy-maker (PM) that impose stochastically three types of lock-down with increasing force. The probability by which the PM apply the lock-down reflects the different attitudes of a PM to face an epidemics (e.g. \textit{laissez-faire } vs very strict): thus depending on this probabilistic-parameter different scenario were simulated. For each of them we predicted a selected set of economic impacts by using parameters estimated via econometric techniques (Difference-in -Difference) on the microeconomic data of Italy. The comparison of the different impacts provide a bird's-eye view on the socio-economic consequences of the PM attitude

\newpage % Start the article content on the second page, remove this if you have a longer abstract that goes onto the second page

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{Introduction}

\section{Methods}

\section{Results and Discussion}

\cite{Figueredo:2009dg}

\bibliographystyle{unsrt}

\bibliography{sample.bib} % The file containing the bibliography

%----------------------------------------------------------------------------------------

\end{document}

### 2021-02-25 Project_script_Stochastic.R

@@ -19,6 +19,7 @@ pop_tot<-60000000
 delta_inf<-0
 #k<-c(1.5,1.5,1.5)
 k<-c(1,1,1)
+#k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.000001
 rate_infection_threshold<-0.000007
 score<-0

### 2021-02-25 Project_script_Stochastic.R
PUB

@@ -66,7 +66,7 @@ closed.sir.model <- function (t, x, params) {
   #  L <- ifelse(I=> 10000, 0.5, 1)
 
 }
-parms <- c(beta=0.5,gamma=0.14,delta=0.01)
+parms <- c(beta=0.55,gamma=0.14,delta=0.01)
 xstart <- c(S=pop_tot
             ,I=1,R=0,D=0)
 
@@ -104,7 +104,7 @@ xstart <- c(S=out$S[8],I=out$I[8],R=out$R[8],D=out$D[8])
 
 if(buffer[(i+1)*7,]$I/pop_tot > rate_infection_threshold && p_vector[i+1] >= 0.5*k[1]) {
   
-  parms <- c(beta=0.5*0.7,gamma=0.14,delta=0.01)
+  parms <- c(beta=0.55*0.7,gamma=0.14,delta=0.01)
   #  print(buffer[(i+1)*7,]$time) 
   #  print(buffer[(i+1)*7,]$I)
 #  print("-LOW")
@@ -112,7 +112,7 @@ if(buffer[(i+1)*7,]$I/pop_tot > rate_infection_threshold && p_vector[i+1] >= 0.5
 
 if(buffer[(i+1)*7,]$I/pop_tot > rate_infection_threshold*10 & p_vector[i+1] >= 0.5*k[2]) {
   
-  parms <- c(beta=0.5*0.25,gamma=0.14,delta=0.01)
+  parms <- c(beta=0.55*0.25,gamma=0.14,delta=0.01)
 #  print(buffer[(i+1)*7,]$time) 
 #  print(buffer[(i+1)*7,]$I)
 #  print("-MEDIUM")
@@ -122,7 +122,7 @@ if(buffer[(i+1)*7,]$I/pop_tot > rate_infection_threshold*10 & p_vector[i+1] >= 0
 
 if(buffer[(i+1)*7,]$I/pop_tot > rate_infection_threshold*50 & p_vector[i+1] >= 0.5*k[3]) {
   
-  parms <- c(beta=0.5*0.025,gamma=0.14,delta=0.01)
+  parms <- c(beta=0.55*0.025,gamma=0.14,delta=0.01)
 #  print(buffer[(i+1)*7,]$time)
 #  print(buffer[(i+1)*7,]$I)
   
@@ -133,37 +133,37 @@ if(buffer[(i+1)*7,]$I/pop_tot > rate_infection_threshold*50 & p_vector[i+1] >= 0
 
[…]

### 2021-02-26 Manuscript/manuscript.tex
PUB

@@
 The probability by which the PM apply the lock-down reflects the different attitudes of a PM to face an epidemics (e.g.
-\textit{laissez-faire } vs very strict): thus depending on this probabilistic-parameter different scenario were simulated.
+\textit{laissez-faire} vs very strict): thus depending on this probabilistic-parameter different scenario were simulated.
 For each of them we predicted a selected set of economic impacts by using parameters estimated via econometric techniques (Difference-in -Difference) on the microeconomic data of Italy.
@@
 
-\section{Methods}
+The recent pandemic due to the spread of SARS-CoV-2 virus, opened a highly debated issue about what it would be the best approach of the policy maker to face the epidemics.
+Differently from the pandemics of the past and in particular of the XX century (e.g.
+Spanish Flu, Asiatic Flu and Hong Kong Flu), for this pandemic a very large amount of data are easily accessible.
+As consequence not only the modelling of the virus diffusion, but also the effect on socio-economic texture for the different countries can be investigated with a finer resolution.
+Among the different scientific challenges that can come up in this context, a interesting one involves the effect of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Infomation).
+Indeed the policy maker can adopt, at a first approximation, a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
+In the first extreme, the spread of virus is, of course, slowed down or stopped but, on the other side, the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods are stopped.
+On the other side, if no lock-down measures are taken by the policy-maker, the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
+In practice the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion with respect to other (for this purpose a very fine analysis was provided by Li et al.
+in  \cite{li2021temporal} and by Brauner et al.
+in \cite{brauner2021inferring}): as consequence the lock-down efficacy, within certain limits, can be tuned.
+In the literature different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.
+In particular for the model in Ref.
+\cite{kabir2020evolutionary} it is assumed that the policy-maker know perfectly the consequences of her choices and that she can act without delay to impose the optimal choice; finally it is assumed that the PM can impose a continuous factor for the lock-down, while, for different countries such factor seems to be much more discrete.
+It can be argued that most of these drawbacks of this last formidable research, are entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy maker.
+On this basis we would propose here an alternative way to model the decision of the policy maker that is based on a stochastic model instead of on a deterministic one.
+
+\section{Methods and models}
+
+\section{Data description}
 
 \section{Results and Discussion}
-
-\cite{Figueredo:2009dg}
 

### 2021-02-26 Manuscript/manuscript.tex
PUb

@@
 
-Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Removed), we considered a policy-maker (PM) that impose stochastically three types of lock-down with increasing force.
+Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead), we considered a policy-maker (PM) that impose stochastically three types of lock-down with increasing force.
 The probability by which the PM apply the lock-down reflects the different attitudes of a PM to face an epidemics (e.g.
@@
 
+\epigraph{"It was then that, in a moment, I saw what I must have been harboring in my hidden thoughts for a considerable time.
+On the one hand, Trantor possessed an extraordinarily complex social system, being a populous world made up of eight hundred smaller worlds.
+It was in itself a system complex enough to make psychohistory meaningful and yet it was simple enough, compared to the Empire as a whole, to make psychohistory perhaps practical"\\
+I.Asimov, Prelude to foundation }
+
+\newpage
 %----------------------------------------------------------------------------------------
@@
 As consequence not only the modelling of the virus diffusion, but also the effect on socio-economic texture for the different countries can be investigated with a finer resolution.
-Among the different scientific challenges that can come up in this context, a interesting one involves the effect of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Infomation).
+Among the different scientific challenges that can come up in this context, a interesting one involves the socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Infomation).
 Indeed the policy maker can adopt, at a first approximation, a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
-In the first extreme, the spread of virus is, of course, slowed down or stopped but, on the other side, the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods are stopped.
+In the first extreme, the spread of virus is, of course, stopped but, on the other side, the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods are stopped.
 On the other side, if no lock-down measures are taken by the policy-maker, the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
@@
 On this basis we would propose here an alternative way to model the decision of the policy maker that is based on a stochastic model instead of on a deterministic one.
+Furthermore, differently with respect to the previous researches, that focused basically on macroeconomic impact, here we modelled the impact of the different lock-down at microeconomic level: in particular, by means of difference in difference, we evaluated the effect of the different levels of restrictions on the sales for different product types in Italy.
+Thus the final output of the model will be not only the cumulative deaths, but also the economic damage for each selling sector.
+Moreover here we also considered that there is not only an economic cost for each death, as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data), because a consistent part of them may be recovered or even should take the intensive therapy.
+In this paper three approaches were simulated that basically shape three different PM: a very careful one, a lazy one that adopts a \textit{laissez-faire} strategy and an intermediate one.
+For each scenario, we will discuss the result of the simulation and then we will compare them in order to get a general insight.
 
-\section{Methods and models}
+\section{Model and methods}
+
+The model of the present study is composed by an epidemiological part, that shapes the diffusion of the virus, and then its output is used by the economic model to quantify the damage.
+Thus we will discuss the epidemiological part and then the economic one
+
+\subsection{Epidemiological model}
+
+Among the very large number of compartmental model that are available in the literature \cite{vynnycky2010introduction}, we considered as the core-engine of the simulations the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
+A review about the dynamics of this model will be provided in the Supporting Info of the present paper.
+Our choice is motivated by the fact that this relative simple model provide the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters.
+Thus, because the final goal of the present article is an insight on the effects of the PM care of pandemic, an not a fine grained description of the epidemics due to COVID-19, such model is suitable for our proposes\footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
+in Ref.
+\cite{ferrari2020modelling} for the description of Italian situation.
+On the other side it is possible to increase the complexity of the model with other compartments as done in the following paper \cite{giordano2020modelling} by Giordano et al.
+Note that in this last case the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)})
 

### 2021-02-26 Manuscript/structure.tex
PUb

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Arsclassica Article
% Structure Specification File
%
% This file has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Lorenzo Pantieri (http://www.lorenzopantieri.net) with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	REQUIRED PACKAGES
%----------------------------------------------------------------------------------------

\usepackage[
nochapters, % Turn off chapters since this is an article        
beramono, % Use the Bera Mono font for monospaced text (\texttt)
eulermath,% Use the Euler font for mathematics
pdfspacing, % Makes use of pdftex’ letter spacing capabilities via the microtype package
dottedtoc % Dotted lines leading to the page numbers in the table of contents
]{classicthesis} % The layout is based on the Classic Thesis style

\usepackage{arsclassica} % Modifies the Classic Thesis package

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs

\usepackage[utf8]{inputenc} % Required for including letters with accents

\usepackage{graphicx} % Required for including images
\graphicspath{{Figures/}} % Set the default folder for images

\usepackage{enumitem} % Required for manipulating the whitespace between and within lists

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{subfig} % Required for creating figures with multiple parts (subfigures)

\usepackage{amsmath,amssymb,amsthm} % For including math equations, theorems, symbols, etc

\usepackage{varioref} % More descriptive referencing

\usepackage{epigraph}

%----------------------------------------------------------------------------------------
%	THEOREM STYLES
%---------------------------------------------------------------------------------------

\theoremstyle{definition} % Define theorem styles here based on the definition style (used for definitions and examples)
\newtheorem{definition}{Definition}

\theoremstyle{plain} % Define theorem styles here based on the plain style (used for theorems, lemmas, propositions)
\newtheorem{theorem}{Theorem}

\theoremstyle{remark} % Define theorem styles here based on the remark style (used for remarks and notes)

%----------------------------------------------------------------------------------------
%	HYPERLINKS
%---------------------------------------------------------------------------------------

\hypersetup{
%draft, % Uncomment to remove all links (useful for printing in black and white)
colorlinks=true, breaklinks=true, bookmarks=true,bookmarksnumbered,
urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen, % Link colors
pdftitle={}, % PDF title
pdfauthor={\textcopyright}, % PDF Author
pdfsubject={}, % PDF Subject
pdfkeywords={}, % PDF Keywords
pdfcreator={pdfLaTeX}, % PDF Creator
pdfproducer={LaTeX with hyperref and ClassicThesis} % PDF producer
}

### 2021-02-26 Tabellozze_ISTAT/tentativo_destagionalizzazione.R

@@ -1,0 +1,2 @@
+library(readxl)
+Fabbricazione_Calzature <- read_excel("GitHub/Advanced_Microeconomics_Project/Produzione/Fabbricazione Calzature.xlsx")

### 2021-02-28 Progetto Micro/R code DID.R
PUB

@@ -1,9 +1,9 @@
 library(readxl)
 library(ggplot2)
 
-Vendite_READY <- read_excel("Vendite_READY.xlsx")
-Vendite_READY_test <- read_excel("/Users/MacBook/Documents/University of Milan/Progetto Micro/Vendite_READY_test.xlsx")
-install.packages("ggplot2")
+Vendite_READY <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Vendite_READY.xlsx")
+#Vendite_READY_test <- read_excel("/Users/MacBook/Documents/University of Milan/Progetto Micro/Vendite_READY_test.xlsx")
+#install.packages("ggplot2")
 
 
 Vendite_READY$delta<-Vendite_READY$Alimentari-Vendite_READY$NAlimentare
@@ -16,26 +16,26 @@ summary(did)
 
 
 #Abbigliamento
-Abbigliamento_READY <- read_excel("Abbigliamento_READY.xlsx")
+Abbigliamento_READY <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Abbigliamento_READY.xlsx")
 
 Abbigliamento_READY$delta1<-Abbigliamento_READY$Alimentari-Abbigliamento_READY$Abbigliamento
 ggplot(data=Abbigliamento_READY,aes(x=Data,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=Abbigliamento),color = "blue")+
   geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=delta1),color = "green")
 
-Abbigliamento <- read_excel("/Users/MacBook/Documents/University of Milan/Progetto Micro/Abbigliamento.xlsx")
+Abbigliamento <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Abbigliamento.xlsx")
 
 did1 <-lm(Alimentari ~  C + Time + Time2+Time3 + C*Time +C*Time2+C*Time3, data = Abbigliamento)
 summary(did1)
 
 
 
-Abbigliamento_PLACEBO <- read_excel("Abbigliamento_PLACEBO.xlsx")
[…]

### 2021-02-28 Tabellozze_ISTAT/tentativo_destagionalizzazione.R

@@ -1,2 +1,244 @@
 library(readxl)
-Fabbricazione_Calzature <- read_excel("GitHub/Advanced_Microeconomics_Project/Produzione/Fabbricazione Calzature.xlsx")
+library(fpp)
+library(ggplot2)
+
+Destagionalizzazione <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Destagionalizzazione.xlsx")
+
+
+ts_beer = ts(Destagionalizzazione$alimentare,frequency = 12)
+
+
+dec<-decompose(ts_beer,type="additive")
+
+plot(dec)
+
+
+ts_beer_2 = ts(Destagionalizzazione$`abbigliamento e pellicce`,frequency = 12)
+
+dec_2<-decompose(ts_beer_2,type="additive")
+
+plot(dec_2)
+
+
+ts_beer_3 = ts(Destagionalizzazione$Calzature,frequency = 12)
+
+dec_3<-decompose(ts_beer_2,type="additive")
+
+plot(dec_3)
+
+
+ts_beer_4 = ts(Destagionalizzazione$Elettrodomestici,frequency = 12)
+
+dec_4<-decompose(ts_beer_4,type="additive")
+
+plot(dec_4)
+
+
+ts_beer_5 = ts(Destagionalizzazione$Mobili,frequency = 12)
+
+dec_5<-decompose(ts_beer_5,type="additive")
+
+plot(dec_5)
+
+ts_beer_6 = ts(Destagionalizzazione$Informatica,frequency = 12)
+
+dec_6<-decompose(ts_beer_6,type="additive")
+
+plot(dec_6)
+
+ts_beer_7 = ts(Destagionalizzazione$Fotoottica,frequency = 12)
+
+dec_7<-decompose(ts_beer_7,type="additive")
+
+plot(dec_7)
+
+ts_beer_8 = ts(Destagionalizzazione$Casalinghi,frequency = 12)
+
+dec_8<-decompose(ts_beer_8,type="additive")
+
+plot(dec_8)
+
+ts_beer_9 = ts(Destagionalizzazione$Utilenseria,frequency = 12)
+
+dec_9<-decompose(ts_beer_9,type="additive")
+
+plot(dec_9)
+
+ts_beer_10 = ts(Destagionalizzazione$Profumeria,frequency = 12)
+
[…]

### 2021-02-28 occupazione.R

@@ -1,0 +1,8 @@
+library(readxl)
+library(ggplot2)
+Occupazione <- read_excel("GitHub/Advanced_Microeconomics_Project/Produzione/Occupazione.xlsx")
+
+ggplot(data=Occupazione,aes(x=Time,y=(Ind-Det)/Ind))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=log(Det)),color = "blue") 
+
+test_Legno_carta<-lm(Ind[1:8]-Det[1:8] ~ Time[1:8],data=Occupazione)
+summary(test_Legno_carta)

### 2021-03-01 Progetto Micro/Destag_check.R
PUB

@@ -1,0 +1,60 @@
+library(readxl)
+Data <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Testtt.xlsx")
+
+Controllo_abbigliamento<-lm(Data$Abbigliamento[20:32]~Data$Time[20:32])
+summary(Controllo_abbigliamento)
+
+Controllo_calzature<-lm(Data$Calzature[20:32]~Data$Time[20:32])
+summary(Controllo_calzature)
+
+Controllo_Elettrodomestici<-lm(Data$Elettrodomestici[20:32]~Data$Time[20:32])
+summary(Controllo_Elettrodomestici)
+
+Controllo_Mobili<-lm(Data$Mobili[20:32]~Data$Time[20:32])
+summary(Controllo_Mobili)
+
+Controllo_Fotootica<-lm(Data$Fotoottica[20:32]~Data$Time[20:32])
+summary(Controllo_Fotootica)
+
+Controllo_Casalinghi<-lm(Data$Casalinghi[20:32]~Data$Time[20:32])
+summary(Controllo_Casalinghi)
+
+Controllo_Utilenseria<-lm(Data$Utilenseria[20:32]~Data$Time[20:32])
+summary(Controllo_Utilenseria)
+
+Controllo_Cartoleria<-lm(Data$Cartoleria[20:32]~Data$Time[20:32])
+summary(Controllo_Cartoleria)
+
+Controllo_Giocattoli<-lm(Data$Giocattoli[20:32]~Data$Time[20:32])
+summary(Controllo_Giocattoli)
+
+
+
+reg2<-lm(Data$Abbigliamento[20:36]~Data$T1[20:36]+Data$T2[20:36]+Data$T3[20:36])
+summary(reg2)
+
+reg3<-lm(Data$Calzature[20:36]~Data$T1[20:36]+Data$T2[20:36]+Data$T3[20:36])
+summary(reg3)
+
+reg4<-lm(Data$Elettrodomestici[20:36]~Data$T1[20:36]+Data$T2[20:36]+Data$T3[20:36])
+summary(reg4)
+
+reg5<-lm(Data$Mobili[20:36]~Data$T1[20:36]+Data$T2[20:36]+Data$T3[20:36])
+summary(reg5)
+
[…]

### 2021-03-01 Tabellozze_ISTAT/tentativo_destagionalizzazione.R

@@ -1,166 +1,224 @@
 library(readxl)
+library(xlsx)
 library(fpp)
 library(ggplot2)
+library(zoo)
+
+
+pallete = c('red', 'blue', 'green', 'orange')
 
 Destagionalizzazione <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Destagionalizzazione.xlsx")
 
 
-ts_beer = ts(Destagionalizzazione$alimentare,frequency = 12)
+TS_Alimentare = ts(Destagionalizzazione$alimentare,frequency = 12)
 
+TS_Alimentare_dec<-decompose(TS_Alimentare,type="additive")
 
-dec<-decompose(ts_beer,type="additive")
+TS_Alimentare_dec$trend=TS_Alimentare_dec$trend-TS_Alimentare_dec$random
 
-plot(dec)
+TS_Alimentare_dec$random[1:48]=0
 
+autoplot(TS_Alimentare_dec)
 
-ts_beer_2 = ts(Destagionalizzazione$`abbigliamento e pellicce`,frequency = 12)
 
-dec_2<-decompose(ts_beer_2,type="additive")
+TS_Abbigliamento = ts(Destagionalizzazione$`abbigliamento e pellicce`,frequency = 12)
 
-plot(dec_2)
+TS_Abbigliamento_dec<-decompose(TS_Abbigliamento,type="additive")
 
+TS_Abbigliamento_dec$trend[30:48]=TS_Abbigliamento_dec$trend[30:48]+TS_Abbigliamento_dec$random[30:48]
 
-ts_beer_3 = ts(Destagionalizzazione$Calzature,frequency = 12)
+TS_Abbigliamento_dec$random[30:48]=0
 
-dec_3<-decompose(ts_beer_2,type="additive")
+autoplot(TS_Abbigliamento_dec)
 
-plot(dec_3)
 
+TS_Calzature = ts(Destagionalizzazione$Calzature,frequency = 12)
 
-ts_beer_4 = ts(Destagionalizzazione$Elettrodomestici,frequency = 12)
+TS_Calzature_dec<-decompose(TS_Calzature,type="additive")
 
-dec_4<-decompose(ts_beer_4,type="additive")
[…]

### 2021-03-01 Manuscript/manuscript.tex
PUB

@@
 
-Among the very large number of compartmental model that are available in the literature \cite{vynnycky2010introduction}, we considered as the core-engine of the simulations the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
-A review about the dynamics of this model will be provided in the Supporting Info of the present paper.
+Among the very large number of compartmental model that are available in the literature \cite{vynnycky2010introduction}, we considered as the simulator of the epidemic diffusion the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
 Our choice is motivated by the fact that this relative simple model provide the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters.
@@
 On the other side it is possible to increase the complexity of the model with other compartments as done in the following paper \cite{giordano2020modelling} by Giordano et al.
-Note that in this last case the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)})
+Note that in this last case the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)}).
+The SIRD model,first proposed by Kermack and McKendrick \cite{kermack1927contribution}, is given by the following set of differential equations\cite{vynnycky2010introduction}:
+\begin{equation} 
+\begin{split}
+\dfrac{dS(t)}{dt} & = - \frac{\beta I(t) S(t)}{N} \\
+\dfrac{dI(t)}{dt} & = \frac{\beta I(t) S(t)}{N} -\gamma I(t) -\mu I(t) \\
+\dfrac{dR(t)}{dt} & = \gamma I(t) \\
+\dfrac{dD(t)}{dt} & = \mu I(t)
+\end{split}
+\end{equation}
+where S is the number of people that are still susceptible, I the number of people that are infected  and R people that are recovered while D are people that are death.
+N denotes the total popolation, that for the timing considered here can be considered fixed \footnote{Othervise, if longer horizontal timing is considered, it is necessary to consider also a source term for the births and a well term for the natural deaths.
+For further details see \cite{vynnycky2010introduction}}.
+On the other side $\beta$,$\gamma$ and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality defined  as the probability to die conditionally to be ill).
+Usually epidemiologist are interested in the ratio:
+\begin{equation} 
+R_{0}=\dfrac{\beta}{\gamma}
+\end{equation}
+know as the basic reproduction factor.
+This number, that is the average number of people that are infected by a single individual, describe if the epidemic is in a negative feedback (R$_{0}$<1), stationary (R$_{0}$=1), or in a positive feedback (R$_{0}$>1).
+As consequence if the epidemic is in a negative feedback it will be going to dissipate, if it is in positive feedback it will grow.
+Note that in this simple model since the parameters are not time dependent this factor is constant.
+If, as performed by \cite{ferrari2020modelling}, one consider time dependet parameters it will obtain a time depended parameter called $R_{t}$.
+For the present work we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
+The overall population $N$ was set to 60M, in order to simulate Italian population.
+Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threeshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$.
+As we said the PM act with a certain probability: in particular each week a random number is extracted: if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not.
+The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one.
+In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results.
 

### 2021-03-01 Analisi_cassa_integrazione/Cassa_integrazione.R

@@ -1,0 +1,10 @@
+library(readxl)
+library(ggplot2)
+
+Dati_cassa_integrazione <- read_excel("GitHub/Advanced_Microeconomics_Project/Analisi_cassa_integrazione/Dati_cassa_integrazione.xlsx")
+
+
+reg<-lm(Ore *3.28 /1000000000 ~ Time+ T1+T2+T3,data=Dati_cassa_integrazione)
+summary(reg)
+
+plot(Dati_cassa_integrazione$Ore*3.28 /1000000000 )

### 2021-03-01 Analisi_vendite/R code DID.R

@@ -1,7 +1,7 @@
 library(readxl)
 library(ggplot2)
 
-Vendite_READY <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Vendite_READY.xlsx")
+Vendite_READY <- read_excel("Vendite_READY.xlsx")
 #Vendite_READY_test <- read_excel("/Users/MacBook/Documents/University of Milan/Progetto Micro/Vendite_READY_test.xlsx")
 #install.packages("ggplot2")
 
@@ -16,26 +16,26 @@ summary(did)
 
 
 #Abbigliamento
-Abbigliamento_READY <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Abbigliamento_READY.xlsx")
+Abbigliamento_READY <- read_excel("Abbigliamento_READY.xlsx")
 
 Abbigliamento_READY$delta1<-Abbigliamento_READY$Alimentari-Abbigliamento_READY$Abbigliamento
 ggplot(data=Abbigliamento_READY,aes(x=Data,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=Abbigliamento),color = "blue")+
   geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=delta1),color = "green")
 
-Abbigliamento <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Abbigliamento.xlsx")
+Abbigliamento <- read_excel("Abbigliamento.xlsx")
 
 did1 <-lm(Alimentari ~  C + Time + Time2+Time3 + C*Time +C*Time2+C*Time3, data = Abbigliamento)
 summary(did1)
 
 
 
-Abbigliamento_PLACEBO <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Abbigliamento_PLACEBO.xlsx")
+Abbigliamento_PLACEBO <- read_excel("Abbigliamento_PLACEBO.xlsx")
 
 did2 <-lm(Alimentari ~  C + Time + Time2+Time3 + C*Time +C*Time2+C*Time3, data = Abbigliamento_PLACEBO  )
 summary(did2)
 
 
[…]

### 2021-03-01 Tabellozze_ISTAT/tentativo_destagionalizzazione.R

@@ -7,16 +7,16 @@ library(zoo)
 
 pallete = c('red', 'blue', 'green', 'orange')
 
-Destagionalizzazione <- read_excel("GitHub/Advanced_Microeconomics_Project/Progetto Micro/Destagionalizzazione.xlsx")
-
+Destagionalizzazione <- read_excel("Destagionalizzazione.xlsx")
 
 TS_Alimentare = ts(Destagionalizzazione$alimentare,frequency = 12)
 
 TS_Alimentare_dec<-decompose(TS_Alimentare,type="additive")
+TS_Alimentare_dec$random[42:48]=0
 
-TS_Alimentare_dec$trend=TS_Alimentare_dec$trend-TS_Alimentare_dec$random
+TS_Alimentare_dec$trend=TS_Alimentare_dec$x-TS_Alimentare_dec$random-TS_Alimentare_dec$seasonal
 
-TS_Alimentare_dec$random[1:48]=0
+
 
 autoplot(TS_Alimentare_dec)
 
@@ -25,20 +25,30 @@ TS_Abbigliamento = ts(Destagionalizzazione$`abbigliamento e pellicce`,frequency 
 
 TS_Abbigliamento_dec<-decompose(TS_Abbigliamento,type="additive")
 
-TS_Abbigliamento_dec$trend[30:48]=TS_Abbigliamento_dec$trend[30:48]+TS_Abbigliamento_dec$random[30:48]
+#TS_Abbigliamento_dec$trend[30:48]=TS_Abbigliamento_dec$trend[30:48]+TS_Abbigliamento_dec$random[30:48]
 
 TS_Abbigliamento_dec$random[30:48]=0
 
+TS_Abbigliamento_dec$trend=TS_Abbigliamento_dec$x-TS_Abbigliamento_dec$random-TS_Abbigliamento_dec$seasonal
+
 autoplot(TS_Abbigliamento_dec)
+
+
+autoplot(TS_Abbigliamento_dec$trend)+ geom_line(aes(y=TS_Alimentare_dec$trend))
+
 
 
 TS_Calzature = ts(Destagionalizzazione$Calzature,frequency = 12)
 
 TS_Calzature_dec<-decompose(TS_Calzature,type="additive")
 
[…]

### 2021-03-01 Manuscript/manuscript.tex
PUB

@@
 The overall population $N$ was set to 60M, in order to simulate Italian population.
-Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threeshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$.
-As we said the PM act with a certain probability: in particular each week a random number is extracted: if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not.
+Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$.
+As we said the PM act with a certain probability, more formally stochastically: each week a random number is extracted, if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not.
 The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one.
 In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results.
+At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions.
+
+\subsection{Economic model}
+
+The values obtained previous are used in the following way to evaluate the economic impact: the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300K EUR), this choice is based on the idea that, the PM, if act improperly, can be incriminated for manslaughter and than, if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account.
+In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}.
+Beside this impact there is also the cost associated to the medical care of each ill people, for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR.
 

### 2021-03-02 Analisi_vendite/Test vari/Destag_Full_check.R
PUB

@@ -1,0 +1,92 @@
+library(readxl)
+library(ggplot2)
+Data <- read_excel("Dati_destagionalizzati.xlsx")
+
+Controllo_abbigliamento<-lm(Data$Abbigliamento[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_abbigliamento)
+
+Controllo_calzature<-lm(Data$Calzature[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_calzature)
+
+Controllo_Elettrodomestici<-lm(Data$Elettrodomestici[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Elettrodomestici)
+
+Controllo_Mobili<-lm(Data$Mobili[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Mobili)
+
+Controllo_Fotootica<-lm(Data$Fotoottica[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Fotootica)
+
+Controllo_Casalinghi<-lm(Data$Casalinghi[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Casalinghi)
+
+Controllo_Utilenseria<-lm(Data$Utilenseria[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Utilenseria)
+
+Controllo_Cartoleria<-lm(Data$Cartoleria[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Cartoleria)
+
+Controllo_Giocattoli<-lm(Data$Giocattoli[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
+summary(Controllo_Giocattoli)
+
+
+reg2<-lm(Data$Abbigliamento-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+summary(reg2)
+
+reg3<-lm(Data$Calzature-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+summary(reg3)
+
+reg4<-lm(Data$Elettrodomestici-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+summary(reg4)
+
+reg5<-lm(Data$Mobili-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+summary(reg5)
+
[…]

### 2021-03-02 Analisi_vendite/Test vari/Plotter_destag.R

@@ -1,0 +1,30 @@
+library(readxl)
+library(ggplot2)
+Data <- read_excel("Dati_destagionalizzati_FULL.xlsx")
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
+  labs(title="Abbigliamento") + geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Calzature),color = "darkgreen")+ 
+  labs(title="Calzature")+ geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Elettrodomestici),color = "orange")+ 
+  labs(title="Elettrodomestici") + geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Mobili),color = "purple")+ 
+  labs(title="Mobili") + geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Fotoottica),color = "darkblue")+ 
+  labs(title="Fotoottica") + geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Casalinghi),color = "cyan")+ 
[…]

### 2021-03-02 Analisi_vendite/Test vari/tentativo_destagionalizzazione.R

@@ -1,0 +1,361 @@
+library(readxl)
+library(xlsx)
+library(fpp)
+library(ggplot2)
+library(zoo)
+
+
+pallete = c('red', 'blue', 'green', 'orange')
+
+Destagionalizzazione <- read_excel("Destagionalizzazione.xlsx")
+
+TS_Alimentare = ts(Destagionalizzazione$alimentare,frequency = 12)
+
+TS_Alimentare_dec<-decompose(TS_Alimentare,type="additive")
+TS_Alimentare_dec$random[1:48]=0
+
+TS_Alimentare_dec$trend=TS_Alimentare_dec$x-TS_Alimentare_dec$random-TS_Alimentare_dec$seasonal
+
+
+
+autoplot(TS_Alimentare_dec)
+
+
+TS_Abbigliamento = ts(Destagionalizzazione$`abbigliamento e pellicce`,frequency = 12)
+
+TS_Abbigliamento_dec<-decompose(TS_Abbigliamento,type="additive")
+
+#TS_Abbigliamento_dec$trend[30:48]=TS_Abbigliamento_dec$trend[30:48]+TS_Abbigliamento_dec$random[30:48]
+
+TS_Abbigliamento_dec$random[30:48]=0
+
+TS_Abbigliamento_dec$trend=TS_Abbigliamento_dec$x-TS_Abbigliamento_dec$random-TS_Abbigliamento_dec$seasonal
+
+autoplot(TS_Abbigliamento_dec)
+
+
+autoplot(log10(TS_Abbigliamento_dec$trend))+ geom_line(aes(y=log10(TS_Alimentare_dec$trend)))
+
+
+
+TS_Calzature = ts(Destagionalizzazione$Calzature,frequency = 12)
+
+TS_Calzature_dec<-decompose(TS_Calzature,type="additive")
+
+#TS_Calzature_dec$trend[30:48]=TS_Calzature_dec$trend[30:48]+TS_Calzature_dec$random[30:48]
+
+TS_Calzature_dec$random[31:48]=0
+
+TS_Calzature_dec$trend=TS_Calzature_dec$x-TS_Calzature_dec$random-TS_Calzature_dec$seasonal
+
+autoplot(TS_Calzature_dec$trend)+ geom_line(aes(y=TS_Alimentare_dec$trend))
+
+autoplot(TS_Calzature_dec)
+
[…]

### 2021-03-02 Presentazione/Presentation.tex
PUB

\documentclass[compress]{beamer}
\usepackage{hyperref}
\hypersetup{
    pdftitle = {Results}, % <-- Missing in PDF
    pdfauthor = {Marzio De Corato},
    pdfsubject = {Deseasoning and DID}
}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
%\author{Marzio De Corato}
\usepackage{varwidth}
\usepackage{beamerthemesplit}

\usepackage[english]{babel}
\usepackage[backend=bibtex]{biblatex}
\addbibresource{bibliography.bib}

\useoutertheme{miniframes}

\usetheme[progressbar=frametitle]{Madrid}
\usefonttheme{professionalfonts}
\setbeamertemplate{itemize items}[triangle]
\setbeamertemplate{enumerate items}[default]
\usecolortheme{beaver}

%Information to be included in the title page:

\title[Deseasoning and DID]{}

\author{Marzio De Corato e Giulia Hadjiandrea}
\date{}

\title{Destagionalizzazione e DID}

\setbeamertemplate{enumerate items}[default]
\usecolortheme{beaver}

\begin{document}

\frame{\titlepage}

\usebackgroundtemplate{ }

%\author{Marzio De Corato}

\section{Intro}

\begin{frame}
\frametitle{Regression}
\begin{itemize}
\item T Variabile temporale: n numero di mesi prima di Febbraio (ultimo mese senza lock-down)
\item $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW). Nei grafici questo periodo è segnato dalle barre tratteggiate.
\item $Y_{x}$ volume di vendite per il settore x 
\end{itemize}
\begin{equation}
Y_{x}-Y_{Alimentare}=\alpha+\delta_{before T1}T+\delta_{T1}T_{1}+\delta_{T2}T_{2}+\delta_{T3}T_{3}+\epsilon
\end{equation}
\end{frame}

\begin{frame}
\frametitle{Abbigliamento}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Abbigliamento.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.33  & 0.07  \\ \hline
$\delta_{T1}$   & -40.16 & 2.30  \\ \hline
$\delta_{T2}$   & -60.07 & 3.1   \\ \hline
$\delta_{T3}$   & -16.45 & 3.17 
\end{tabular}
\end{table}

\end{columns}
\end{frame}

\begin{frame}
\frametitle{Calzature}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Calzature.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
$\delta_{T1}$   & -38.70 & 1.86   \\ \hline
$\delta_{T2}$   & -65.78 & 2.57  \\ \hline
$\delta_{T3}$   & -20.62 & 2.57 
\end{tabular}
\end{table}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Elettrodomestici}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Elettrodomestici.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.12  & 0.06  \\ \hline
$\delta_{T1}$   & -20.32 & 2.62   \\ \hline
$\delta_{T2}$   & -27.34 & 3.62  \\ \hline
$\delta_{T3}$   & -3.68 & 3.62
\end{tabular}
\end{table}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Fotoottica}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Fotoottica.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.40  & 0.07  \\ \hline
$\delta_{T1}$   & -34.14 & 2.76   \\ \hline
$\delta_{T2}$   & -52.32 & 3.82  \\ \hline
$\delta_{T3}$   & -7.86 & 3.82
\end{tabular}
\end{table}
\end{columns}
\end{frame}

%\subsection{Stars Feature}

%\begin{frame}
%\frametitle{Theoretical background - Star features }
%\begin{columns}
%\column{0.4\textwidth}
%\begin{itemize}
%\item \textbf{Main features}: For this work the main features of star are the stellar luminosity (S\_L), its temperature (S\_T) and spectral type (S\_S\_T)
%\item\textbf{H-R diagram}: with these features the Hertzsprung-Russell diagram classify the stars (the temperature and spectral type of a star are two faces of the same medal)
%\end{itemize}
%\column{0.45\textwidth}
%\includegraphics[width=\linewidth,]{Pic/S_T_T_explanation.png}
%\begin{center}
%Image taken from \cite{HR_diagram}
%\end{center}
%\end{columns}
%\end{frame}

\end{document}

### 2021-03-02 Analisi_vendite/Test vari/Destag_Full_check.R
PUB

@@ -30,19 +30,19 @@ Controllo_Giocattoli<-lm(Data$Giocattoli[1:19]-Data$Alimentari[1:19]~Data$Time[1
 summary(Controllo_Giocattoli)
 
 
-reg2<-lm(Data$Abbigliamento-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+reg2<-lm(Data$Abbigliamento-Data$Alimentari~Data$Time+Data$T1+Data$T2+Data$T3)
 summary(reg2)
 
-reg3<-lm(Data$Calzature-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+reg3<-lm(Data$Calzature-Data$Alimentari~Data$Time+Data$T1+Data$T2+Data$T3)
 summary(reg3)
 
-reg4<-lm(Data$Elettrodomestici-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+reg4<-lm(Data$Elettrodomestici-Data$Alimentari~Data$Time+Data$T1+Data$T2+Data$T3)
 summary(reg4)
 
-reg5<-lm(Data$Mobili-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+reg5<-lm(Data$Mobili-Data$Alimentari~Data$Time+Data$T1+Data$T2+Data$T3)
 summary(reg5)
 
-reg6<-lm(Data$Fotoottica-Data$Alimentari~Data$T1+Data$T2+Data$T3)
+reg6<-lm(Data$Fotoottica-Data$Alimentari~Data$Time+Data$T1+Data$T2+Data$T3)
 summary(reg6)
 
 reg7<-lm(Data$Casalinghi-Data$Alimentari~Data$T1+Data$T2+Data$T3)

### 2021-03-02 Presentazione/Presentation.tex
PUB

@@
 \includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_RAW.pdf}\\
-\includegraphics[width=5cm,height=4cm]{Pic/Abbigliamento.pdf}
+\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento.pdf}
 \column{.5\textwidth}
@@
 \includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_Matrix.pdf}\\
-\begin{itemize}
-\item Rosso: Alimentari
-\end{itemize}
 \begin{table}[]
@@
                 & Value  & Error \\ \hline
-$\delta$ Slope before T1 & -0.33  & 0.07  \\ \hline
-$\delta_{T1}$   & -40.16 & 2.30  \\ \hline
-$\delta_{T2}$   & -60.07 & 3.1   \\ \hline
-$\delta_{T3}$   & -16.45 & 3.17 
+$\delta$ Slope before T1 & -0.33  & 0.09  \\ \hline
+$\delta_{T1}$   & -36.33 & 2.15  \\ \hline
+$\delta_{T2}$   & -56.23 & 2.77   \\ \hline
+$\delta_{T3}$   & -11.95 & 2.86 \\ \hline
+$\delta_{T4}$ (Plc T= -3)   & 14.55  & 13.14 \\ \hline
+$\delta_{T6}$ (Plc T= -1) & 13.90 & 13.30
 \end{tabular}
@@
 \includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_Matrix.pdf}\\
-\begin{itemize}
-\item Rosso: Alimentari
-\end{itemize}
 \begin{table}[]
@@
                 & Value  & Error \\ \hline
-$\delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
-$\delta_{T1}$   & -38.70 & 1.86   \\ \hline
-$\delta_{T2}$   & -65.78 & 2.57  \\ \hline
-$\delta_{T3}$   & -20.62 & 2.57 
+$\delta$ Slope before T1 & -0.22  & 0.08  \\ \hline
+$\delta_{T1}$   & -38.70 & 1.91   \\ \hline
+$\delta_{T2}$   & -63.21 & 2.47  \\ \hline
+$\delta_{T3}$   & -17.61 & 2.54  \\ \hline
+$\delta_{T4}$ (Plc T= -3)   & 15.10  & 13.95 \\ \hline
+$\delta_{T6}$ (Plc T= -1) & 15.36 & 14.12
 \end{tabular}
@@
 \includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_Matrix.pdf}\\
-\begin{itemize}
-\item Rosso: Alimentari
-\end{itemize}
 \begin{table}[]
@@
                 & Value  & Error \\ \hline
-$\delta$ Slope before T1 & -0.12  & 0.06  \\ \hline
-$\delta_{T1}$   & -20.32 & 2.62   \\ \hline
-$\delta_{T2}$   & -27.34 & 3.62  \\ \hline
-$\delta_{T3}$   & -3.68 & 3.62
+$\delta$ Slope before T1 & -0.12  & 0.14  \\ \hline
+$\delta_{T1}$   & -19.21 & 3.10   \\ \hline
+$\delta_{T2}$   & -26.23 & 4.00  \\ \hline
+$\delta_{T3}$   & -2.37 & 4.12  \\ \hline
+$\delta_{T4}$ (Plc T= -3)   & 8.80  & 7.57 \\ \hline
+$\delta_{T6}$ (Plc T= -1) & 4.86 & 7.66
 \end{tabular}
@@
 \includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_Matrix.pdf}\\
-\begin{itemize}
-\item Rosso: Alimentari
-\end{itemize}
+
 \begin{table}[]
@@
                 & Value  & Error \\ \hline
-$\delta$ Slope before T1 & -0.40  & 0.07  \\ \hline
-$\delta_{T1}$   & -34.14 & 2.76   \\ \hline
-$\delta_{T2}$   & -52.32 & 3.82  \\ \hline
-$\delta_{T3}$   & -7.86 & 3.82
+$\delta$ Slope before T1 & -0.36  & 0.12 \\ \hline
+$\delta_{T1}$   & -29.94 & 2.73   \\ \hline
+$\delta_{T2}$   & -48.11 & 3.52  \\ \hline
+$\delta_{T3}$   & -2.93 & 3.63 \\ \hline
+$\delta_{T4}$ (Plc T= -3)   & 8.87  & 78.87 \\ \hline
+$\delta_{T6}$ (Plc T= -1) & 11.65 & 12.12
 \end{tabular}

### 2021-03-02 Analisi_vendite/Test vari/Destag_Full_check.R

@@ -58,6 +58,81 @@ reg10<-lm(Data$Giocattoli-Data$Alimentari~Data$T1+Data$T2+Data$T3)
 summary(reg10)
 
 
+
+###########################PLACEBO_1#####################################
+
+
+reg2<-lm(Data$Abbigliamento-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg2)
+
+reg3<-lm(Data$Calzature-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg3)
+
+reg4<-lm(Data$Elettrodomestici-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg4)
+
+reg5<-lm(Data$Mobili-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg5)
+
+reg6<-lm(Data$Fotoottica-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg6)
+
+reg7<-lm(Data$Casalinghi-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg7)
+
+reg8<-lm(Data$Utilenseria-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg8)
+
+reg9<-lm(Data$Cartoleria-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg9)
+
+reg10<-lm(Data$Giocattoli-Data$Alimentari~Data$Time+Data$T4+Data$T5+Data$T6)
+summary(reg10)
+
+
+
+###########################PLACEBO_2#####################################
+
+
+reg2<-lm(Data$Abbigliamento-Data$Alimentari~Data$Time+Data$T7+Data$T8+Data$T9)
+summary(reg2)
+
+reg3<-lm(Data$Calzature-Data$Alimentari~Data$Time+Data$T7+Data$T8+Data$T9)
+summary(reg3)
+
+reg4<-lm(Data$Elettrodomestici-Data$Alimentari~Data$Time+Data$T7+Data$T8+Data$T9)
+summary(reg4)
+
+reg5<-lm(Data$Mobili-Data$Alimentari~Data$Time+Data$T7+Data$T8+Data$T9)
+summary(reg5)
+
[…]

### 2021-03-02 Analisi_vendite/Test vari/DID_files/DID_code_dest.R
PUB

@@ -1,0 +1,40 @@
+library(readxl)
+
+Dati_Abbigliamento <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Abbigliamento")
+
+
+Abbigliamento <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Abbigliamento )
+summary(Abbigliamento)
+
+Abbigliamento_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Abbigliamento )
+summary(Abbigliamento_placebo)
+
+
+Dati_Calzature <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Calzature")
+
+
+Calzature <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Calzature)
+summary(Calzature)
+
+Calzature_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Calzature )
+summary(Calzature_placebo)
+
+
+Dati_Elettrodomestici <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Elettrodomestici")
+
+
+Elettrodomestici <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Elettrodomestici)
+summary(Elettrodomestici)
+
+Elettrodomestici_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Elettrodomestici )
+summary(Elettrodomestici_placebo)
+
+
+Dati_Fotoottica <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Fotoottica")
+
+
+Fotoottica  <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Fotoottica )
+summary(Fotoottica)
+
+Fotoottica_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Fotoottica )
+summary(Fotoottica_placebo)

### 2021-03-02 Manuscript/manuscript.tex
PUB

@@
 Note that in this simple model since the parameters are not time dependent this factor is constant.
-If, as performed by \cite{ferrari2020modelling}, one consider time dependet parameters it will obtain a time depended parameter called $R_{t}$.
-For the present work we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
+If, as performed by Ferrari et al.
+\cite{ferrari2020modelling}, time dependent parameters are considered a time depended parameter called $R_{t}$.
+For the present work, we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
 The overall population $N$ was set to 60M, in order to simulate Italian population.
 Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$, there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$, if the normalized infected people are more than 10 the previous threshold  she will impose, with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$, finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$.
+These attenuation parameters were adjusted taking in consideration the results of Marziano et al.
+in Ref.
+\cite{marziano2021retrospective}.
 As we said the PM act with a certain probability, more formally stochastically: each week a random number is extracted, if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not.

### 2021-03-03 Manuscript/manuscript.tex
PUB

@@
 \cite{marziano2021retrospective}.
-As we said the PM act with a certain probability, more formally stochastically: each week a random number is extracted, if this is higher than a certain threshold the relative restrictive decision is taken, otherwise not.
+As we said the PM act with a certain probability, more formally stochastically: each week a random number (from zero to one) is extracted, if this is higher than a certain threshold, the relative restrictive decision is taken, otherwise not.
 The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one.
 In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results.
-At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions.
+At the end of the simulation, beside the values given by the standard SIRD model (recovered and deaths), the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
 
@@
 
-The values obtained previous are used in the following way to evaluate the economic impact: the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300K EUR), this choice is based on the idea that, the PM, if act improperly, can be incriminated for manslaughter and than, if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account.
+The economic impact for each epidemiological scenario is shaped as follow: the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
+This choice is based on the idea that, if the PM act improperly, can be incriminated for manslaughter and than, if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account.
 In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}.
-Beside this impact there is also the cost associated to the medical care of each ill people, for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR.
+Beside this impact there is also the cost associated to the medical care of each ill people, for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that, in principle, there is also another import health-care impact due to the fact that the ill people for COVID-19 saturate the health system thus making it unreachable for other disease.
+This spillover translates in to more death and more ill people with respect to the baseline situation where there isn't an pandemic: however, by now, this effect is difficult to quantify and so we did not included in to the present model}.
 

### 2021-03-03 Presentazione/Presentation.tex
PUB

@@
 \useoutertheme{miniframes}
+\DeclareUnicodeCharacter{200A}{!!!FIX ME!!!}
 
@@
 \begin{frame}
-\frametitle{Regression}
+\frametitle{Trend Check}
 \begin{itemize}
@@
 \item $Y_{x}$ volume di vendite per il settore x 
+\item I dati sono stati raccolti dal sito ISTAT 
 \end{itemize}
@@
 
-%\subsection{Stars Feature}
+\begin{frame}
+\frametitle{DID estimation with deseasonalized data}
+\begin{itemize}
+\item C dummy per il gruppo di controllo (Alimentari), $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW)
+\item DID a più tempi come già sviluppato con successo da Draca et. al in \cite{draca2011panic} and da Wooldridge in  \cite{wooldridge2012introductory}
 
-%\begin{frame}
-%\frametitle{Theoretical background - Star features }
-%\begin{columns}
-%\column{0.4\textwidth}
-%\begin{itemize}
-%\item \textbf{Main features}: For this work the main features of star are the stellar luminosity (S\_L), its temperature (S\_T) and spectral type (S\_S\_T)
-%\item\textbf{H-R diagram}: with these features the Hertzsprung-Russell diagram classify the stars (the temperature and spectral type of a star are two faces of the same medal)
-%\end{itemize}
-%\column{0.45\textwidth}
-%\includegraphics[width=\linewidth,]{Pic/S_T_T_explanation.png}
-%\begin{center}
-%Image taken from \cite{HR_diagram}
-%\end{center}
-%\end{columns}
-%\end{frame}
+\end{itemize}
+\begin{equation*}
+Y=C+T_{1}+T_{2}+T_{3}+\delta_{1}(T_{1}\times C)+\delta_{2}(T_{2}\times C)+\delta_{3}(T_{3}\times C)+\epsilon
+\end{equation*}
+\begin{table}[]
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l}
+                 & $\delta_{1}$     & $\sigma_{\delta_{1}} $   & $\delta_{2}  $    &$ \sigma_{\delta_{2}}  $   & $\delta_{3}     $ & $\sigma_{\delta_{3}} $    \\ \hline
+Abbigliamento    & -40.16 & 2.01 & -60.07 & 2.77 & -16.46 & 2.77  \\ \hline
+Calzature        & -38.70 & 1.73 & -65.78 & 2.39 & -20.62 & 2.39  \\ \hline
+Elettrodomestici & -20.32 & 2.5  & -27.34 & 3.45 & -3.68  & 3.45  \\ \hline
+Fotoottica       & -34.14 & 2.55 & -52.32 & 3.52 & -7.8   & 3.52 \\ \cline{1-1}
+\end{tabular}
+\end{table}
+\end{frame}
+
+\begin{frame}
+\frametitle{DID estimation with RAW data}
+\begin{itemize}
+\item C dummy per il gruppo di controllo (Alimentari), $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW)
+\item Errore decisamente maggiore rispetto ai dati de-stagionalizzati
+\end{itemize}
+\begin{equation*}
+Y=C+T_{1}+T_{2}+T_{3}+\delta_{1}(T_{1}\times C)+\delta_{2}(T_{2}\times C)+\delta_{3}(T_{3}\times C)+\epsilon
+\end{equation*}
+\begin{table}[]
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l}
+                 & $\delta_{1}$     & $\sigma_{\delta_{1}} $   & $\delta_{2}  $    &$ \sigma_{\delta_{2}}  $   & $\delta_{3}     $ & $\sigma_{\delta_{3}} $    \\ \hline
+Abbigliamento    & -60.70 & 13.32 & -90.89 & 13.32 & -15.69 & 13.32  \\ \hline
+Calzature        & -57.37 & 14.95 & -95.97 & 20.76 & -11.70 & 8.67  \\ \hline
+Elettrodomestici & -41.81 & 16.47  & -68.26 & 22.88 & 3.24  & 9.56  \\ \hline
+Fotoottica       & -45.33 & 9.22 & -76.48 & 12.80 & -3.77   & 5.35 \\ \cline{1-1}
+\end{tabular}
+\end{table}
+\end{frame}
+
+\begin{frame}
+\frametitle{DID estimation - placebo (deseasonalized data)}
+\begin{table}[]
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l}
+                 & $\delta_{4}$     & $\sigma_{\delta_{4}} $   & $\delta_{5}  $    &$ \sigma_{\delta_{5}}  $   & $\delta_{6}     $ & $\sigma_{\delta_{6}} $    \\ \hline
+Abbigliamento     & 3.94 & 12.65 & 4.87 & 17.47 & 0.70  & 17.47 \\ \hline
+Calzature        & 5.04 & 13.14 & 5.31 & 18.15 & 2.00  & 18.16 \\ \hline
+Elettrodomestici   & 1.13 & 6.26  & 4.63 & 8.65  & -0.81 & 8.65  \\ \hline
+Fotoottica        & 0.84 & 10.98 & 1.71 & 15.18 & 0.69  & 15.18 \\ \cline{1-1}
+\end{tabular}
+\end{table}
+\end{frame}
+
+\begin{frame}
+\frametitle{DID - Cassa integrazione}
+\centering
+\includegraphics[width=10cm,height=7cm]{Pic/CIG_TOT.pdf}\\
+
+\end{frame}
+
+\begin{frame}
+\frametitle{DID - Cassa integrazione}
+\begin{columns}[t]
+\column{.5\textwidth}
+\centering
+\includegraphics[width=5cm,height=3.5cm]{Pic/Manifattura_CIG.pdf}\\
+\includegraphics[width=5cm,height=3.5cm]{Pic/Commercio_CIG.pdf}
+\column{.5\textwidth}
+\centering
+\includegraphics[width=5cm,height=3.5cm]{Pic/Costruzioni_CIG.pdf}\\
+\includegraphics[width=5cm,height=3.5cm]{Pic/Immob_CIG.pdf}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+\frametitle{References}
+\printbibliography
+\end{frame}
 

### 2021-03-03 Analisi_cassa_integrazione/Cassa_integrazione.R

@@ -1,7 +1,74 @@
 library(readxl)
 library(ggplot2)
 
-Dati_cassa_integrazione <- read_excel("GitHub/Advanced_Microeconomics_Project/Analisi_cassa_integrazione/Dati_cassa_integrazione.xlsx")
+Dati_cassa_integrazione <- read_excel("Dati_cassa_integrazione.xlsx")
+Dati_cassa_integrazione_Manifattura <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Manifattura")
+Dati_cassa_integrazione_Manifattura <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Manifattura")
+
+ggplot(data=Dati_cassa_integrazione_Manifattura ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
+geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
+  geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
+geom_vline(xintercept = 27, linetype="dashed", color = "orange", size=1)+ 
+geom_vline(xintercept = 28, linetype="dashed", color = "red", size=1)+
+geom_vline(xintercept = 29, linetype="dashed", color = "orange", size=1)+ 
+geom_vline(xintercept = 30, linetype="dashed", color = "darkgreen", size=1)+
+ggtitle("Ore CIG COVID (ord) vs non COVID (str1) vs non COVID (str2) - Manifattura")+
+theme_bw() 
+
+
+
+Dati_cassa_integrazione_Commercio <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Commercio")
+
+
+ggplot(data=Dati_cassa_integrazione_Commercio  ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
+  geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
+  geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
+  geom_vline(xintercept = 27, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 28, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 29, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 30, linetype="dashed", color = "darkgreen", size=1)+
[…]

### 2021-03-03 Presentazione/Presentation.tex
PUB

@@
     pdftitle = {Results}, % <-- Missing in PDF
-    pdfauthor = {Marzio De Corato},
-    pdfsubject = {Deseasoning and DID}
+    pdfauthor = {Marzio De Corato and Giulia Hadjiandrea},
+    pdfsubject = {ID for COVID19 impact estimation}
 }
@@
 
-\title[Deseasoning and DID]{}
+\title[DID - COVID19]{}
 
@@
 
-\title{Destagionalizzazione e DID}
+\title{DID for COVID19 impact estimation}
 
@@
 \frametitle{DID - Cassa integrazione}
+\begin{itemize}
+\item Blu cassa integrazione ordinaria(CIG), Rosso Straordinaria Ristrutturazione e Crisi, Purple Straordinaria Solidarietà
+\end{itemize}
 \centering
-\includegraphics[width=10cm,height=7cm]{Pic/CIG_TOT.pdf}\\
+\includegraphics[width=9cm,height=6cm]{Pic/CIG_TOT.pdf}\\
 

### 2021-03-04 Analisi_cassa_integrazione/Cassa_integrazione.R
pub

@@ -8,10 +8,10 @@ Dati_cassa_integrazione_Manifattura <- read_excel("Cassa_integrazione_Ordered.xl
 ggplot(data=Dati_cassa_integrazione_Manifattura ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
 geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
   geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
-geom_vline(xintercept = 27, linetype="dashed", color = "orange", size=1)+ 
-geom_vline(xintercept = 28, linetype="dashed", color = "red", size=1)+
-geom_vline(xintercept = 29, linetype="dashed", color = "orange", size=1)+ 
-geom_vline(xintercept = 30, linetype="dashed", color = "darkgreen", size=1)+
+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+
 ggtitle("Ore CIG COVID (ord) vs non COVID (str1) vs non COVID (str2) - Manifattura")+
 theme_bw() 
 
@@ -23,10 +23,10 @@ Dati_cassa_integrazione_Commercio <- read_excel("Cassa_integrazione_Ordered.xlsx
 ggplot(data=Dati_cassa_integrazione_Commercio  ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
   geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
   geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
-  geom_vline(xintercept = 27, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = 28, linetype="dashed", color = "red", size=1)+
-  geom_vline(xintercept = 29, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = 30, linetype="dashed", color = "darkgreen", size=1)+
+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
[…]

### 2021-03-04 Presentazione/Presentation.tex
PUB

@@
 \usepackage{beamerthemesplit} 
+\usepackage{xcolor}
+
+\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
 
@@
 \begin{frame}
-\frametitle{Trend Check}
+\frametitle{Pre-Trend Check for performing DID}
 \begin{itemize}
 \item T Variabile temporale: n numero di mesi prima di Febbraio (ultimo mese senza lock-down)
-\item $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW). Nei grafici questo periodo è segnato dalle barre tratteggiate.
+\item $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio \textcolor{orange}{MEDIUM}, T2 Aprile  \textcolor{red}{HIGH} e T3 Giugno \textcolor{ao(english)}{LOW}.
+Nei grafici questo periodo è segnato dalle barre tratteggiate.
 \item $Y_{x}$ volume di vendite per il settore x 
-\item I dati sono stati raccolti dal sito ISTAT 
+\item I dati sono stati raccolti dal sito ISTAT e destagionalizzati con il pacchetto R \textit{Forecasting: Principles and Practice - ffp} 
 \end{itemize}
@@
 \begin{itemize}
-\item C dummy per il gruppo di controllo (Alimentari), $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio (MEDIUM), T2 Aprile (HIGH) e T3 Giugno (LOW)
+\item C dummy per il gruppo di controllo/trattamento, $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown: T1 per Marzo e Maggio \textcolor{orange}{MEDIUM}, T2 Aprile  \textcolor{red}{HIGH} e T3 Giugno \textcolor{ao(english)}{LOW}.
+\item Y volume vendite (settore x vs alimentari(controllo) )
+\item La pendenza pretrend è di due ordini di grandezza inferiore rispetto a quella degli eventi T1 e T2
 \item DID a più tempi come già sviluppato con successo da Draca et. al in \cite{draca2011panic} and da Wooldridge in  \cite{wooldridge2012introductory}
@@
 \item Blu cassa integrazione ordinaria(CIG), Rosso Straordinaria Ristrutturazione e Crisi, Purple Straordinaria Solidarietà
+\item I dati sono stati raccolti dal sito Osservatorio Cassa Integrazione Guadagni (INPS)
 \end{itemize}
@@
 \begin{frame}
+\frametitle{DID - Cassa integrazione}
+\begin{itemize}
+\item C dummy per il gruppo di controllo/trattamento, $T1$,$T2$ e $T3$ dummy per i 3 livelli di lockdown:  T1 Aprile  \textcolor{red}{HIGH}, T2 Maggio \textcolor{orange}{MEDIUM}, T3 Giugno \textcolor{ao(english)}{LOW}.
+Questo, a differenza delle vendite, perche le CIG sono più lente nell'attivarsi
+\item Come gruppo di controllo si sono usate le CIG Straordinarie - Solidarietà (purple nei grafici precedenti) 
+\item Y ore CIG erogate (Ordinaria vs Straordinaria Solidarietà (controllo))
+
+\item DID a più tempi come già sviluppato con successo da Draca et. al in \cite{draca2011panic} and da Wooldridge in  \cite{wooldridge2012introductory}
+\end{itemize}
+\begin{equation*}
+Y=C+T_{1}+T_{2}+T_{3}+\delta_{1}(T_{1}\times C)+\delta_{2}(T_{2}\times C)+\delta_{3}(T_{3}\times C)+\epsilon
+\end{equation*}
+\end{frame}
+
+\begin{frame}
+\frametitle{DID - Cassa integrazione}
+\begin{equation*}
+Y=C+T_{1}+T_{2}+T_{3}+\delta_{1}(T_{1}\times C)+\delta_{2}(T_{2}\times C)+\delta_{3}(T_{3}\times C)+\epsilon
+\end{equation*}
+\begin{table}[]
+\begin{tabular}{l|l|l|l|l|l|l}
+            & $\delta_{T1}$ (M) &  $\sigma$ (M)  & $\delta_{T2}$ (M) &    $\sigma$ (M) & $\delta_{T3}$ (M) &   $\sigma$ (M)  \\ \hline
+Totale      & 706.8  & 3.5 & 217.8  & 3.5 & 144.3  & 3.5 \\ \hline
+Manifattura & 494.1  & 3.1 & 162.3  & 3.1 & 111.4  & 3.1 \\ \hline
+Commercio   & 16.4   & 2.5 & 3.7    & 2.5 & 2.9    & 2.5 \\ \hline
+Costruzioni & 13.4   & 0.8 & 2.9    & 0.8 & 1.4    & 0.8 \\ \hline
+Immobiliare & 0      & 0   & 12.3   & 0.1 & 5.7    & 0.1
+\end{tabular}
+\end{table}
+\begin{itemize}
+\item Il settore immobiliare sembra che abbia reagito più lentamente (+1  mese)
+\end{itemize}
+\end{frame}
+
+\begin{frame}
 \frametitle{References}

### 2021-03-04 Analisi_cassa_integrazione/Cassa_integrazione.R

@@ -3,18 +3,21 @@ library(ggplot2)
 
 Dati_cassa_integrazione <- read_excel("Dati_cassa_integrazione.xlsx")
 Dati_cassa_integrazione_Manifattura <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Manifattura")
-Dati_cassa_integrazione_Manifattura <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Manifattura")
+
 
 ggplot(data=Dati_cassa_integrazione_Manifattura ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
 geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
   geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
-  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+
-ggtitle("Ore CIG COVID (ord) vs non COVID (str1) vs non COVID (str2) - Manifattura")+
+ggtitle("Ore CIG COVID (ord) vs non COVID (str1) (str2) - Manifattura")+
 theme_bw() 
 
+Dati_cassa_integrazione_Manifattura_DID <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Manifattura_DID")
+
+did_Manifattura <-lm(Hours ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_cassa_integrazione_Manifattura_DID)
+summary(did_Manifattura)
 
 
 Dati_cassa_integrazione_Commercio <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Commercio")
@@ -23,12 +26,16 @@ Dati_cassa_integrazione_Commercio <- read_excel("Cassa_integrazione_Ordered.xlsx
 ggplot(data=Dati_cassa_integrazione_Commercio  ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
   geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
   geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
[…]

### 2021-03-04 Analisi_vendite/R code DID.R

@@ -8,7 +8,10 @@ Vendite_READY <- read_excel("Vendite_READY.xlsx")
 
 Vendite_READY$delta<-Vendite_READY$Alimentari-Vendite_READY$NAlimentare
 ggplot(data=Vendite_READY,aes(x=Data,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=NAlimentare),color = "blue")+
-  geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=delta),color = "green")
+  geom_line(size=2,color = "red")+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ggtitle("Vendite Alimentari vs Dati mon Alimentari Non Destagionalizzati")+theme_bw()
 
 did <-lm(Alimentari ~  C + Time + Time2+Time3 + C*Time +C*Time2+C*Time3, data = Vendite_READY_test)
 summary(did)
@@ -20,7 +23,10 @@ Abbigliamento_READY <- read_excel("Abbigliamento_READY.xlsx")
 
 Abbigliamento_READY$delta1<-Abbigliamento_READY$Alimentari-Abbigliamento_READY$Abbigliamento
 ggplot(data=Abbigliamento_READY,aes(x=Data,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=Abbigliamento),color = "blue")+
-  geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=delta1),color = "green")
+  geom_line(size=2,color = "red")+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ggtitle("Vendite Alimentari vs Abbigliamento Dati Non Destagionalizzati")+theme_bw()
 
 Abbigliamento <- read_excel("Abbigliamento.xlsx")
[…]

### 2021-03-04 Analisi_vendite/Test vari/Plotter_destag.R

@@ -3,19 +3,35 @@ library(ggplot2)
 Data <- read_excel("Dati_destagionalizzati_FULL.xlsx")
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
-  labs(title="Abbigliamento") + geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+  labs(title="Abbigliamento")+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+theme_bw()
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Calzature),color = "darkgreen")+ 
-  labs(title="Calzature")+ geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+  labs(title="Calzature")+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+theme_bw()
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Elettrodomestici),color = "orange")+ 
-  labs(title="Elettrodomestici") + geom_vline(xintercept=5, linetype="dashed", color = "black", size=1) + geom_vline(xintercept=0, linetype="dashed", color = "black", size=1)
+  labs(title="Elettrodomestici") +  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
[…]

### 2021-03-05 Manuscript/manuscript.tex
PUB

@@
 ]{scrartcl}
+
+\usepackage{hyperref}
 
@@
 
-The economic impact for each epidemiological scenario is shaped as follow: the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
-This choice is based on the idea that, if the PM act improperly, can be incriminated for manslaughter and than, if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account.
+The economic impact for each epidemiological scenario is shaped as follow: a first set of parameters, as the economic value of a death and of being infected by COVID-19 ,was taken directly from the reports/documentation of official sources; other parameters as the effect on selling for different areas and on the unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
+Concerning the first set, the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
+This choice is based on the idea that, if the PM act improperly, can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and than, if judged guilty, charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account.
 In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}.
@@
 This spillover translates in to more death and more ill people with respect to the baseline situation where there isn't an pandemic: however, by now, this effect is difficult to quantify and so we did not included in to the present model}.
+Among the different sectors affected by the pandemic and the consequent lock-down, we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories\footnote{The category Equipment for information technology/telephony and telecommunications was omitted since there is no point to argue that the lock-down affected, in reverse there it is more likely to argue that is increased due to the fact that people was forced to work remotely \cite{guo2020digitalization}}  \footnote{In the rest part of the paper these categories will be referred as the part of the name labelled in blue.
+}: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, \textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
+\textcolor{blue}{Appliances}/radios/televisions and tape recorders, \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware, \textcolor{blue}{Stationery products}/ books/ newspapers and magazines, \textcolor{blue}{Games}/toys/sports and camping articles.
+The choice to use the selling as a parameter for the evaluation of the lock-down lies on the fact that with them it is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa).
+Such calculation may be considered as a future outlook of this work}.
+Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods, \textcolor{blue}{Real estate} activities, rental, IT, research, business services\footnote{On contrary with respect to the category Equipment for information technology of selling, here the IT contribution is overwhelmed by the other ones (e.g Real Estate), making it negligible.
+Thus, in this case we included the whole sector}.
+In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down\footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
+Contrary with respect to the first wave, the lock-down did not banned by law the production.
+As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}.
+For the empirical evaluation of the impact on selling and unemployment benefit we performed a Difference-In-Difference where multiple times where considered as used in Refs.
+\cite{draca2011panic} and \cite{wooldridge2012introductory}.
+The following regression was performed:
+\begin{equation}
+Y_{outcome}=\alpha+\sum_{1}^{3}\beta_{i}T_{i}+\sum_{1}^{3}\delta_{i}(C \cdot T_{i})+\epsilon
+\end{equation}
+where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lockdown timing i, C a dummy for the treated group and $\epsilon$ a error term
 
@@
 \section{Results and Discussion}
+
+\newpage
 

### 2021-03-05 Manuscript/structure.tex
PUB

@@
 urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen, % Link colors
-pdftitle={}, % PDF title
-pdfauthor={\textcopyright}, % PDF Author
-pdfsubject={}, % PDF Subject
+pdftitle={The economic consequences of the different attitudes of a policy maker: a combined epidemiological-econometric study}, % PDF title
+pdfauthor={\textcopyright Marzio De Corato and Giulia Hadjiandrea}, % PDF Author
+pdfsubject={Project for Advanced Microeconomics Exam - DSE}, % PDF Subject
 pdfkeywords={}, % PDF Keywords

### 2021-03-07 Manuscript/manuscript.tex
PUB

@@
 \usepackage{hyperref}
+
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}.
-For the empirical evaluation of the impact on selling and unemployment benefit we performed a Difference-In-Difference where multiple times where considered as used in Refs.
+For the empirical evaluation of the impact on selling and unemployment benefit we performed a Difference-In-Difference (DID) where multiple times where considered as used in Refs.
 \cite{draca2011panic} and \cite{wooldridge2012introductory}.
@@
 \begin{equation}
-Y_{outcome}=\alpha+\sum_{1}^{3}\beta_{i}T_{i}+\sum_{1}^{3}\delta_{i}(C \cdot T_{i})+\epsilon
+Y_{outcome}=\alpha+\sum_{i=1}^{3}\beta_{i}T_{i}+\sum_{i=1}^{3}\delta_{i}(C \cdot T_{i})+\epsilon
+\label{DID-eq}
 \end{equation}
-where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lockdown timing i, C a dummy for the treated group and $\epsilon$ a error term
+where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  C a dummy for the treated group and $\epsilon$ a error term.
+[...].
+The DID considered  here has three different times for the lock-down:  for the sales we considered, as  done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as High lock-down and June 2020 as weak lock-down.
+On the other side  concerning the subsidies we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the subsidies for workers was slightly delayed with respect to effect lock-down effects on sales.
+Performing the DID we estimated the coefficients for the effect of each intensity of lock-down on sales and subsidies,  then we we rescaled them for a week (multiplying them by a factor of $\frac{7}{30})$.
+Finally we multiplied the number obtained from the previous calculation by the number of lock-down weeks, with the respective intensity,  in each scenario simulated via the epidemiological model described before.
+As consequence we obtained,  for each scenario, an economics simulation based on parameters obtained from an empirical evaluation.
 
@@
 
+The monthly sales data were take retrieved from the website of National Institute of Statistics \cite{istat}.
+In particular we considered the period starting from 2018 up to June 2020.
+The choice to not consider the month after June and in particular the last part of the year lies on the fact that in the latter the lock-down were imposed at regional level and not to national level \footnote{With the only exception of Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here,
+as far as the author knows, were not available,  at all for regional cluster.
+Moreover if regional cluster were considered it was necessary to model an ensemble of SIRD model that communicate each other with a defined rate (that change also with respect to the lock-down restriction).
+This make the model much more complicated.
+However if all the data that are necessary for performing the analysis will become availbale the author may consider, as an outlook, to extend the present analysis to regional clusters} As discussed in Supporting Information,  these data were not de-seasoned: thus we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
+Concerning the subsidies we retried the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+It is worth nothing that here we considered only the authorized subsidy and not the asked one.
+Furthermore these data,  differently with respect to the sales one were not affected by seasonality noise,  and thus no de-seasoning was necessary.
+
 \section{Results and Discussion}
+
+As done for the section Model and methods we will divide the discussion of the result in the following way: first the result of the economic model will be presented,  then on the basis of them we will discuss the  scenarios obtained with them via the epidemiological model.
+Finally we will discuss the overall results.
+
+\paragraph{DID}
+
+For each sales category we run the regression reported in the Eq.
+\ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots}:  the coefficients obtained are reported in Tab.
+As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
+As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.
+
+\paragraph{Scenarios}
+
+\paragraph{Conclusions}
+
+\begin{figure}
+     \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Abbigliamento.pdf}
+         \caption{ \textcolor{blue}{Clothing} (blue) }
+         \label{fig:y equals x}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Calzature.pdf}}
+         \caption{\textcolor{OliveGreen}{Footwear} (green)}
+         \label{fig:three sin x}
+     \end{subfigure}
+          \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Elettrodomestici.pdf}
+         \caption{ \textcolor{Orange}{Appliances} (orange)}
+         \label{fig:y equals x}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Fotoottica.pdf}}
+          \caption{\textcolor{Blue}{Photo-optics} (blue)}
+         \label{fig:three sin x}
+     \end{subfigure}
+          \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Mobili.pdf}}
+         \caption{\textcolor{Purple}{Household kinds} (purple)}
+         \label{fig:three sin x}
+     \end{subfigure}
+\caption{Selling data, with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+The timing for each lock-down is marked with a dashed line: red for high, orange medium and green for low.
+Note that despite there is a pre-trend this is negligible with respect to the slope of medium and high lock-down slopes}
+\label{Selling_plots}
+\end{figure}
 

### 2021-03-08 Manuscript/manuscript.tex
PUB

@@
 }: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, \textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
-\textcolor{blue}{Appliances}/radios/televisions and tape recorders, \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware, \textcolor{blue}{Stationery products}/ books/ newspapers and magazines, \textcolor{blue}{Games}/toys/sports and camping articles.
+\textcolor{blue}{Appliances}/radios/televisions and tape recorders, \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware,  \textcolor{blue}{Games}/toys/sports and camping articles.
 The choice to use the selling as a parameter for the evaluation of the lock-down lies on the fact that with them it is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa).
@@
 Thus, in this case we included the whole sector}.
-In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down\footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
+In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
 Contrary with respect to the first wave, the lock-down did not banned by law the production.
@@
 For each sales category we run the regression reported in the Eq.
-\ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots}:  the coefficients obtained are reported in Tab.
+\ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots} and \ref{Selling_plots_II}.
+The coefficients obtained are reported in Tab.
+\ref{selling_DID_table_delta}.
 As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
@@
      \end{subfigure}
-          \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{Figures/Mobili.pdf}}
-         \caption{\textcolor{Purple}{Household kinds} (purple)}
-         \label{fig:three sin x}
-     \end{subfigure}
-\caption{Selling data, with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+\caption{Selling data (I), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
 The timing for each lock-down is marked with a dashed line: red for high, orange medium and green for low.
@@
 
+\begin{figure}
+     \centering
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Mobili.pdf}}
+         \caption{\textcolor{OliveGreen}{Household kids} (Orchid)}
+         \label{fig:three sin x}
+     \end{subfigure}
+        \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Utilenseria.pdf}
+         \caption{ \textcolor{Orange}{Household tools} (Light green)}
+         \label{fig:y equals x}
+     \end{subfigure}
+             \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Giocattoli.pdf}
+         \caption{ \textcolor{Thistle}{Games} (Thistle)}
+         \label{fig:y equals x}
+     \end{subfigure}
+\caption{Selling data (II), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+The timing for each lock-down is marked with a dashed line: red for high, orange medium and green for low.
+Note that despite there is a pre-trend this is negligible with respect to the slope of medium and high lock-down slopes}
+\label{Selling_plots_II}
+\end{figure}
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
+The values of the  intercept ($\alpha$), C and T$_{i}$ are provided in the Supporting Info.
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
+{\color[HTML]{3531FF} Clothing}        & -60.07 & 2.77  & -21.64 & 40.16  & 2.01  & -19.99 & -16.45 & 2.77  & -5.92 \\ \hline
+{\color[HTML]{009901} Footwear}        & -65.78 & 2.39  & -27.49 & -20.62 & 1.73  & -22.35 & -20.62 & 2.39  & -8.62 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & -27.34 & 3.45  & -7.90  & -20.32 & 2.50  & -8.11  & -3.68  & 3.45  & 1.06  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & -52.32 & 3.52  & -14.84 & -34.14 & 2.55  & -13.38 & -7.86  & 3.52  & 2.23  \\ \hline
+{\color[HTML]{6200C9} Household kids}  & -18.99 & 2.07  & -9.13  & -10.51 & 1.50  & -6.98  & -3.61  & 2.07  & -1.74 \\ \hline
+{\color[HTML]{00D2CB} Household tools} & -30.23 & 4.85  & -6.23  & -13.02 & 3.51  & -3.70  & 2.33   & 4.85  & 0.48  \\ \hline
+{\color[HTML]{FFC9FD} Games}           & -30.23 & 4.85  & -6.22  & -13.02 & 3.51  & -3.70  & 2.33   & 4.85  & 0.48
+
+\end{tabular}
+\label{selling_DID_table_delta}
+\end{table}
+\end{landscape}
 \newpage

### 2021-03-08 Analisi_vendite/Test vari/DID_files/DID_code_dest.R

@@ -38,3 +38,35 @@ summary(Fotoottica)
 
 Fotoottica_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Fotoottica )
 summary(Fotoottica_placebo)
+
+
+Dati_Casalinghi <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Casalinghi")
+
+
+Casalinghi <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Casalinghi )
+summary(Casalinghi)
+
+Casalinghi_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Casalinghi )
+summary(Casalinghi_placebo)
+
+
+Dati_Utilenseria <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Utilenseria")
+
+
+Utilenseria <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Utilenseria )
+summary(Utilenseria)
+
+Utilenseria_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Utilenseria )
+summary(Utilenseria_placebo)
+
+
+Dati_Giocattoli <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Giocattoli")
+
+
+Giocattoli <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Utilenseria )
+summary(Giocattoli)
+
+Giocattoli_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Giocattoli )
+summary(Giocattoli_placebo)
+
+

### 2021-03-08 Analisi_vendite/Test vari/Plotter_destag.R

@@ -3,44 +3,58 @@ library(ggplot2)
 Data <- read_excel("Dati_destagionalizzati_FULL.xlsx")
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
-  labs(title="Abbigliamento")+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+theme_bw()
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Calzature),color = "darkgreen")+ 
-  labs(title="Calzature")+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+theme_bw()
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Elettrodomestici),color = "orange")+ 
-  labs(title="Elettrodomestici") +  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
[…]

### 2021-03-08 Manuscript/manuscript.tex
PUB

@@
 Such calculation may be considered as a future outlook of this work}.
-Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods, \textcolor{blue}{Real estate} activities, rental, IT, research, business services\footnote{On contrary with respect to the category Equipment for information technology of selling, here the IT contribution is overwhelmed by the other ones (e.g Real Estate), making it negligible.
-Thus, in this case we included the whole sector}.
+Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
 In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
@@
 As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.
+In order to make a further control,  a placebo test was performed by choosing timing before the pandemic of COVID19.
+As illustrated in the Supporting Info,  this test was successful.
+We than run the DID regression also for the subsidies: the plot of the data and the DID coefficients are reported in Fig \ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.
+Also in this case the placebo test were successfully performed.
 
@@
 \end{landscape}
+
+\begin{figure}
+     \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/CIG_Manifattura.pdf}
+         \caption{Subsidies paid for manufacture} 
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/CIG_Commercio.pdf}}
+         \caption{Subsidies paid for trade}
+     \end{subfigure}
+          \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/CIG_Costruzioni.pdf}
+         \caption{Construction}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/CIG_TOT.pdf}}
+          \caption{Total}
+     \end{subfigure}
+\caption{Comparison between the ordinary subsides (blue)   vs the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total.
+The dashed lines represent the different timing  and intensity for the lock-down:  red for high, orange medium and green for low.
+}
+\label{CIG_sector_plots}
+\end{figure}
+
+% Please add the following required packages to your document preamble:
+% \usepackage[table,xcdraw]{xcolor}
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\delta$ cofficients as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) according to equation \ref{DID-eq} \\ for the different lock-down timings.
+The values of the  intercept ($\alpha$), C and T$_{i}$ are provided in the Supporting Info.
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
+{\color[HTML]{343434} Total}        & 706    & 3     & 199.5  & 217    & 3     & 61.48 & 144    & 3     & 40.72 \\ \hline
+{\color[HTML]{343434} Manufacture}  & 494    & 3     & 158.56 & 162    & 3     & 52    & 111    & 3     & 35.7  \\ \hline
+{\color[HTML]{343434} Trade}        & 16.4   & 0.24  & 66.10  & 3.72   & 0.24  & 15.00 & 2.92   & 0.24  & 11.78 \\ \hline
+{\color[HTML]{343434} Construction} & 134    & 0.87  & 153.10 & 29     & 0.87  & 33.13 & 14     & 0.87  & 16.41 \\ \hline
+\label{CIG_DID}
+\end{tabular}
+\end{table}
+\end{landscape}
+
+\clearpage
 \newpage

### 2021-03-09 Manuscript/manuscript.tex
PUB

@@
 
-Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead), we considered a policy-maker (PM) that impose stochastically three types of lock-down with increasing force.
+Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead), we considered a policy-maker (PM) that impose stochastically two types of lock-down with increasing force.
 The probability by which the PM apply the lock-down reflects the different attitudes of a PM to face an epidemics (e.g.
@@
 Moreover here we also considered that there is not only an economic cost for each death, as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data), because a consistent part of them may be recovered or even should take the intensive therapy.
-In this paper three approaches were simulated that basically shape three different PM: a very careful one, a lazy one that adopts a \textit{laissez-faire} strategy and an intermediate one.
+In this paper three approaches were simulated that basically shape three different PM: a very careful one, and a lazy one that adopts a \textit{laissez-faire} strategy.
 For each scenario, we will discuss the result of the simulation and then we will compare them in order to get a general insight.
@@
 
-\paragraph{DID}
+\subsection{DID}
 
@@
 We than run the DID regression also for the subsidies: the plot of the data and the DID coefficients are reported in Fig \ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.
-Also in this case the placebo test were successfully performed.
+Also in this case the placebo tests were successfully performed.
 
@@
                                        & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
-{\color[HTML]{3531FF} Clothing}        & -60.07 & 2.77  & -21.64 & 40.16  & 2.01  & -19.99 & -16.45 & 2.77  & -5.92 \\ \hline
-{\color[HTML]{009901} Footwear}        & -65.78 & 2.39  & -27.49 & -20.62 & 1.73  & -22.35 & -20.62 & 2.39  & -8.62 \\ \hline
-{\color[HTML]{F56B00} Appliances}      & -27.34 & 3.45  & -7.90  & -20.32 & 2.50  & -8.11  & -3.68  & 3.45  & 1.06  \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & -52.32 & 3.52  & -14.84 & -34.14 & 2.55  & -13.38 & -7.86  & 3.52  & 2.23  \\ \hline
-{\color[HTML]{6200C9} Household kids}  & -18.99 & 2.07  & -9.13  & -10.51 & 1.50  & -6.98  & -3.61  & 2.07  & -1.74 \\ \hline
-{\color[HTML]{00D2CB} Household tools} & -30.23 & 4.85  & -6.23  & -13.02 & 3.51  & -3.70  & 2.33   & 4.85  & 0.48  \\ \hline
-{\color[HTML]{FFC9FD} Games}           & -30.23 & 4.85  & -6.22  & -13.02 & 3.51  & -3.70  & 2.33   & 4.85  & 0.48
+{\color[HTML]{3531FF} Clothing}        & -40.16  & 2.01  & -19.99 & -60.07 & 2.77  & -21.64 & -16.45 & 2.77  & -5.92 \\ \hline
+{\color[HTML]{009901} Footwear}        & -20.62 & 1.73  & -22.35 & -65.78 & 2.39  & -27.49 & -20.62 & 2.39  & -8.62 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & -20.32 & 2.50  & -8.11  & -27.34 & 3.45  & -7.90  & -3.68  & 3.45  & 1.06  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & -34.14 & 2.55  & -13.38 & -52.32 & 3.52  & -14.84 & -7.86  & 3.52  & 2.23  \\ \hline
+{\color[HTML]{6200C9} Household kids}   & -10.51 & 1.50  & -6.98  & -18.99 & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
+{\color[HTML]{00D2CB} Household tools} & -13.02 & 3.51  & -3.70 & -30.23 & 4.85  & -6.23    & 2.33   & 4.85  & 0.48  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & -27.55 & 3.47 & -7.93 & -64.31 &  4.79  & -13.40 & 0.26 &  4.79 & 0.05
 
@@
 \begin{flushleft}
-$\delta$ cofficients as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) according to equation \ref{DID-eq} \\ for the different lock-down timings.
+$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for the different lock-down timings.
 The values of the  intercept ($\alpha$), C and T$_{i}$ are provided in the Supporting Info.

### 2021-03-09 Analisi_cassa_integrazione/Cassa_integrazione.R

@@ -11,8 +11,8 @@ geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+
-ggtitle("Ore CIG COVID (ord) vs non COVID (str1) (str2) - Manifattura")+
-theme_bw() 
+  labs(y = "Hours Paid ")+ labs(x = "Time (months)")+
+theme_bw(base_size = 18) 
 
 Dati_cassa_integrazione_Manifattura_DID <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Manifattura_DID")
 
@@ -29,8 +29,8 @@ ggplot(data=Dati_cassa_integrazione_Commercio  ,aes(x=Time,y=CIG_S))+geom_line(s
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+
-  ggtitle("Ore CIG COVID (ord) vs non COVID (str1) (str2) - Commercio")+
-  theme_bw() 
+  labs(y = "Hours Paid ")+ labs(x = "Time (months)")+
+  theme_bw(base_size = 18) 
 
 Dati_cassa_integrazione_Commercio_DID <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Commercio_DID")
 
@@ -47,8 +47,8 @@ ggplot(data=Dati_cassa_integrazione_Costruzioni   ,aes(x=Time,y=CIG_S))+geom_lin
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+
-  ggtitle("Ore CIG COVID (ord) vs non COVID (str1) (str2) - Costruzioni ")+
-  theme_bw() 
+  labs(y = "Hours Paid ")+ labs(x = "Time (months)")+
+  theme_bw(base_size = 18) 
 
[…]

### 2021-03-09 Analisi_vendite/Test vari/DID_files/DID_code_dest.R

@@ -63,7 +63,7 @@ summary(Utilenseria_placebo)
 Dati_Giocattoli <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Giocattoli")
 
 
-Giocattoli <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Utilenseria )
+Giocattoli <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Giocattoli )
 summary(Giocattoli)
 
 Giocattoli_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Giocattoli )

### 2021-03-09 Project_script_Stochastic.R

@@ -18,8 +18,8 @@ colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
 #k<-c(1.5,1.5,1.5)
-k<-c(1,1,1)
-#k<-c(0.1,0.1,0.1)
+#k<-c(1,1,1)
+k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.000001
 rate_infection_threshold<-0.000007
 score<-0
@@ -196,6 +196,9 @@ selling_effect$P_value <- 2 * pt(abs(selling_effect$Effect/selling_effect$Effect
 selling_effect$High <- strong_lockdown_weeks
 selling_effect$Medium <- medium_lockdown_weeks
 selling_effect$Low <- soft_lockdown_weeks
+
+ggplot(selling_effect, aes(x=Type, y=Effect)) + geom_pointrange(aes(ymin=Effect-Effect_error, ymax=Effect+Effect_error,color = Type))+theme_bw(base_size = 18) + theme(legend.position = "none")+ coord_flip() +scale_color_manual(values=c('green','darkblue','orange','blue','palevioletred1','purple','cyan'))
+
 
 
 buffer %>%

### 2021-03-09 Manuscript/manuscript.tex
PUB

@@
 
+\section{Pictures and Tables}
+
 \begin{figure}
@@
 
+\begin{figure}
+     \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Epidemics_1_1_1.pdf}
+         \caption{Active PM} 
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Epidemics_1.5_1.5_1.5.pdf}}
+         \caption{Lazy PM}
+     \end{subfigure}
+\caption{Comparison between the epidemiological scenarios obtained via a SIRD model (Susceptible-Infectious-Recovered-Dead) where the PM impose stochastically the different levels of the lock-down.
+In the left panel an active PM is considered: this is modelled by making more likeable that the PM impose the lock-down as the number of infected goes over the different thresholds.
+On the contrary,  in the left panel a lazy PM that prefer the \textit{laissez-faire} approach is considered: in this case,  differently with respect to the previous scenario, the probability that the PM impose the lock-down  is less likely.
+}
+\label{CIG_sector_plots}
+\end{figure}
+
+\begin{figure}
+     \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Selling_Scenario_1_1_1.pdf}
+         \caption{Active PM} 
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Selling_Scenario_1.5_1.5_1.5.pdf}}
+         \caption{Lazy PM}
+     \end{subfigure}
+\caption{Comparison between the sales effects for the scenarios where an active vs lazy PM is considered.
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (divided by 4).
+The error bars were calculated by considering the error propagation  }
+\label{CIG_sector_plots}
+\end{figure}
+
+\begin{figure}
+     \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/CIG_effect_1_1_1.pdf}
+         \caption{Active PM} 
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/CIG_1.5_1.5_1.5.pdf}}
+         \caption{Lazy PM}
+     \end{subfigure}
+\caption{Comparison between the subsides effects for the scenarios where an active vs lazy PM is considered.
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (divided by 4).
+The error bars were calculated by considering the error propagation}
+\label{CIG_sector_plots}
+\end{figure}
+
 \clearpage

### 2021-03-09 Project_script_Stochastic.R

@@ -3,6 +3,7 @@ library(optimization)
 library(tidyverse)
 library(MASS)
 library(ggplot2)
+library(readxl)
 
 
 
@@ -14,12 +15,13 @@ no_lockdown_weeks<- 0
 lockdown_weeks<-0
 out<-data.frame(matrix(ncol = 5))
 selling_effect<-data.frame(matrix(ncol = 0,nrow=7))
+CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-#k<-c(1.5,1.5,1.5)
+k<-c(1.5,1.5,1.5)
 #k<-c(1,1,1)
-k<-c(0.1,0.1,0.1)
+#k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.000001
 rate_infection_threshold<-0.000007
 score<-0
@@ -36,6 +38,17 @@ load("DID_selling_matrix.rda")
 #as.data.frame(DID_selling_matrix_error)
 #save(DID_selling_matrix_error,file="DID_selling_matrix_error.rda")
 load("DID_selling_matrix_error.rda")
+
+
+#DID_CIG_matrix <- read_excel("Risultati/DID_CIG_matrix.xlsx")
+#as.data.frame(DID_CIG_matrix)
+#save(DID_CIG_matrix,file="DID_CIG_matrix.rda")
+load("DID_CIG_matrix.rda")
+
+#DID_CIG_matrix_error <- read_excel("Risultati/DID_CIG_matrix_error.xlsx")
+#as.data.frame(DID_CIG_matrix_error)
+#save(DID_CIG_matrix_error ,file="DID_CIG_matrix_error.rda")
+load("DID_CIG_matrix_error.rda")
 
 
 #p_vector <- runif(400, 0.000, 1.000)
@@ -190,8 +203,8 @@ score <- soft_lockdown_weeks+(1/7)+medium_lockdown_weeks*(1/0.25)+strong_lockdow
 score
 
 selling_effect$Type <- DID_selling_matrix$Type
-selling_effect$Effect <- DID_selling_matrix$High*strong_lockdown_weeks+DID_selling_matrix$Medium*medium_lockdown_weeks
[…]

### 2021-03-11 Manuscript/manuscript.tex
PUB

@@
 
-%\tableofcontents % Print the table of contents
-
 %\listoffigures % Print the list of figures%
@@
 
-\newpage % Start the article content on the second page, remove this if you have a longer abstract that goes onto the second page
+\newpage
 
@@
 I.Asimov, Prelude to foundation }
+
+\newpage
+
+\tableofcontents % Print the table of contents
+
+\newpage % Start the article content on the second page, remove this if you have a longer abstract that goes onto the second page
 
@@
 As illustrated in the Supporting Info,  this test was successful.
+By inspecting the Tab.
+\ref{selling_DID_table_delta} we see that the most severe damage of lock-down hit the clothing,  and the footwear.
+On the other side the Household kids and the Household tools seems lesser affected by the lock-down.
+
 We than run the DID regression also for the subsidies: the plot of the data and the DID coefficients are reported in Fig \ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.
@@
 
-\paragraph{Scenarios}
+\subsection{Scenarios}
+
+Now that we have the parameters for the economic impact given by the lock-downs,  we are ready to discuss the simulations that output the epidemiological and economic consequences of the attitude of PM.
+In Tab.
+\ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost}  the outcomes of the epidemiological model are given,  while the SIRD curves for the scenarios are provided in Fig.
+\ref{SIRD_scenario}; on the other side the effect on selling and subsidies for both scenarios are given in Fig.
+\ref{Selling_sector_effects} and \ref{CIG_sector_effects}.
+In order to assure the \textit{ceteris pariubus} condition we used for both scenario the same set of random number.
+First,  we see that where the PM is more reactive we have small different waves of epidemics,  while if the PM is poorly reactive only one intense wave is present (basically the standard wave of SIRD model).
+Since this change happens in a discontinuous way,  as the reactivity of the PM is changed,  we can consider this as a phase transition of a physical system.
+This explains our choice to consider only two scenarios: indeed we considered only a sample for each phase of the system.
+It is worth nothing that a similar result,  in a different epidemiological model,  was obtained by Balcan and Vespignani in Ref.
+\cite{Vespignani}.
+A possible explanation of this similar behaviour is that both model have a stochastic component,  that as pointed out by Balcan and Vespignani, give the phase transition: indeed while in their model this was directly related to the contagion probability,  here this is indirectly made stochastically by the decision of PM that modify the $\beta$ parameter and so the transmission rate.
+We see that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and infects by a consistent use of the confinement,  this obviously has it immediate drawback on the economic data: the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
+In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the author view this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
+For this reason here we considered the epidemiological consequences separated with respect to the economic ones  A more intriguing issue is where the economic cost is causally associated to an number indirect of deaths (for instance if people does not have the money for food or other first necessity goods ),  in this case the two factor (epidemiological and economic) can be,  in principle,  summed.
+We say in principle because the jurisprudence is here very reduced or totally missing since the pandemics are rare events.
+For the present study these indirect deaths are,  by now,  not easily to quantify and thus we did not considered this option.
 
@@
          \centering
-         \includegraphics[width=\textwidth]{Figures/Calzature.pdf}}
+         \includegraphics[width=\textwidth]{Figures/Calzature.pdf}
          \caption{\textcolor{OliveGreen}{Footwear} (green)}
@@
 }
-\label{CIG_sector_plots}
+\label{SIRD_scenario}
 \end{figure}
@@
 The error bars were calculated by considering the error propagation  }
-\label{CIG_sector_plots}
+\label{Selling_sector_effects}
 \end{figure}
@@
 The error bars were calculated by considering the error propagation}
-\label{CIG_sector_plots}
+\label{CIG_sector_effects}
 \end{figure}
+
+\begin{table}[]
+\begin{center}
+\caption{Comparison of epidemiological consequences for a reactive vs non-reactive PM with respect to the overcoming of the epidemiological thresholds.
+The values are reported as percentage with respect to the total population considered in the model (60 M) }
+\begin{tabular}{c|c|c}
+         & Active & Lazy  \\ \hline
+Deaths   & 0,06   & 6,50  \\ \hline
+Infected & 0,92   & 91,01 \\ \hline
+\label{Table_Epidemiological_effect}
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[]
+\begin{center}
+\caption{Cost associated with deaths and infected people that need to be assisted in terms of $10^{9}$ EUR.
+The  value of life correspond to the maximum compensation according to Milan court \cite{tribunaleMilano},  while the cost for infected people was taken from ANAC report \cite{Anac}}
+
+\begin{tabular}{c|c|c}
+         & Active & Lazy \\ \hline
+Deaths   & 11     & 1170 \\ \hline
+Infected & 15     & 1538 \\ \hline
+Total    & 26     & 2708 \\ \hline
+\label{Table_Epidemiological_cost}
+\end{tabular}
+\end{center}
+\end{table}
 

### 2021-03-11 Manuscript/manuscript.tex
PUB

@@
 
-Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead), we considered a policy-maker (PM) that impose stochastically two types of lock-down with increasing force.
-The probability by which the PM apply the lock-down reflects the different attitudes of a PM to face an epidemics (e.g.
-\textit{laissez-faire} vs very strict): thus depending on this probabilistic-parameter different scenario were simulated.
-For each of them we predicted a selected set of economic impacts by using parameters estimated via econometric techniques (Difference-in -Difference) on the microeconomic data of Italy.
-The comparison of the different impacts provide a bird's-eye view on the socio-economic consequences of the PM attitude
+Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically two types of lock-down with increasing force.
+The probability by which the PM applies the lock-down reflects his different attitude to face an epidemics (e.g.
+\textit{laissez-faire} vs very strict).
+We found that,  by modifying this parameter with continuity a phase transition (as defined for  a physical system) was obtained.
+For each phase we predicted a selected set of economic impacts (selling and subsidy) by using parameters estimated via econometric techniques (Difference-in -Difference) on the microeconomic data of Italy.
+The comparison of these two scenarios and their impact provide provide a bird's-eye view on the socio-economic consequences of the PM attitude
 
@@
 Differently from the pandemics of the past and in particular of the XX century (e.g.
-Spanish Flu, Asiatic Flu and Hong Kong Flu), for this pandemic a very large amount of data are easily accessible.
+Spanish Flu,  Asiatic Flu and Hong-Kong Flu),  for this pandemic a very large amount of data are easily accessible.
 As consequence not only the modelling of the virus diffusion,  but also the effect on socio-economic texture for the different countries can be investigated with a finer resolution.
-Among the different scientific challenges that can come up in this context, a interesting one involves the socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Infomation).
+Among the different scientific challenges that can come up in this context,  an interesting one involves the socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Information).
 Indeed the policy maker can adopt, at a first approximation,  a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
 In the first extreme,  the spread of virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods are stopped.
-On the other side, if no lock-down measures are taken by the policy-maker, the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
+On the other side,  if no lock-down measures are taken by the PM the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
 In practice the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion with respect to other (for this purpose a very fine analysis was provided by Li et al.
 in  \cite{li2021temporal} and by Brauner et al.
-in \cite{brauner2021inferring}): as consequence the lock-down efficacy, within certain limits, can be tuned.
+in \cite{brauner2021inferring}).
+As consequence the lock-down efficacy,  within certain limits,  can be tuned.
 In the literature different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.
@@
 On this basis we would propose here an alternative way to model the decision of the policy maker that is based on a stochastic model instead of on a deterministic one.
-Furthermore, differently with respect to the previous researches, that focused basically on macroeconomic impact, here we modelled the impact of the different lock-down at microeconomic level: in particular, by means of difference in difference, we evaluated the effect of the different levels of restrictions on the sales for different product types in Italy.
+Furthermore, differently with respect to the previous researches, that focused basically on macroeconomic impact,  here we modelled the impact of the different lock-down at microeconomic level: in particular,  by means of difference in difference,  we evaluated the effect of the different levels of lock-down on the sales for different product types in Italy.
 Thus the final output of the model will be not only the cumulative deaths,  but also the economic damage for each selling sector.
 Moreover here we also considered that there is not only an economic cost for each death,  as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data),  because a consistent part of them may be recovered or even should take the intensive therapy.
-In this paper three approaches were simulated that basically shape three different PM: a very careful one, and a lazy one that adopts a \textit{laissez-faire} strategy.
-For each scenario, we will discuss the result of the simulation and then we will compare them in order to get a general insight.
+As we will show by varying with continuity the probabilistic parameter by which the PM impose the lock-down,  a discontinuity in the SIRD model and in the days of the lock-down was obtained.
+Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.
+For each phase we will discuss the result of the simulation and then we will compare them in order to get a general insight.
 
@@
 Our choice is motivated by the fact that this relative simple model provide the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters.
-Thus, because the final goal of the present article is an insight on the effects of the PM care of pandemic, an not a fine grained description of the epidemics due to COVID-19, such model is suitable for our proposes\footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
+Thus,  because the final goal of the present article is an insight on the effects of the PM care of pandemic,  and not a fine grained description of the epidemics due to COVID-19,  such model is suitable for our proposes\footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
 in Ref.
@@
 Note that in this last case the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)}).
-The SIRD model,first proposed by Kermack and McKendrick \cite{kermack1927contribution}, is given by the following set of differential equations\cite{vynnycky2010introduction}:
+The SIRD model,first proposed by Kermack and McKendrick in 1927 \cite{kermack1927contribution},  is given by the following set of differential equations\cite{vynnycky2010introduction}:
 \begin{equation} 
@@
 where S is the number of people that are still susceptible,  I the number of people that are infected and R people that are recovered while D are people that are death.
-N denotes the total popolation, that for the timing considered here can be considered fixed \footnote{Othervise, if longer horizontal timing is considered, it is necessary to consider also a source term for the births and a well term for the natural deaths.
+N denotes the total population,  that for the timing of this paper,  it will be considered fixed \footnote{Othervise, if longer horizontal timing is considered,  it is necessary to consider also a source term for the births and a well term for the natural deaths.
 For further details see \cite{vynnycky2010introduction}}.
@@
 know as the basic reproduction factor.
-This number, that is the average number of people that are infected by a single individual, describe if the epidemic is in a negative feedback (R$_{0}$<1), stationary (R$_{0}$=1), or in a positive feedback (R$_{0}$>1).
+This number,  that is the average number of people that are infected by a single individual,  describes if the epidemic is in a negative feedback (R$_{0}$<1),  stationary (R$_{0}$=1),  or in a positive feedback (R$_{0}$>1).
 As consequence if the epidemic is in a negative feedback it will be going to dissipate,  if it is in positive feedback it will grow.
@@
 At the end of the simulation,  beside the values given by the standard SIRD model (recovered and deaths),  the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
+It is worth nothing that here as lock-down we considered only the national one that was applied in the first wave of the epidemics: from March 2020 to June 2020.
+This choice is motivated by the fact that modelling a unique system is more simpler with respect to modelling an ensemble of a communicating clusters that represent region or provinces: therefore,  if one is interested to model the second wave of pandemics such approach should be undertaken.
+Moreover in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at regional or province level,  and as far as the authors know, such data are not available.
+For these reasons here the modelling will be always referred to national data and national lock-downs,  therefore the period after June when starting from October regional lock-down were imposed,  will be not considered.
 
@@
 Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
-This choice is based on the idea that, if the PM act improperly, can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and than, if judged guilty, charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require a model in which also the age of people is keep into account.
+This choice is based on the idea that,  if the PM act improperly,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and than,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is keep into account.
 In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}.
-Beside this impact there is also the cost associated to the medical care of each ill people, for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that, in principle, there is also another import health-care impact due to the fact that the ill people for COVID-19 saturate the health system thus making it unreachable for other disease.
+Beside this impact, there is also the cost associated to the medical care of each ill people,  for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another import health-care impact due to the fact that the ill people for COVID-19 saturate the health system thus making it unreachable for other diseases.
 This spillover translates in to more death and more ill people with respect to the baseline situation where there isn't an pandemic: however,  by now,  this effect is difficult to quantify and so we did not included in to the present model}.
@@
 where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  C a dummy for the treated group and $\epsilon$ a error term.
-[...].
+As control group for the sales we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down \footnote{It is true that a slight increase of food consumption was done by people that were forced to stay at home as the plots in Fig.
+\ref{Selling_plots} \ref{Selling_plots_II} captures: however as proven numerically in the Supporting Info this change does not significantly affect the DID estimations } (note that in this selling also the one for the restaurants are included: thus,  if it is true that the restaurants were closed,  it is also true that people will purchase basically the same amount of food from the supermarket that they will consume into restaurant if these were opened).
+On the other side,  for subsidies \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
+This subsidy can be used by firms in order to reduce the working hours of employee by keeping part of the original salary.
+However,  during the first months of pandemic firms preferred (as it was indicated by Italian Government),  for reducing the daily hours worked,  to force employee to use holiday days in order to keep their salary constant.
+Thus  this particular subsidy can be considered as not treated by the first wave of the lock-down.
+On the contrary the Cassa Integrazione Ordinaria is largely affected by the lock-down since firms use this subsidy in order to reduce the monthly costs of employee (in particular when the holiday day of a worker were zero or negative).
 The DID considered here has three different times for the lock-down:  for the sales we considered, as  done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as High lock-down and June 2020 as weak lock-down.
@@
 As illustrated in the Supporting Info,  this test was successful.
+On the other side,  concerning $T_{3}$ only the effect for clothing and footwear can be considered significant,  also by considering the pre-trend slope as discussed in the Supporting Information.
+Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations, only the clothing and footwear sectors.
 By inspecting the Tab.
@@
 On the other side the Household kids and the Household tools seems lesser affected by the lock-down.
-
-We than run the DID regression also for the subsidies: the plot of the data and the DID coefficients are reported in Fig \ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.
+The same DID regression was used  for the subsidies,  using as control group the extraordinary solidarity subsidies (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
+\ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.
 Also in this case the placebo tests were successfully performed.
+An interesting insight is also provided by the inspection of the extraordinary subsidies for renovation ( \textit{cassa integrazione ristrutturazione}): these subsidies,  as compared to the solidarity ones,  seems much more sensitive with respect to external shock in particular for trade sector
 
@@
 Since this change happens in a discontinuous way,  as the reactivity of the PM is changed,  we can consider this as a phase transition of a physical system.
-This explains our choice to consider only two scenarios: indeed we considered only a sample for each phase of the system.
-It is worth nothing that a similar result,  in a different epidemiological model,  was obtained by Balcan and Vespignani in Ref.
+This explains our choice to consider only two scenarios: indeed we considered only a sample for each phase.
+It is worth nothing that a similar result,  within a different epidemiological model,  was obtained by Balcan and Vespignani in Ref.
 \cite{Vespignani}.
@@
 We see that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and infects by a consistent use of the confinement,  this obviously has it immediate drawback on the economic data: the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
-In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the author view this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
+In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the authors view this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation, the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
 For this reason here we considered the epidemiological consequences separated with respect to the economic ones  A more intriguing issue is where the economic cost is causally associated to an number indirect of deaths (for instance if people does not have the money for food or other first necessity goods ),  in this case the two factor (epidemiological and economic) can be,  in principle,  summed.

### 2021-03-11 Project_script_Stochastic.R
PUB

@@ -19,7 +19,8 @@ CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-k<-c(1.5,1.5,1.5)
+#k<-c(1.5,1.5,1.5)
+k<-c(0.9,0.9,0.9)
 #k<-c(1,1,1)
 #k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.000001

### 2021-03-11 Risultati/Phase_transition_diagram.R

@@ -1,0 +1,5 @@
+library(readxl)
+library(ggplot2)
+
+Phase_transition <- read_excel("Risultati/Phase_transition.xlsx")
+ggplot(Phase_transition,aes(x=PM_attitute, y=Deaths),size=2,color = "red") + geom_line(color="red") +   geom_point(color="red") + labs(y = "Death ")+ labs(x = "PM attitute")+ theme_bw(base_size = 18) 

### 2021-03-12 Manuscript/manuscript.tex
PUB

@@
 
-\title{\normalfont\spacedallcaps{The economic consequences of the different attitudes of a policy maker: a combined epidemiological-econometric study}} % The article title
+\title{\normalfont\spacedallcaps{The economic consequences of different attitudes of a policy maker: a combined epidemiological-econometric study}} % The article title
 
@@
 
+\newpage
+
+{\centering
+\includegraphics[width=0.5\textwidth]{Phase_transition.pdf}
+\par
+}
+
 \section*{Abstract} % This section will not appear in the table of contents due to the star (\section*)
@@
 
-The recent pandemic due to the spread of SARS-CoV-2 virus,  opened a highly debated issue about what it would be the best approach of the policy maker to face the epidemics.
-Differently from the pandemics of the past and in particular of the XX century (e.g.
+The recent pandemic due to the spread of SARS-CoV-2 virus,  opened a highly debated issue about what it would be the best approach of the policy maker to face the epidemic.
+Differently from the past pandemics and in particular of the XX century (e.g.
 Spanish Flu,  Asiatic Flu and Hong-Kong Flu),  for this pandemic a very large amount of data are easily accessible.
-As consequence not only the modelling of the virus diffusion,  but also the effect on socio-economic texture for the different countries can be investigated with a finer resolution.
-Among the different scientific challenges that can come up in this context,  an interesting one involves the socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Information).
+As a consequence not only the modelling of the virus diffusion but also the effect on socio-economic texture for different countries can be investigated with a finer resolution.
+Among the different scientific challenges that can come up in this context,  an interesting one involves socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Information).
 Indeed the policy maker can adopt, at a first approximation,  a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
 In the first extreme,  the spread of virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods are stopped.
-On the other side,  if no lock-down measures are taken by the PM the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
+On the other side,  if no lock-down measures are taken by the PM the toll to be paid will not only be the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
 In practice the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion with respect to other (for this purpose a very fine analysis was provided by Li et al.
@@
 In particular for the model in Ref.
-\cite{kabir2020evolutionary} it is assumed that the policy-maker know perfectly the consequences of her choices and that she can act without delay to impose the optimal choice; finally it is assumed that the PM can impose a continuous factor for the lock-down, while, for different countries such factor seems to be much more discrete.
+\cite{kabir2020evolutionary} it is assumed that the policy-maker knows perfectly the consequences of his/her choices and that he/she can act without delay to impose the optimal choice; finally it is assumed that the PM can impose a continuous factor for the lock-down while for different countries such factor seems to be much more discrete.
 It can be argued that most of these drawbacks of this last formidable research, are entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy maker.
 On this basis we would propose here an alternative way to model the decision of the policy maker that is based on a stochastic model instead of on a deterministic one.
-Furthermore, differently with respect to the previous researches, that focused basically on macroeconomic impact,  here we modelled the impact of the different lock-down at microeconomic level: in particular,  by means of difference in difference,  we evaluated the effect of the different levels of lock-down on the sales for different product types in Italy.
+Furthermore, differently with respect to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-down at microeconomic level: in particular,  by means of difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
 Thus the final output of the model will be not only the cumulative deaths,  but also the economic damage for each selling sector.
-Moreover here we also considered that there is not only an economic cost for each death,  as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data),  because a consistent part of them may be recovered or even should take the intensive therapy.
+Moreover here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data),  because a consistent part of them may be recovered or even should take the intensive therapy.
 As we will show by varying with continuity the probabilistic parameter by which the PM impose the lock-down,  a discontinuity in the SIRD model and in the days of the lock-down was obtained.
@@
 
-The model of the present study is composed by an epidemiological part,  that shapes the diffusion of the virus, and then its output is used by the economic model to quantify the damage.
+The model of the present study is composed by an epidemiological part that shapes the diffusion of the virus and then its output is used by the economic model to quantify the damage.
 Thus we will discuss the epidemiological part and then the economic one
@@
 
-Among the very large number of compartmental model that are available in the literature \cite{vynnycky2010introduction},  we considered as the simulator of the epidemic diffusion the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
-Our choice is motivated by the fact that this relative simple model provide the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters.
-Thus,  because the final goal of the present article is an insight on the effects of the PM care of pandemic,  and not a fine grained description of the epidemics due to COVID-19,  such model is suitable for our proposes\footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
+Among the very large number of compartmental model available in the literature \cite{vynnycky2010introduction} we considered, as the simulator of the epidemic diffusion the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
+Our choice is motivated by the fact that this relative simple model provides the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters \footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
 in Ref.
@@
 \end{equation}
-know as the basic reproduction factor.
-This number,  that is the average number of people that are infected by a single individual,  describes if the epidemic is in a negative feedback (R$_{0}$<1),  stationary (R$_{0}$=1),  or in a positive feedback (R$_{0}$>1).
-As consequence if the epidemic is in a negative feedback it will be going to dissipate,  if it is in positive feedback it will grow.
-Note that in this simple model since the parameters are not time dependent this factor is constant.
-If,  as performed by Ferrari et al.
-\cite{ferrari2020modelling},  time dependent parameters are considered a time depended parameter called $R_{t}$.
+known as the basic reproduction factor.
+This number is the average number of people that are infected by a single individual and describes if the epidemic is in a negative feedback (R$_{0}$<1),  stationary (R$_{0}$=1),  or in a positive feedback (R$_{0}$>1).
+As consequence if the epidemic is in a negative feedback will be dissipate, while if it is in positive feedback will grow.
+Note that in this simple model, since the parameters are not time dependent this factor is constant.
+As performed by Ferrari et al.
+\cite{ferrari2020modelling} time dependent parameters are considered a time depended parameter called $R_{t}$.
 For the present work,  we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
 The overall population $N$ was set to 60M,  in order to simulate Italian population.
-Within the daily temporal evolution of this model, that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package,  we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$,  if the normalized infected people are more than 10 the previous threshold  she will impose,  with a certain probability, restrictions that multiply the $\beta$ starting $\beta$ factor by $0.25$,  finally if the  threshold is exceeded more than 50 times the PM will impose with a certain probability restrictive measures that multiply the $\beta$ by $0.025$.
-These attenuation parameters were adjusted taking in consideration the results of Marziano et al.
+Within the daily temporal evolution of this model,  that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package,  we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$,  if the normalized infected people are more than 10 the previous threshold he/she will impose with a certain probability restrictions that multiply $\beta$ starting $\beta$ factor by $0.25$;  finally,  if the  threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that multiply $\beta$ by $0.025$.
+These attenuation parameters were adjusted taking in consideration results of Marziano et al.
 in Ref.
 \cite{marziano2021retrospective}.
-As we said the PM act with a certain probability, more formally stochastically: each week a random number (from zero to one) is extracted,  if this is higher than a certain threshold, the relative restrictive decision is taken, otherwise not.
-The threshold value capture the PM attitude to impose the lock-down: lower values model a careful PM,  hight value a lazy one.
+As we said the PM acts with a certain probability, more formally stochastically: each week a random number (from zero to one) is extracted: if this is higher than a certain threshold, the relative restrictive decision is taken, otherwise not.
+The threshold value captures the PM attitude to impose the lock-down: lower values model a careful PM,  hight value a lazy one.
 In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results.
@@
 
-The economic impact for each epidemiological scenario is shaped as follow: a first set of parameters,  as the economic value of a death and of being infected by COVID-19 ,was taken directly from the reports/documentation of official sources; other parameters as the effect on selling for different areas and on the unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
+The economic impact for each epidemiological scenario is shaped as follow: a first set of parameters,  as the economic value of a death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on selling for different areas and on the unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
 Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
-This choice is based on the idea that,  if the PM act improperly,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and than,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is keep into account.
+This choice is based on the idea that,  if the PM acts improperly,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and than,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is keep into account.
 In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}.
@@
 This spillover translates in to more death and more ill people with respect to the baseline situation where there isn't an pandemic: however,  by now,  this effect is difficult to quantify and so we did not included in to the present model}.
-Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories\footnote{The category Equipment for information technology/telephony and telecommunications was omitted since there is no point to argue that the lock-down affected, in reverse there it is more likely to argue that is increased due to the fact that people was forced to work remotely \cite{guo2020digitalization}}  \footnote{In the rest part of the paper these categories will be referred as the part of the name labelled in blue.
-}: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, \textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
-\textcolor{blue}{Appliances}/radios/televisions and tape recorders, \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware,  \textcolor{blue}{Games}/toys/sports and camping articles.
-The choice to use the selling as a parameter for the evaluation of the lock-down lies on the fact that with them it is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa).
+Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper these categories will be referred as the part of the name labelled in blue.
+}: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, \textcolor{blue}{Appliances}/radios/televisions and
+tape recorders,\textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
+\textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware,  \textcolor{blue}{Games}/toys/sports and camping articles.
+The choice to use sales as a parameter for the evaluation of the lock-down lies on the fact that with them  is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa).
 Such calculation may be considered as a future outlook of this work}.
 Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
-In this case the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them the production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
+In this case, the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
 Contrary with respect to the first wave, the lock-down did not banned by law the production.
 As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}.
-For the empirical evaluation of the impact on selling and unemployment benefit we performed a Difference-In-Difference (DID) where multiple times where considered as used in Refs.
+For the empirical evaluation of the impact on selling and unemployment benefit we performed a multiple time Difference in Difference as used in Refs.
 \cite{draca2011panic} and \cite{wooldridge2012introductory}.
@@
 where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  C a dummy for the treated group and $\epsilon$ a error term.
-As control group for the sales we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down \footnote{It is true that a slight increase of food consumption was done by people that were forced to stay at home as the plots in Fig.
+As control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down \footnote{It is true that a slight increase of food consumption was done by people that were forced to stay at home as the plots in Fig.
 \ref{Selling_plots} \ref{Selling_plots_II} captures: however as proven numerically in the Supporting Info this change does not significantly affect the DID estimations } (note that in this selling also the one for the restaurants are included: thus,  if it is true that the restaurants were closed,  it is also true that people will purchase basically the same amount of food from the supermarket that they will consume into restaurant if these were opened).
 On the other side,  for subsidies \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
-This subsidy can be used by firms in order to reduce the working hours of employee by keeping part of the original salary.
-However,  during the first months of pandemic firms preferred (as it was indicated by Italian Government),  for reducing the daily hours worked,  to force employee to use holiday days in order to keep their salary constant.
-Thus  this particular subsidy can be considered as not treated by the first wave of the lock-down.
-On the contrary the Cassa Integrazione Ordinaria is largely affected by the lock-down since firms use this subsidy in order to reduce the monthly costs of employee (in particular when the holiday day of a worker were zero or negative).
-The DID considered here has three different times for the lock-down:  for the sales we considered, as  done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as High lock-down and June 2020 as weak lock-down.
-On the other side  concerning the subsidies we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the subsidies for workers was slightly delayed with respect to effect lock-down effects on sales.
-Performing the DID we estimated the coefficients for the effect of each intensity of lock-down on sales and subsidies,  then we we rescaled them for a week (multiplying them by a factor of $\frac{7}{30})$.
+This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labour cost but at same time guaranteeing to the workers part of their original salary.
+During the first months of the pandemic firms,  following the rules stated by the Italian Governament (Decreto Cura Italia \cite{curaitalia}),  firms that would reduce their labour cost,  first forced the employees to use their holiday budget and than,  after it was run out,  they put the employees in to the Cassa Integrazione Ordinaria.
+Thus the Cassa Integrazione Straordinaria-Solidarietà can be considered as not treated by the first wave of the lock-down while the ordinary one the treated.
+The DID considered here has three different times for the national lock-down:  for the sales we considered,  as  done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down and June 2020 as weak lock-down.
+On the other side concerning the subsidies,  we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the subsidies for workers was slightly delayed basically due to the fact that firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as consequence,  because of this buffer effect, in the month of March there is no significant effect of this subsidies although there is a significant reduction of hours worked (see e.g.
+\cite{istat_lavoro}).
+Performing the DID we estimated the coefficients for the effect of each intensity of lock-down on sales and subsidies,  then we we rescaled them for a week.
 Finally we multiplied the number obtained from the previous calculation by the number of lock-down weeks,  with the respective intensity,  in each scenario simulated via the epidemiological model described before.
@@
 In particular we considered the period starting from 2018 up to June 2020.
-The choice to not consider the month after June and in particular the last part of the year lies on the fact that in the latter the lock-down were imposed at regional level and not to national level \footnote{With the only exception of Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here,
-as far as the author knows, were not available,  at all for regional cluster.
+The choice to not consider the months after June and in particular the last part of the year lies on the fact that in the latter the lock-down were imposed at regional level and not to national level \footnote{With the only exception of Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for regional cluster.
 Moreover if regional cluster were considered it was necessary to model an ensemble of SIRD model that communicate each other with a defined rate (that change also with respect to the lock-down restriction).
 This make the model much more complicated.
-However if all the data that are necessary for performing the analysis will become availbale the author may consider, as an outlook, to extend the present analysis to regional clusters} As discussed in Supporting Information,  these data were not de-seasoned: thus we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
+However if all the data that are necessary for performing the analysis will become available the author may consider, as an outlook, to extend the present analysis to regional clusters}.
+As discussed in Supporting Information,  these data were not de-seasoned: thus we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
 Concerning the subsidies we retried the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
@@
 Furthermore these data,  differently with respect to the sales one were not affected by seasonality noise,  and thus no de-seasoning was necessary.
+We checked also if any significant effect on DID coefficient was obtained for sales and for subsidies by adding one and two year before 2018 (e.g.
+2016 and 2017): no significant effect was found.
 
@@
 
-As done for the section Model and methods we will divide the discussion of the result in the following way: first the result of the economic model will be presented,  then on the basis of them we will discuss the  scenarios obtained with them via the epidemiological model.
+As done for the section Model and methods we will divide the discussion of the results in the following way: first the outcomes of the economic model will be presented,  then on the basis of them,  we will discuss the  scenarios obtained with them via the epidemiological model.
 Finally we will discuss the overall results.
@@
 As illustrated in the Supporting Info,  this test was successful.
-On the other side,  concerning $T_{3}$ only the effect for clothing and footwear can be considered significant,  also by considering the pre-trend slope as discussed in the Supporting Information.
+On the other side,  concerning $T_{3}$  (low lock-down), only the effect for clothing and footwear can be considered significant,  also by considering the pre-trend slope as discussed in the Supporting Information.
 Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations,  only the clothing and footwear sectors.
@@
 Also in this case the placebo tests were successfully performed.
-An interesting insight is also provided by the inspection of the extraordinary subsidies for renovation ( \textit{cassa integrazione ristrutturazione}): these subsidies,  as compared to the solidarity ones,  seems much more sensitive with respect to external shock in particular for trade sector
+An interesting insight is also provided by the inspection of the extraordinary subsidies for renovation ( \textit{cassa integrazione ristrutturazione}): these subsidies,  as compared to the solidarity ones,  seems much more sensitive with respect to external shock in particular for trade sector.
 
@@
 \ref{Selling_sector_effects} and \ref{CIG_sector_effects}.
-In order to assure the \textit{ceteris pariubus} condition we used for both scenario the same set of random number.
+In order to assure the \textit{ceteris pariubus} condition we used for both scenario the same set of random numbers.
 First,  we see that where the PM is more reactive we have small different waves of epidemics,  while if the PM is poorly reactive only one intense wave is present (basically the standard wave of SIRD model).
-Since this change happens in a discontinuous way,  as the reactivity of the PM is changed,  we can consider this as a phase transition of a physical system.
+Since this change happens in a discontinuous way as showed in Fig.
+\ref{Phase_transition},   as the reactivity of the PM is changed,  we can consider this as a phase transition of a physical system (it is interesting to point out the closness with respect to the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
 This explains our choice to consider only two scenarios: indeed we considered only a sample for each phase.
@@
 \cite{Vespignani}.
-A possible explanation of this similar behaviour is that both model have a stochastic component,  that as pointed out by Balcan and Vespignani,  give the phase transition: indeed while in their model this was directly related to the contagion probability,  here this is indirectly made stochastically by the decision of PM that modify the $\beta$ parameter and so the transmission rate.
-We see that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and infects by a consistent use of the confinement,  this obviously has it immediate drawback on the economic data: the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
-In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the authors view this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation, the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
-For this reason here we considered the epidemiological consequences separated with respect to the economic ones  A more intriguing issue is where the economic cost is causally associated to an number indirect of deaths (for instance if people does not have the money for food or other first necessity goods ),  in this case the two factor (epidemiological and economic) can be,  in principle,  summed.
+The explanation of this similar behaviour is that both model have a stochastic component,  that as pointed out by Balcan and Vespignani,  give the phase transition: indeed while in their model this was directly related to the contagion probability,  here this is indirectly made stochastically by the decision of PM that modify the $\beta$ parameter and so the transmission rate.
+We see that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by a consistent use of the confinement.
+This has it immediate drawback on the economic data: the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
+In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation, the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
+For this reason here we considered the epidemiological consequences separated with respect to the economic ones.
+A more intriguing issue is come up when the economic cost is causally associated to an number indirect of deaths (for instance if people does not have the money for food or other first necessity goods ),  in this case the two factor (epidemiological and economic) can be,  in principle,  summed.
 We say in principle because the jurisprudence is here very reduced or totally missing since the pandemics are rare events.
@@
 
-\paragraph{Conclusions}
+\section{Conclusions}
+
+We have obtained a model that combines the epidemiological aspects as well the economic ones within a stochastic approach.
+This was made possible by evaluating the causal effect of lock-downs, via a DID regression,  on different sales sector as well on the subsidies dedicated to firms that would reduce the labour cost.
+Furthermore we show numerically that,  within a stochastic approach,  the PM attitude to impose the lock-downs is critical,  as this attitude,  within a \textit{ceteris paribus} condition,  decide the phase of the outcome scenario and thus the economic and social effects.
 
@@
 \label{CIG_sector_plots}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Phase_transition.pdf}
+\caption{The number of deaths of SIRD scenario with stochasic lockdown as obtained by chaing the PM attitute to active the lockdown (e.g.
+by modifying the probability parameter by which the lock-down is imposed).
+As the PM attitude is near 1.3 a sharp discontinuity is present in the overall death: thus a different phase is obtained.
+It is worth nothing the similarity of this plot with the gold-standard one of phase transition: the Ising model (see \cite{Ising} or \cite{Ising_2} for a more deep analysis)}
+\label{Phase_transition}
 \end{figure}

### 2021-03-12 Manuscript/manuscript.tex
PUB

@@
 
-\newpage
-
-{\centering
-\includegraphics[width=0.5\textwidth]{Phase_transition.pdf}
-\par
-}
-
 \section*{Abstract} % This section will not appear in the table of contents due to the star (\section*)
@@
 On this basis we would propose here an alternative way to model the decision of the policy maker that is based on a stochastic model instead of on a deterministic one.
-Furthermore, differently with respect to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-down at microeconomic level: in particular,  by means of difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
-Thus the final output of the model will be not only the cumulative deaths,  but also the economic damage for each selling sector.
+Furthermore,  differently with respect to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at microeconomic level: in particular,  by means of difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
+Thus, the final output of the model will be not only the cumulative deaths,  but also the economic damage for each selling sector.
 Moreover here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data),  because a consistent part of them may be recovered or even should take the intensive therapy.
@@
 It is worth nothing that here as lock-down we considered only the national one that was applied in the first wave of the epidemics: from March 2020 to June 2020.
-This choice is motivated by the fact that modelling a unique system is more simpler with respect to modelling an ensemble of a communicating clusters that represent region or provinces: therefore,  if one is interested to model the second wave of pandemics such approach should be undertaken.
+This choice is motivated by the fact that modelling a unique system is more simpler with respect to modelling an ensemble of a communicating clusters that represent regions or provinces: therefore,  if one is interested to model the second wave of pandemics such approach should be undertaken.
 Moreover in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at regional or province level,  and as far as the authors know,  such data are not available.
@@
 As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}.
-For the empirical evaluation of the impact on selling and unemployment benefit we performed a multiple time Difference in Difference as used in Refs.
-\cite{draca2011panic} and \cite{wooldridge2012introductory}.
+For the empirical evaluation of the impact on selling and unemployment benefit we performed a multiple time Difference in Difference as presented in Refs.
+\cite{draca2011panic},  \cite{imbens2009recent} and \cite{wooldridge2012introductory}.
 The following regression was performed:
@@
 
-The monthly sales data were take retrieved from the website of National Institute of Statistics \cite{istat}.
+The monthly sales data were retrieved from the National Institute of Statistics website \cite{istat}.
 In particular we considered the period starting from 2018 up to June 2020.
-The choice to not consider the months after June and in particular the last part of the year lies on the fact that in the latter the lock-down were imposed at regional level and not to national level \footnote{With the only exception of Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for regional cluster.
+The choice to not consider the months after June and in particular the last part of the year lies on the fact that in the latter lock-downs were imposed at regional level and not to national level \footnote{With the only exception of Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for regional cluster.
 Moreover if regional cluster were considered it was necessary to model an ensemble of SIRD model that communicate each other with a defined rate (that change also with respect to the lock-down restriction).
@@
 As discussed in Supporting Information,  these data were not de-seasoned: thus we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
-Concerning the subsidies we retried the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
-It is worth nothing that here we considered only the authorized subsidy and not the asked one.
+Concerning subsidies we retried the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+It is worth nothing that here we considered only the authorized subsidies and not the asked one .
 Furthermore these data,  differently with respect to the sales one were not affected by seasonality noise,  and thus no de-seasoning was necessary.
@@
 
-As done for the section Model and methods we will divide the discussion of the results in the following way: first the outcomes of the economic model will be presented,  then on the basis of them,  we will discuss the  scenarios obtained with them via the epidemiological model.
+As done for the section Model and methods we will divide the discussion of the results in the following way: first the outcomes of the economic model will be presented,  then basing on this result,  we will discuss the  scenarios obtained with them via the epidemiological model.
 Finally we will discuss the overall results.
@@
 This has it immediate drawback on the economic data: the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
+A deeper inspection on the reproduction number for both scenarios provide a further insight about these two very different outcomes:  as shown in Fig.
+\ref{R_t_scenarios}  the reactivity PM basically stabilize the reproduction number in to its value of a medium lock-down,  on the contrary the inactivity of the PM to set the lock-downs make the epidemic to be almost out of control since it the reproduction factor basically remain (with an exception of an intermediate spike) at it maximum level.
+The Fig.
+\ref{R_t_scenarios} can be also used to see the number of weeks elapsed for each lock-down intensity.
 In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation,  the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
@@
 We have obtained a model that combines the epidemiological aspects as well the economic ones within a stochastic approach.
-This was made possible by evaluating the causal effect of lock-downs, via a DID regression,  on different sales sector as well on the subsidies dedicated to firms that would reduce the labour cost.
+This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales sector as well on the subsidies dedicated to firms that would reduce the labour cost.
 Furthermore we show numerically that,  within a stochastic approach,  the PM attitude to impose the lock-downs is critical,  as this attitude,  within a \textit{ceteris paribus} condition,  decide the phase of the outcome scenario and thus the economic and social effects.
+
+\clearall
+\newpage
 
@@
  \centering
- \includegraphics[width=\textwidth]{Figures/Phase_transition.pdf}
+ \includegraphics[width=0.5\textwidth]{Figures/Phase_transition.pdf}
 \caption{The number of deaths of SIRD scenario with stochasic lockdown as obtained by chaing the PM attitute to active the lockdown (e.g.
@@
 \label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+     \centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/R_t_1_1_1.pdf}
+         \caption{Active PM} 
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/R_t_1.5_1.5_1.5.pdf}}
+         \caption{Lazy PM}
+     \end{subfigure}
+\caption{Comparison between the reproduction number (calculated as effective the $\frac{\beta}{\gamma}$ ratio when the lock-down is applied) for a highly reactive PM vs to the one of a poorly reactive one.
+It can be noted that while in the former the PM reactivity almost allows him/her to control this factor in to a stable medium lock-down,  in the second one the reproduction number (and thus the epidemic) is almost out of control of the PM since it remains,  for most of weeks at its maximum level.
+Note that the levels of reproduction number are discrete, as marked by the dashed lines (green low,  orange medium,  red high) since the lock-down is the only way to change this number.
+On the contrary if a time dependent SIRD was considered as done by \cite{ferrari2020modelling},  a continuous form of R(t) would be obtained}
+\label{R_t_scenarios}
 \end{figure}
@@
      \centering
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}{0.45\textwidth}
          \centering     
@@
      \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}{0.45\textwidth}
          \centering

### 2021-03-12 Project_script_Stochastic.R

@@ -19,11 +19,11 @@ CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-#k<-c(1.5,1.5,1.5)
-k<-c(0.9,0.9,0.9)
 #k<-c(1,1,1)
+#k<-c(0.9,0.9,0.9)
+k<-c(1.5,1.5,1.5)
 #k<-c(0.1,0.1,0.1)
-#rate_infection_threshold<-0.000001
+#rate_infection_threshold<-0.00000007
 rate_infection_threshold<-0.000007
 score<-0
 p_vector<-numeric(400)
@@ -238,4 +238,10 @@ buffer %>%
 #  scale_y_log10() +
   labs(x='time (days)',y='Log number of individuals')
 
+#R_t<-as.data.frame(R_t)
 
+A<-data.frame(1:52)
+A$Value<-as.data.frame(R_t)
+
+
+ggplot(A,aes(y=R_t,x=X1.52),size=2,color = "blue") + geom_line(color="blue") +   geom_point(color="blue") + labs(y = " R(t)")+ labs(x = "Weeks")+ geom_hline(yintercept=0.2857,linetype="dashed", color = "orange", size=0.5)+geom_point(color="blue") + labs(y = " R(t)")+ labs(x = "Weeks")+ geom_hline(yintercept=1.4285,linetype="dashed", color = "red", size=0.5)+ geom_hline(yintercept=0.1428,linetype="dashed", color = "green", size=0.5)+theme_bw(base_size = 18) 

### 2021-03-12 Analisi_vendite/Test vari/DID_files/DID_code_dest.R
PUB

@@ -1,30 +1,40 @@
 library(readxl)
 
 Dati_Abbigliamento <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Abbigliamento")
+Dati_Abbigliamento_phantom <- read_excel("Dati_destagionalizzati_DID_phantom.xlsx", sheet = "Abbigliamento")
 
 
 Abbigliamento <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Abbigliamento )
 summary(Abbigliamento)
+
+Abbigliamento_phantom <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Abbigliamento_phantom )
+summary(Abbigliamento_phantom)
 
 Abbigliamento_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Abbigliamento )
 summary(Abbigliamento_placebo)
 
 
 Dati_Calzature <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Calzature")
-
+Dati_Calzature_phantom <- read_excel("Dati_destagionalizzati_DID_phantom.xlsx", sheet = "Calzature")
 
 Calzature <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Calzature)
 summary(Calzature)
+
+Calzature_phantom <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Calzature_phantom)
+summary(Calzature_phantom)
 
 Calzature_placebo <-lm(Outcome ~  C + T4 + T5+T6 + C*T4 +C*T5+C*T6, data = Dati_Calzature )
 summary(Calzature_placebo)
 
 
 Dati_Elettrodomestici <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Elettrodomestici")
-
+Dati_Elettrodomestici_phantom <- read_excel("Dati_destagionalizzati_DID_phantom.xlsx", sheet = "Elettrodomestici")
 
 Elettrodomestici <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Elettrodomestici)
 summary(Elettrodomestici)
+
[…]

### 2021-03-12 Project_script_Stochastic.R
PUB

@@ -19,9 +19,9 @@ CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-#k<-c(1,1,1)
+k<-c(1,1,1)
 #k<-c(0.9,0.9,0.9)
-k<-c(1.5,1.5,1.5)
+#k<-c(1.5,1.5,1.5)
 #k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.00000007
 rate_infection_threshold<-0.000007
@@ -244,4 +244,4 @@ A<-data.frame(1:52)
 A$Value<-as.data.frame(R_t)
 
 
-ggplot(A,aes(y=R_t,x=X1.52),size=2,color = "blue") + geom_line(color="blue") +   geom_point(color="blue") + labs(y = " R(t)")+ labs(x = "Weeks")+ geom_hline(yintercept=0.2857,linetype="dashed", color = "orange", size=0.5)+geom_point(color="blue") + labs(y = " R(t)")+ labs(x = "Weeks")+ geom_hline(yintercept=1.4285,linetype="dashed", color = "red", size=0.5)+ geom_hline(yintercept=0.1428,linetype="dashed", color = "green", size=0.5)+theme_bw(base_size = 18) 
+ggplot(A,aes(y=R_t,x=X1.52),size=2,color = "blue") + geom_line(color="blue") +   geom_point(color="blue") + labs(y = " R(t)")+ labs(x = "Weeks")+ geom_hline(yintercept=0.2857,linetype="dashed", color = "orange", size=0.5)+geom_point(color="blue") + labs(y = " R(t)")+ labs(x = "Weeks")+ geom_hline(yintercept=1.4285,linetype="dashed", color = "green", size=0.5)+ geom_hline(yintercept=0.1428,linetype="dashed", color = "red", size=0.5)+theme_bw(base_size = 18) 

### 2021-03-13 Manuscript/manuscript.tex
PUB

@@
 
-\author{\spacedlowsmallcaps{Marzio De Corato and Giulia Hadjiandrea}} % The article author(s) - author affiliations need to be specified in the AUTHOR AFFILIATIONS block
+\author{
+  Marzio De Corato (944459)\\
+  \and
+  Giulia Hadjiandrea (941780) \\
+}
 
@@
 
-Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically two types of lock-down with increasing force.
-The probability by which the PM applies the lock-down reflects his different attitude to face an epidemics (e.g.
+Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically different types of lock-downs.
+The probability that tune this stochastic process reflects his/her different attitude to face an epidemics (e.g.
 \textit{laissez-faire} vs very strict).
-We found that,  by modifying this parameter with continuity a phase transition (as defined for  a physical system) was obtained.
-For each phase we predicted a selected set of economic impacts (selling and subsidy) by using parameters estimated via econometric techniques (Difference-in -Difference) on the microeconomic data of Italy.
+In order to simulate not only an epidemiological scenario but also an economic one we estimated , via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales and on subsidies (\textit{Cassa Integrazione}).
+We found that,  by modifying with continuity the PM attitude  to impose the lock-down a phase transition (as defined for  a physical system) is obtained.
 The comparison of these two scenarios and their impact provide provide a bird's-eye view on the socio-economic consequences of the PM attitude
@@
 As performed by Ferrari et al.
-\cite{ferrari2020modelling} time dependent parameters are considered a time depended parameter called $R_{t}$.
+\cite{ferrari2020modelling},  when time dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ become time depended: thus scholar rename it as $R_{t}$.
 For the present work,  we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
@@
 \cite{marziano2021retrospective}.
+Therefore such trigger make the  R$_{0}$ parameter time dependent,  although in to a discrete way.
 As we said the PM acts with a certain probability,  more formally stochastically: each week a random number (from zero to one) is extracted: if this is higher than a certain threshold,  the relative restrictive decision is taken, otherwise not.
@@
 In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results.
-At the end of the simulation,  beside the values given by the standard SIRD model (recovered and deaths),  the model also provide the number of days in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
+At the end of the simulation,  beside the values given by the standard SIRD model (recovered and deaths),  the algorithm also provide the number of weeks in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
 It is worth nothing that here as lock-down we considered only the national one that was applied in the first wave of the epidemics: from March 2020 to June 2020.
@@
 For these reasons here the modelling will be always referred to national data and national lock-downs,  therefore the period after June when starting from October regional lock-down were imposed,  will be not considered.
+Another point that is it is worth mentioning,  is that in this model, on the contrary with respect to the SIS one, individual can not re-infect: concerning the COVID-19 the possibility of reinfection is still discussed among scholars \cite{ledford2020covid,iwasaki2021reinfections}.
+Basically to the know of author it is established that the immunity last at least 8 months  \cite{dan2021immunological} and very few cases of reinfection are reported.
+Thus the immunity considered in the model,  for an interval of one year seems almost  a realistic approximation.
 
@@
 {\color[HTML]{3531FF} Clothing}        & -40.16  & 2.01  & -19.99 & -60.07 & 2.77  & -21.64 & -16.45 & 2.77  & -5.92 \\ \hline
-{\color[HTML]{009901} Footwear}        & -20.62 & 1.73  & -22.35 & -65.78 & 2.39  & -27.49 & -20.62 & 2.39  & -8.62 \\ \hline
+{\color[HTML]{009901} Footwear}        & -38.70 & 1.73  & -22.35 & -65.78 & 2.39  & -27.49 & -20.62 & 2.39  & -8.62 \\ \hline
 {\color[HTML]{F56B00} Appliances}      & -20.32 & 2.50  & -8.11  & -27.34 & 3.45  & -7.90  & -3.68  & 3.45  & 1.06  \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & -34.14 & 2.55  & -13.38 & -52.32 & 3.52  & -14.84 & -7.86  & 3.52  & 2.23  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & -34.14 & 2.55  & -13.38 & -52.32 & 3.52  & -14.84 & -7.86  & 3.52  & -2.23 \\ \hline
 {\color[HTML]{6200C9} Household kids}   & -10.51 & 1.50  & -6.98  & -18.99 & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
@@
 
+\clearall
+\newpage
+
+\section*{Supporting information A}
+
+In order to check if any significant effect is obtained on the coefficients of Tab.
+\ref{selling_DID_table_delta_phantom} by the slight increase of food consumption during the lockdown,  we considered an hypothetical scenario were this increase did not happened (e.g.
+the selling for March to June were identical to February): as one can point out by comparing the Tab.
+\ref{selling_DID_table_delta_phantom} with Tab, \ref{selling_DID_table_delta} no significant difference can be found.
+Thus since the real scenario where this increase happened (real one), and the scenario where this did not happened (hypothetical one) are indistinguishable, we can consider this increase negligible for the estimation of coefficient
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings where the food selling are modified in order to have,  during the lockdown timings, the same constant value of February.
+Note that no signficative difference can be found with respect to the coeffient obtained in Tab \ref{selling_DID_table_delta}.
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
+{\color[HTML]{3531FF} Clothing}        & -39.71  & 2.00  & -19.76 & -59.34 & 2.77  & -21.37 & -15.50 & 2.77 & -5.58 \\ \hline
+{\color[HTML]{009901} Footwear}        & -38.24 & 1.73  & -22.08 & -65.05 & 2.39  & -27.18 & -19.68 & 2.39  & -8.22 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & -19.86 & 2.50  & -7.93 & -26.61 & 3.45  & -7.69  & -2.73 & 3.45  & -0.79 \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & -33.68 & 2.55 & -13.21 & -51.59 & 3.52 & -14.64 & -6.91 & 3.52  & -1.96 \\ \hline
+{\color[HTML]{6200C9} Household kids}   & -10.06 & 1.50  & -6.68  & -18.26 & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
+{\color[HTML]{00D2CB} Household tools} & -12.57 & 3.51 & -3.57 & -29.50 & 4.85  & -6.07   & 3.28   & 4.85  & 0.67  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & -27.10 & 3.47 & -7.80 & -63.58 &  4.79 & -13.24 & 1.21 &  4.79 & 0.25
+
+\end{tabular}
+\label{selling_DID_table_delta_phantom}
+\end{table}
+\end{landscape}
+
 %----------------------------------------------------------------------------------------

### 2021-03-14 Manuscript/manuscript.tex
PUB

@@
 where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  C a dummy for the treated group and $\epsilon$ a error term.
-As control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down \footnote{It is true that a slight increase of food consumption was done by people that were forced to stay at home as the plots in Fig.
-\ref{Selling_plots} \ref{Selling_plots_II} captures: however as proven numerically in the Supporting Info this change does not significantly affect the DID estimations } (note that in this selling also the one for the restaurants are included: thus,  if it is true that the restaurants were closed,  it is also true that people will purchase basically the same amount of food from the supermarket that they will consume into restaurant if these were opened).
+As control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down\footnote{Although it is true that a slight increase of food sales during the lock-down is present in the plots in Fig.
+\ref{Selling_plots} \ref{Selling_plots_II},  it must be stressed the fact that, as proven numerically in the Supporting Info A, this change does not significantly affect the DID estimations }.
 On the other side,  for subsidies \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
@@
 In order to make a further control,  a placebo test was performed by choosing timing before the pandemic of COVID19.
-As illustrated in the Supporting Info,  this test was successful.
+As illustrated in the Supporting Info B,  this test was successful.
 On the other side,  concerning $T_{3}$  (low lock-down),  only the effect for clothing and footwear can be considered significant,  also by considering the pre-trend slope as discussed in the Supporting Information.
@@
 
-\section*{Supporting information A}
+\section{Supporting information A}
 
@@
 \ref{selling_DID_table_delta_phantom} with Tab, \ref{selling_DID_table_delta} no significant difference can be found.
-Thus since the real scenario where this increase happened (real one), and the scenario where this did not happened (hypothetical one) are indistinguishable, we can consider this increase negligible for the estimation of coefficient
+Thus since the real scenario where this increase happened (real one), and the scenario where this did not happened (hypothetical one) are indistinguishable,  we can consider this increase negligible for the estimation of the DID $\delta$ coefficient
 
@@
 \begin{flushleft}
-$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings where the food selling are modified in order to have,  during the lockdown timings, the same constant value of February.
-Note that no signficative difference can be found with respect to the coeffient obtained in Tab \ref{selling_DID_table_delta}.
+$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} for the different lock-down timings where the food selling are modified in order to have,  during the lockdown timings, the same constant value of February.
+Note that no significant difference can be found with respect to the coeffient obtained in Tab \ref{selling_DID_table_delta}.
 \end{flushleft}
@@
 
+\clearall
+\newpage
+
+\section{Supporting information B}
+
+In order to assets the common trend the credibility of the DID coefficient we performed a placebo test (as proposed e.g.
+by \cite{schnabl2012international,placebo}) by moving back the lock-down timings as illustrated in Fig.
+\ref{DID_selling_placebo}.
+As showed in Tab.
+\ref{selling_DID_table_delta} no significant effect was found for the placebo timing before the lock-down of March 2020-June 2020.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{Figures/DID_selling_placebo.pdf}
+\caption{Timing for placebo test for food vs clothing sales: $T_{4}$ is placed at $T=-4$ and $T=-2$,  $T_{5}$ at $T=-3$ and  $T_{6}$ at $T=-1$).
+For the other sales sector the placebo timing is identical}
+\label{DID_selling_placebo}
+\end{figure}
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for a placebo timings as showed in Fig.  \ref{DID_selling_placebo}
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+                                       & $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{5} $ & $\sigma_{\delta_{5}$ & t      &  $\delta_{6}$ & $\sigma_{\delta_{6}$  & t     \\ \hline
+{\color[HTML]{3531FF} Clothing}        & 4.87  & 17.47  & 0.28 & 3.94 & 12.65 & 0.31 & 0.70 & 17.48  & 0.04 \\ \hline
+{\color[HTML]{009901} Footwear}        & 5.31 & 18.16 & 0.29 & 5.05  & 13.14 & 0.38 & 2.00  &  18. 16 & 0.11 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & 4.64 & 8.66  & 0.54 & 1.14 & 6.26  & 0.18  & -0.81  & 8.66 & -0.09  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & 1.71 & 15.18  & 0.11 & 0.84 & 10.99 & 0.07 & 0.70  & 15.18  & 0.11  \\ \hline
+{\color[HTML]{6200C9} Household kids}   & 1.23 & 5.15  & 0.24 & -0.07 & 3.72  & -0.018  & -0.86  & 5.15 & -0.17 \\ \hline
+{\color[HTML]{00D2CB} Household tools} & 0.26  & 8.78  & 0.03 & -0.21 & 6.36  & -0.03   & 0.14  & 8.79  & 0.97  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & 3.26 & 16.55 & 0.20 & 1.12 &  11.98  & 0.09 & 1.37 &  16.56 & 0.08
+
+\end{tabular}
+\label{selling_DID_table_delta}
+\end{table}
+\end{landscape}
+
 %----------------------------------------------------------------------------------------

### 2021-03-14 Analisi_vendite/Test vari/Plotter_destag.R

@@ -3,10 +3,20 @@ library(ggplot2)
 Data <- read_excel("Dati_destagionalizzati_FULL.xlsx")
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
+  geom_vline(xintercept = -4, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = -3, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = -2, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = -1, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
+
+
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
   geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
+
+
+
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Calzature),color = "darkgreen")+ 
   geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 

### 2021-03-14 Manuscript/manuscript.tex
PUB

@@
 \ref{selling_DID_table_delta}.
-As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
+As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
 As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.
 In order to make a further control,  a placebo test was performed by choosing timing before the pandemic of COVID19.
-As illustrated in the Supporting Info B,  this test was successful.
+As illustrated in the Supporting Info C,  this test was successful.
 On the other side,  concerning $T_{3}$  (low lock-down),  only the effect for clothing and footwear can be considered significant,  also by considering the pre-trend slope as discussed in the Supporting Information.
@@
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (divided by 4).
-The error bars were calculated by considering the error propagation}
+The error bars, although are visible because are too reduced,  were calculated by considering the error propagation}
 \label{CIG_sector_effects}
@@
 
+In order to perform a further assessment on the credibility of the DID coefficients obtained in Tab.
+\ref{selling_DID_table_delta} we make a comparison between the trends of the difference of food sales and the other sectors, before ($\Delta$ Slope before $T_{T1}$) and after the three lock-down at $T_{T1}$,$T_{T2}$ and $T_{T3}$.
+As can be seen from the following tables (Tab.
+\ref{ASS_Clothing}, \ref{ASS_Footwear},  \ref{ASS_Appliances},   \ref{ASS_Photooptics}, \ref{ASS_Household_K},  \ref{ASS_Household_T} and \ref{ASS_Games})  the lock-down $\Delta$ at $T_{T1}$ and $T_{T2}$ are much larger with respect to the pre-trend $\Delta$ before.
+Thus the DID coefficients obtained in Tab \ref{selling_DID_table_delta} can be considered credible.
+Concerning $T_{T3}$,  as said in the main text,  we considered significant only the values for Clothing and Footwear.
+
+\begin{table}
+\centering
+\caption{Clothing}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.33  & 0.08  \\ \hline
+$\Delta_{T1}$   & -36.33 & 2.15  \\ \hline
+$\Delta_{T2}$   & -56.23 & 2.77   \\ \hline
+$\Delta_{T3}$   & -11.95 & 2.86 \\ \hline
+\label{ASS_Clothing}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Footwear}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
+$\Delta_{T1}$   & -38.70 & 1.91   \\ \hline
+$\Delta_{T2}$   & -63.21 & 2.47  \\ \hline
+$\Delta_{T3}$   & -17.61 & 2.54  \\ \hline
+\label{ASS_Footwear}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Appliances}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
+$\Delta_{T1}$   & -19.21 & 3.10   \\ \hline
+$\Delta_{T2}$   & -26.23 & 4.00  \\ \hline
+$\Delta_{T3}$   & -2.37 & 4.12  \\ \hline
+\label{ASS_Appliances}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Photo-optics}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.40  & 0.07 \\ \hline
+$\Delta_{T1}$   & -29.94 & 2.73   \\ \hline
+$\Delta_{T2}$   & -48.11 & 3.52  \\ \hline
+$\Delta_{T3}$   & -2.93 & 3.63 \\ \hline
+\label{ASS_Photooptics}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Household kids}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.16  & 0.04  \\ \hline
+$\Delta_{T1}$   & -10.51 & 1.55  \\ \hline
+$\Delta_{T2}$   & -19.00 & 2.14  \\ \hline
+$\Delta_{T3}$   & -3.61 & 2.14 \\ \hline
+\label{ASS_Household_K}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Household tools}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.21 & 0.05  \\ \hline
+$\Delta_{T1}$   & -13.02 & 3.53 \\ \hline
+$\Delta_{T2}$   & -30.23 & 4.88  \\ \hline
+$\Delta_{T3}$   & 2.33 & 4.88 \\ \hline
+\label{ASS_Household_T}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Games}
+\begin{tabular}{l|l|l}
+                & Value  & Error \\ \hline
+$\Delta$ Slope before T1 & -0.37 & 0.10 \\ \hline
+$\Delta_{T1}$   & -27.56 & 3.63 \\ \hline
+$\Delta_{T2}$   & -64.31 & 5.01  \\ \hline
+$\Delta_{T3}$   & 0.27 & 5.01\\ \hline
+\label{ASS_Games}
+\end{tabular}
+\end{table}
+
+\clearpage
+\newpage
+
+\section{Supporting information C}
+
 In order to assets the common trend the credibility of the DID coefficient we performed a placebo test (as proposed e.g.
@@
 \begin{landscape}
-\begin{table}[]
+\begin{table}
 \caption{
@@
 
+\clearpage
+\newpage
+
 %----------------------------------------------------------------------------------------

### 2021-03-14 Manuscript/manuscript.tex
PUB

@@
 
-\section{Supporting information A}
+\section{Supporting information}
+
+\subsection{A}
 
@@
 
-\section{Supporting information B}
+\subsection{B}
 
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  & $\sigma$ \\ \hline
 $\Delta$ Slope before T1 & -0.33  & 0.08  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  &  $\sigma$ \ \\ \hline
 $\Delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  & $\sigma$ \\ \hline
 $\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  & $\sigma$ \\ \hline
 $\Delta$ Slope before T1 & -0.40  & 0.07 \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  & $\sigma$ \\ \hline
 $\Delta$ Slope before T1 & -0.16  & 0.04  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  & $\sigma$ \\ \hline
 $\Delta$ Slope before T1 & -0.21 & 0.05  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & Error \\ \hline
+                & Value  & $\sigma$ \\ \hline
 $\Delta$ Slope before T1 & -0.37 & 0.10 \\ \hline
@@
 
-\section{Supporting information C}
+\subsection{C}
 
@@
 
+\subsection{D}
+
+Here we report the estimation of the other parameters, obtained in the DID regression,  that were not put in to the main text
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+& $\alpha $&   $ \sigma_{\alpha}$   & t      & $C$ & $\sigma_{C}$ & t      &  $\beta_{1}$ & $\sigma_{\delta_{1}$  & t     \\ \hline
+{\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 & 1.47 & 1.96 & 0.75  \\ \hline
+{\color[HTML]{009901} Footwear}        & 102.88 & 0.37  & 278.66 & -2.05 & 0.52  & -3.93 & 1.47 & 1.69 & 0.87 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & 102.88 & 0.53  & 192.78 & 1.71 & 0.75  & 2.27 & 1.47  & 2.44  & 0.60  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & 102.88  & 0.54  &  189.22 & -7.69 & 0.76 & -10.00 & 1.47  & 2.49  & 0.59 \\ \hline
+{\color[HTML]{6200C9} Household kids}   & 102.88  & 0.32  & 320.61  & -5.14 & 0.45  & -11.33  & 1.47  & 1.47  & 1.00  \\ \hline
+{\color[HTML]{00D2CB} Household tools} & 102.88 & 0.75  & 137.25 & -2.21 & 1.06  & -2.08    & 1.47   & 3.43 & 0.43  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & 102.88 & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 &  1.47 &  3.39 & 0.43
+\end{tabular}
+\label{selling_DID_table_par_1}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+& $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
+{\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 \\ \hline
+{\color[HTML]{009901} Footwear}        & 102.88 & 0.37  & 278.66 & -2.05 & 0.52  & -3.93 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & 102.88 & 0.53  & 192.78 & 1.71 & 0.75  & 2.27  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & 102.88  & 0.54  &  189.22 & -7.69 & 0.76 & -10.00  \\ \hline
+{\color[HTML]{6200C9} Household kids}   & 102.88  & 0.32  & 320.61  & -5.14 & 0.45  & -11.33    \\ \hline
+{\color[HTML]{00D2CB} Household tools} & 102.88 & 0.75  & 137.25 & -2.21 & 1.06  & -2.08   \\ \hline
+{\color[HTML]{FFC9FD} Games}             & 102.88 & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 
+\end{tabular}
+\label{selling_DID_table_par_1}
+\end{table}
+\end{landscape}
+
 \clearpage

### 2021-03-14 Manuscript/manuscript.tex
PUB

@@
 The coefficients obtained are reported in Tab.
-\ref{selling_DID_table_delta}.
+\ref{selling_DID_table_delta} (the estimation of the other parameters is given in Supporting Information D).
 As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
@@
 \begin{flushleft}
-$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
@@
 & $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
-{\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 \\ \hline
-{\color[HTML]{009901} Footwear}        & 102.88 & 0.37  & 278.66 & -2.05 & 0.52  & -3.93 \\ \hline
-{\color[HTML]{F56B00} Appliances}      & 102.88 & 0.53  & 192.78 & 1.71 & 0.75  & 2.27  \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & 102.88  & 0.54  &  189.22 & -7.69 & 0.76 & -10.00  \\ \hline
-{\color[HTML]{6200C9} Household kids}   & 102.88  & 0.32  & 320.61  & -5.14 & 0.45  & -11.33    \\ \hline
-{\color[HTML]{00D2CB} Household tools} & 102.88 & 0.75  & 137.25 & -2.21 & 1.06  & -2.08   \\ \hline
-{\color[HTML]{FFC9FD} Games}             & 102.88 & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 
+{\color[HTML]{3531FF} Clothing}        & 1.2012  & 1.4206  & 0.84 & 1.69 & 1.96  & 0.86 \\ \hline
+{\color[HTML]{009901} Footwear}        & 1.20 & 1.22 &  0.98 & 1.69 &  1.69   & 1.00  \\ \hline
+{\color[HTML]{F56B00} Appliances}      & 1.20 & 1.77 & 0.67   & 1.69 & 2.44 & 0.69  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & 1.20 & 1.80  & 0.66 & 1.69 & 2.49 & 0.68  \\ \hline
+{\color[HTML]{6200C9} Household kids}   & 1.20  & 1.06 & 1.12  & 1.69 & 1.47  & 1.15    \\ \hline
+{\color[HTML]{00D2CB} Household tools} & 1.20 & 2.48  & 0.48 &  1.69  & 3.43  & 0.49   \\ \hline
+{\color[HTML]{FFC9FD} Games}             & 1.20 & 2.45 & 0.48  & 1.69 &  3.39 & 0.50
 \end{tabular}
-\label{selling_DID_table_par_1}
+\label{selling_DID_table_par_2}
 \end{table}

### 2021-03-15 Manuscript/manuscript.tex
PUB

@@
 \begin{equation} 
-R_{0}=\dfrac{\beta}{\gamma}
+R_{0}=\dfrac{\beta}{\gamma+\mu}
 \end{equation}
@@
 For the present work,  we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
+The $\mu$ was set in order to keep in to account the calculated lethality for Italy: 1 \% \cite{fernandez2020estimating} (see also the very fine analysis made by the Institute for International Political Studies (ISPI) \cite{ISPI})\footnote{The authors are aware that this ratio is far from being homogeneus for the the different ages of population: however if this factor is taken into account,  it requires the solution of a system of partial derivative equations.
+In this case the numerical calculations become much more complicated}.
 The overall population $N$ was set to 60M,  in order to simulate Italian population.
@@
 Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
-In this case, the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged by the contraction in demand as well as by the fact that for different sector of them production was also banned by law during the lock-down \footnote{In principle one can be also interested to disentangle these two effects: in this case an interesting option is to study the second-wave of the epidemics in Italy that happened in the second half of the 2020.
-Contrary with respect to the first wave, the lock-down did not banned by law the production.
-As told previously this option was not considered by the authors since the most of the economic data were available, with the temporal resolution considered in this work, only at national level.}.
+In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged the lock-down restrictions.
 For the empirical evaluation of the impact on selling and unemployment benefit we performed a multiple time Difference in Difference as presented in Refs.
@@
 \begin{equation}
-Y_{outcome}=\alpha+\sum_{i=1}^{3}\beta_{i}T_{i}+\sum_{i=1}^{3}\delta_{i}(C \cdot T_{i})+\epsilon
+Y_{outcome}=\alpha+\beta_{0}C+\sum_{i=1}^{3}\beta_{i}T_{i}+\sum_{i=1}^{3}\delta_{i}(C \cdot T_{i})+\epsilon
 \label{DID-eq}
 \end{equation}
-where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  C a dummy for the treated group and $\epsilon$ a error term.
+where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group and $\epsilon$ a error term.
 As control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down\footnote{Although it is true that a slight increase of food sales during the lock-down is present in the plots in Fig.
@@
 On the other side,  for subsidies \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
-This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labour cost but at same time guaranteeing to the workers part of their original salary.
+This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labour cost but at same time guaranteeing to the workers part of their original salary \footnote{It is worth nothing that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
+However in the present study we consider,for simplicity,  only the sectors covered by Cassa Integrazione Ordinaria.
+}.
 During the first months of the pandemic firms,  following the rules stated by the Italian Governament (Decreto Cura Italia \cite{curaitalia}),  firms that would reduce their labour cost,  first forced the employees to use their holiday budget and than,  after it was run out,  they put the employees in to the Cassa Integrazione Ordinaria.
@@
 As discussed in Supporting Information,  these data were not de-seasoned: thus we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
+The decomposition results are reported in the Supporting Info E.
 Concerning subsidies we retried the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
@@
 In order to assure the \textit{ceteris pariubus} condition we used for both scenario the same set of random numbers.
-First,  we see that where the PM is more reactive we have small different waves of epidemics,  while if the PM is poorly reactive only one intense wave is present (basically the standard wave of SIRD model).
-Since this change happens in a discontinuous way as showed in Fig.
+First,  we see that where the PM is more reactive we have small different waves of epidemics,  while if the PM is poorly reactive only one intense wave is present,  indeed in the latter scenario the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: when the PM acts is too late,  as shown in Fig.
+\ref{SIRD_scenario}, since the pandemics has almost hit the large part of the population.
+This can be pointed out in Fig.
+\ref{R_t_scenarios} by noting that that the reproduction factor remains at its maximum level for large number of weeks after the beginning of the pandemic.
+This also explains why in the second half of the scenario the lock-downs are so week: the remaining part of the population is immune.,  an thus no further action is required.
+On the contrary in the first scenario the PM is able,  using the lock-downs to transform the SIRD peak in to small waves (Fig.
+\ref{SIRD_scenario}).
+As shown in Fig.
+\ref{R_t_scenarios} this result is basically obtained by keeping the reproduction factor in the value of medium lock-down value.
+These two theoretical model correspond,  in practice,  for the lazy PM to the one considered by the PMs that aimed to heard immunity,  while,  concerning the active-PM,  to the PMs that would not saturate the saturate the health system and aimed to reduce the death at the minimum.
+It is interesting to point out that the change between the scenarios develops in a discontinuous way as showed in Fig.
 \ref{Phase_transition},   as the reactivity of the PM is changed,  we can consider this as a phase transition of a physical system (it is interesting to point out the closness with respect to the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
@@
 The explanation of this similar behaviour is that both model have a stochastic component,  that as pointed out by Balcan and Vespignani,  give the phase transition: indeed while in their model this was directly related to the contagion probability,  here this is indirectly made stochastically by the decision of PM that modify the $\beta$ parameter and so the transmission rate.
-We see that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by a consistent use of the confinement.
-This has it immediate drawback on the economic data: the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
-A deeper inspection on the reproduction number for both scenarios provide a further insight about these two very different outcomes:  as shown in Fig.
-\ref{R_t_scenarios}  the reactivity PM basically stabilize the reproduction number in to its value of a medium lock-down,  on the contrary the inactivity of the PM to set the lock-downs make the epidemic to be almost out of control since it the reproduction factor basically remain (with an exception of an intermediate spike) at it maximum level.
-The Fig.
-\ref{R_t_scenarios} can be also used to see the number of weeks elapsed for each lock-down intensity.
+Moving to the socio-economic outcome of the model used we see, from Tab.
+\ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost},  that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by a consistent use of the confinement.
+This has an  immediate drawback on the economic data: as shown in Fig.
+\ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
 In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation,  the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
@@
 $\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
-The values of the  intercept ($\alpha$), C and T$_{i}$ are provided in the Supporting Info.
+The values of the  intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Info.
 \end{flushleft}
@@
      \end{subfigure}
-\caption{Comparison between the reproduction number (calculated as effective the $\frac{\beta}{\gamma}$ ratio when the lock-down is applied) for a highly reactive PM vs to the one of a poorly reactive one.
+\caption{Comparison between the reproduction number (calculated as effective the $\frac{\beta}{\gamma+\mu}$ ratio when the lock-down is applied) for a highly reactive PM vs to the one of a poorly reactive one.
 It can be noted that while in the former the PM reactivity almost allows him/her to control this factor in to a stable medium lock-down,  in the second one the reproduction number (and thus the epidemic) is almost out of control of the PM since it remains,  for most of weeks at its maximum level.
+In particular in the second scenario,  the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: when the PM act is too late since the pandemics has almost hit the large part of the population.
+This also explain why in the second half of the scenario the lock-downs are so week: the remaining part of the population is immune.
+On the contrary in the first scenario the PM is able,  using the lockdown to transform the sharp SIRD peak in to small waves.
 Note that the levels of reproduction number are discrete,  as marked by the dashed lines (green low,  orange medium,  red high) since the lock-down is the only way to change this number.
@@
 $\delta$ cofficients, expressed in millions as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for the different lock-down timings.
-The values of the  intercept ($\alpha$), C and T$_{i}$ are provided in the Supporting Info.
+The values of the  intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Information D.
 \end{flushleft}
@@
 
-\subsection{A}
+\subsection{A - Food consumption during the lock-down}
 
@@
 \ref{selling_DID_table_delta_phantom} with Tab, \ref{selling_DID_table_delta} no significant difference can be found.
-Thus since the real scenario where this increase happened (real one), and the scenario where this did not happened (hypothetical one) are indistinguishable,  we can consider this increase negligible for the estimation of the DID $\delta$ coefficient
+Thus since the real scenario where this increase happened (real one), and the scenario where this did not happened (hypothetical one) are indistinguishable,  we can consider this increase negligible for the estimation of the DID $\delta$ coefficients
 
@@
 
-\subsection{B}
+\subsection{B - Pre-trend check}
 
@@
 
-\subsection{C}
+\subsection{C - Placebo tests for DID}
 
@@
 
-\subsection{D}
-
-Here we report the estimation of the other parameters, obtained in the DID regression,  that were not put in to the main text
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{Figures/DID_subsidies_placebo.pdf}
+\caption{Timing for placebo test for the total subsidies paid (in hour) \textit{Cassa integrazione Ordinaria} (blue) vs  \textit{Cassa integrazione Straordinaria Solidarietà} (purple)  sales: $T_{4}$ is placed at $T=-2$,  $T_{5}$ at $T=-1$ and  $T_{6}$ at $T=0$).
+For the other categories the placebo timing is identical}
+\label{DID_subsidies_placebo}
+\end{figure}
 
@@
 \begin{flushleft}
-$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for a placebo timings as showed in Fig.
+\ref{DID_subsidies_placebo}
 \end{flushleft}
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-& $\alpha $&   $ \sigma_{\alpha}$   & t      & $C$ & $\sigma_{C}$ & t      &  $\beta_{1}$ & $\sigma_{\delta_{1}$  & t     \\ \hline
+                                       & $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{4} $ & $\sigma_{\delta_{4}$ & t      &  $\delta_{5}$ & $\sigma_{\delta_{5}$  & t     \\ \hline
+{\color[HTML]{343434} Total}        & -36   & 144    &  -0.26  & -36   & 144   & -0.25 & -36  & 144    & -0.25 \\ \hline
+{\color[HTML]{343434} Manufacture}  & -26   & 101    &  -0.25  & -26   & 101   & -0.26 & -26  & 101     & -0.25   \\ \hline
+{\color[HTML]{343434} Trade}        & -0.88   & 3.2  & -0.27  & -0.60   & 3.2  & -0.18 & -0.70   & 3.2  & -0.21 \\ \hline
+{\color[HTML]{343434} Construction} & -6.7   & 26  &  -0.25 &  -5.8    & 26  & -0.22 & -6.5    & 26 & -0.25 \\ \hline
+\label{sub_DID_placebo}
+\end{tabular}
+\end{table}
+\end{landscape}
+
+\subsection{D - DID coefficients}
+
+Here we report the estimation of the other parameters,  obtained in the DID regression for sales and subsidies,  that were not put in to the main text
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\alpha$ , $\beta_{0}$ and $\beta_{1}$  obtained by the DID regression,  for sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+& $\alpha $&   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
 {\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 & 1.47 & 1.96 & 0.75  \\ \hline
@@
 \begin{flushleft}
-$\alpha$ , $C$ and $T_{1}$ obtained by the DID regression,  for the sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\beta_{2}$ and $\beta_{3}$ obtained by the DID regression,  for  sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
 }
-\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+\begin{tabular}{l|l|l|l|l|l|l}
 & $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
@@
 
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\alpha$ , $\beta_{0}$ and $\beta_{1}$ obtained by the DID regression,  for subsidies  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
+                                       & $\alpha$ &   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
+{\color[HTML]{343434} Total}        & 4.75   &  0.47   & 10.04  & 3.90    &  0.66    & 5.84  & -2.46   &  2.50    & -0.98  \\ \hline
+{\color[HTML]{343434} Manufacture}  & 3.72   &  0.41    & 8.95  & 2.59    &  0.59    & 4.40 & -2.00   & 2.20     & -0.91   \\ \hline
+{\color[HTML]{343434} Trade}        & 0.23   & 0.03  & 7.13  & -0. 16  & 0.05  & -3.36  & -0.15  & 0.17  & -0.83 \\ \hline
+{\color[HTML]{343434} Construction} & 0.06    & 0.11  & 0.53 & 1.97     & 0.16  & 11.91 &  -0.06    & 0.62  &  -0.095  \\ \hline
+\label{CIG_DID_coef_I}
+\end{tabular}
+\end{table}
+\end{landscape}
+
+\begin{landscape}
+\begin{table}[]
+\caption{
+\begin{flushleft}
+$\beta_{2}$ and $\beta_{3}$ obtained by the DID regression,  for subsidies  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+\end{flushleft}
+}
+\begin{tabular}{l|l|l|l|l|l|l}
+& $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
+{\color[HTML]{343434} Total}        & -2.39   &  2.50   & -0.95  & -3.17    &  2.50    & -1.26  \\ \hline
+{\color[HTML]{343434} Manufacture}  & -2.72   &  2.20    & -1.23  & -3.33    &  2.20    & -1.50   \\ \hline
+{\color[HTML]{343434} Trade}        & -0.12   & 0.17  & -0.68  & -0.07  & 0.17  & -0.39   \\ \hline
+{\color[HTML]{343434} Construction} & -0.06    & 0.62 & -0.096  & 0.06     & 0.62  & 0.10  
+\label{CIG_DID_coef_II}
+\end{tabular}
+\end{table}
+\end{landscape}
+
 \clearpage
 \newpage
+
+\subsection{E - De-seasoning}
+
+In this section of we report the results of the de-seasoning for raw sales data taken from ISTAT \cite{istat}.
+The first panel refer to the raw data (data)  the third to the seasonal component that is perfectly periodical (seasonal),  the forth one to the seasonal component that is not perfectly periodical (remainder) and the second one the trend extracted (trend).
+This decomposition was made by using an Hilbert-Huang transform as implemented in the \cite{forecast} R package.
+The final trend in the second panel was obtained from by subtracting from the raw data the signal obtained in the third and forth panel.
+This approach of de-seasoning is known as additive.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Alimentare.pdf}
+\caption{De-seasoning components for food sales} 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Abbigliamento.pdf}
+\caption{De-seasoning component for clothing sales} 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Calzature.pdf}
+\caption{De-seasoning components for footwear sales} 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Elettrodomestici.pdf}
+\caption{De-seasoning components for appliances sales} 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Fotoottica.pdf}
+\caption{De-seasoning components for photo-optics sales} 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Casalinghi.pdf}
+\caption{de-seasoning components  for household kids sales } 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Utilenseria.pdf}
+\caption{De-seasoning components for household tools sales} 
+\label{Phase_transition}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{Figures/Deseasoning/Giocattoli.pdf}
+\caption{De-seasoning components for games sales } 
+\label{Phase_transition}
+\end{figure}
 

### 2021-03-15 Analisi_cassa_integrazione/Cassa_integrazione.R

@@ -19,6 +19,9 @@ Dati_cassa_integrazione_Manifattura_DID <- read_excel("Cassa_integrazione_Ordere
 did_Manifattura <-lm(Hours ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_cassa_integrazione_Manifattura_DID)
 summary(did_Manifattura)
 
+did_Manifattura_placebo <-lm(Hours ~  C + T4 + T5+ T6 + C*T4 +C*T5+C*T6, data = Dati_cassa_integrazione_Manifattura_DID)
+summary(did_Manifattura_placebo)
+
 
 Dati_cassa_integrazione_Commercio <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Commercio")
 
@@ -37,6 +40,9 @@ Dati_cassa_integrazione_Commercio_DID <- read_excel("Cassa_integrazione_Ordered.
 did_Commercio <-lm(Hours ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_cassa_integrazione_Commercio_DID )
 summary(did_Commercio)
 
+did_Commercio_placebo <-lm(Hours ~  C + T4 + T5+ T6 + C*T4 +C*T5+C*T6, data = Dati_cassa_integrazione_Commercio_DID)
+summary(did_Commercio_placebo)
+
 
 Dati_cassa_integrazione_Costruzioni<- read_excel("Cassa_integrazione_Ordered.xlsx", sheet = "Costruzioni")
 
@@ -52,9 +58,13 @@ ggplot(data=Dati_cassa_integrazione_Costruzioni   ,aes(x=Time,y=CIG_S))+geom_lin
 
 Dati_cassa_integrazione_Costruzioni_DID <- read_excel("Cassa_integrazione_Ordered.xlsx",sheet = "Costruzioni_DID")
 
+
+
 did_Costruzioni <-lm(Hours ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_cassa_integrazione_Costruzioni_DID )
 summary(did_Costruzioni)
 
+did_Costruzioni_placebo <-lm(Hours ~  C + T4 + T5+ T6 + C*T4 +C*T5+C*T6, data = Dati_cassa_integrazione_Costruzioni_DID)
+summary(did_Costruzioni_placebo)
 
[…]

### 2021-03-15 Analisi_vendite/Test vari/tentativo_destagionalizzazione.R

@@ -18,7 +18,7 @@ TS_Alimentare_dec$trend=TS_Alimentare_dec$x-TS_Alimentare_dec$random-TS_Alimenta
 
 
 
-autoplot(TS_Alimentare_dec)
+autoplot(TS_Alimentare_dec)+labs(colour = NULL)
 
 
 TS_Abbigliamento = ts(Destagionalizzazione$`abbigliamento e pellicce`,frequency = 12)

### 2021-03-15 Project_script_Stochastic.R

@@ -19,9 +19,9 @@ CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-k<-c(1,1,1)
+#k<-c(1,1,1)
 #k<-c(0.9,0.9,0.9)
-#k<-c(1.5,1.5,1.5)
+k<-c(1.5,1.5,1.5)
 #k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.00000007
 rate_infection_threshold<-0.000007
@@ -153,25 +153,25 @@ if(buffer[(i+1)*7,]$I/pop_tot < rate_infection_threshold*0.5 & p_vector[i+1] >= 
 
 if(parms == c(beta=0.55)) {
    no_lockdown_weeks <- no_lockdown_weeks +1
-   R_t[i]=0.4/0.14
+   R_t[i]=0.4/(0.14+0.01)
    print("NO RESTRICTION")
 }
 
   
 if(parms == c(beta=0.55*0.7)) {
     soft_lockdown_weeks <- soft_lockdown_weeks +1
-    R_t[i]=0.4*0.5/0.14
+    R_t[i]=0.4*0.5/(0.14+0.01)
     print("SOFT")
   }
 
 if(parms == c(beta=0.55*0.25)) {
   medium_lockdown_weeks <- medium_lockdown_weeks +1
-    R_t[i]=0.4*0.1/0.14
+    R_t[i]=0.4*0.1/(0.14+0.01)
     print("MEDIUM")
 }
 
 if(parms == c(beta=0.55*0.025)) {
-  R_t[i]=0.4*0.05/0.14
+  R_t[i]=0.4*0.05/(0.14+0.01)
   strong_lockdown_weeks <- strong_lockdown_weeks +1
   print("HIGH")
 }
@@ -244,4 +244,4 @@ A<-data.frame(1:52)
 A$Value<-as.data.frame(R_t)
 
 
[…]

### 2021-03-15 Manuscript/manuscript.tex
PUB

@@
 
+In all tables the following significance code will be used:  *** for 0.001,  ** for 0.01 and * for 0.05
+
 \begin{figure}
@@
                                        & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
-{\color[HTML]{3531FF} Clothing}        & -40.16  & 2.01  & -19.99 & -60.07 & 2.77  & -21.64 & -16.45 & 2.77  & -5.92 \\ \hline
-{\color[HTML]{009901} Footwear}        & -38.70 & 1.73  & -22.35 & -65.78 & 2.39  & -27.49 & -20.62 & 2.39  & -8.62 \\ \hline
-{\color[HTML]{F56B00} Appliances}      & -20.32 & 2.50  & -8.11  & -27.34 & 3.45  & -7.90  & -3.68  & 3.45  & 1.06  \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & -34.14 & 2.55  & -13.38 & -52.32 & 3.52  & -14.84 & -7.86  & 3.52  & -2.23 \\ \hline
-{\color[HTML]{6200C9} Household kids}   & -10.51 & 1.50  & -6.98  & -18.99 & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
-{\color[HTML]{00D2CB} Household tools} & -13.02 & 3.51  & -3.70 & -30.23 & 4.85  & -6.23    & 2.33   & 4.85  & 0.48  \\ \hline
-{\color[HTML]{FFC9FD} Games}             & -27.55 & 3.47 & -7.93 & -64.31 &  4.79  & -13.40 & 0.26 &  4.79 & 0.05
+{\color[HTML]{3531FF} Clothing}        & -40.16 *** & 2.01  & -19.99 & -60.07 *** & 2.77  & -21.64 & -16.45 *** & 2.77  & -5.92 \\ \hline
+{\color[HTML]{009901} Footwear}        & -38.70 *** & 1.73  & -22.35 & -65.78 *** & 2.39  & -27.49 & -20.62 *** & 2.39  & -8.62 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & -20.32 *** & 2.50  & -8.11  & -27.34 *** & 3.45  & -7.90  & -3.68  & 3.45  & 1.06  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & -34.14 *** & 2.55  & -13.38 & -52.32 ***  & 3.52  & -14.84 & -7.86 *  & 3.52  & -2.23 \\ \hline
+{\color[HTML]{6200C9} Household kids}   & -10.51 *** & 1.50  & -6.98  & -18.99 ***  & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
+{\color[HTML]{00D2CB} Household tools} & -13.02  *** & 3.51  & -3.70 & -30.23 *** & 4.85  & -6.23    & 2.33   & 4.85  & 0.48  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & -27.55 *** & 3.47 & -7.93 & -64.31 *** &  4.79  & -13.40 & 0.26 &  4.79 & 0.05
 
@@
                                        & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
-{\color[HTML]{343434} Total}        & 706    & 3     & 199.5  & 217    & 3     & 61.48 & 144    & 3     & 40.72 \\ \hline
-{\color[HTML]{343434} Manufacture}  & 494    & 3     & 158.56 & 162    & 3     & 52    & 111    & 3     & 35.7  \\ \hline
-{\color[HTML]{343434} Trade}        & 16.4   & 0.24  & 66.10  & 3.72   & 0.24  & 15.00 & 2.92   & 0.24  & 11.78 \\ \hline
-{\color[HTML]{343434} Construction} & 134    & 0.87  & 153.10 & 29     & 0.87  & 33.13 & 14     & 0.87  & 16.41 \\ \hline
+{\color[HTML]{343434} Total}        & 706 ***   & 3     & 199.5  & 217  ***  & 3     & 61.48 & 144  ***  & 3     & 40.72 \\ \hline
+{\color[HTML]{343434} Manufacture}  & 494  ***  & 3     & 158.56 & 162  ***  & 3     & 52    & 111   *** & 3     & 35.7  \\ \hline
+{\color[HTML]{343434} Trade}        & 16.4  *** & 0.24  & 66.10  & 3.72 ***  & 0.24  & 15.00 & 2.92  *** & 0.24  & 11.78 \\ \hline
+{\color[HTML]{343434} Construction} & 134  ***   & 0.87  & 153.10 & 29  ***   & 0.87  & 33.13 & 14   ***  & 0.87  & 16.41 \\ \hline
 \label{CIG_DID}
@@
                                        & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
-{\color[HTML]{3531FF} Clothing}        & -39.71  & 2.00  & -19.76 & -59.34 & 2.77  & -21.37 & -15.50 & 2.77 & -5.58 \\ \hline
-{\color[HTML]{009901} Footwear}        & -38.24 & 1.73  & -22.08 & -65.05 & 2.39  & -27.18 & -19.68 & 2.39  & -8.22 \\ \hline
-{\color[HTML]{F56B00} Appliances}      & -19.86 & 2.50  & -7.93 & -26.61 & 3.45  & -7.69  & -2.73 & 3.45  & -0.79 \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & -33.68 & 2.55 & -13.21 & -51.59 & 3.52 & -14.64 & -6.91 & 3.52  & -1.96 \\ \hline
-{\color[HTML]{6200C9} Household kids}   & -10.06 & 1.50  & -6.68  & -18.26 & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
-{\color[HTML]{00D2CB} Household tools} & -12.57 & 3.51 & -3.57 & -29.50 & 4.85  & -6.07   & 3.28   & 4.85  & 0.67  \\ \hline
-{\color[HTML]{FFC9FD} Games}             & -27.10 & 3.47 & -7.80 & -63.58 &  4.79 & -13.24 & 1.21 &  4.79 & 0.25
+{\color[HTML]{3531FF} Clothing}        & -39.71 ***  & 2.00  & -19.76 & -59.34 *** & 2.77  & -21.37 & -15.50  *** & 2.77 & -5.58 \\ \hline
+{\color[HTML]{009901} Footwear}        & -38.24 *** & 1.73  & -22.08 & -65.05  *** & 2.39  & -27.18 & -19.68 *** & 2.39  & -8.22 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & -19.86 *** & 2.50  & -7.93 & -26.61 *** & 3.45  & -7.69  & -2.73 & 3.45  & -0.79 \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & -33.68 ***  & 2.55 & -13.21 & -51.59 ***  & 3.52 & -14.64 & -6.91 & 3.52  & -1.96 \\ \hline
+{\color[HTML]{6200C9} Household kids}   & -10.06  *** & 1.50  & -6.68  & -18.26 *** & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
+{\color[HTML]{00D2CB} Household tools} & -12.57 *** & 3.51 & -3.57 & -29.50 ***  & 4.85  & -6.07   & 3.28   & 4.85  & 0.67  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & -27.10 *** & 3.47 & -7.80 & -63.58 *** &  4.79 & -13.24 & 1.21 &  4.79 & 0.25
 
@@
                 & Value  & $\sigma$ \\ \hline
-$\Delta$ Slope before T1 & -0.33  & 0.08  \\ \hline
-$\Delta_{T1}$   & -36.33 & 2.15  \\ \hline
-$\Delta_{T2}$   & -56.23 & 2.77   \\ \hline
-$\Delta_{T3}$   & -11.95 & 2.86 \\ \hline
+$\Delta$ Slope before T1 & -0.33  *** & 0.08  \\ \hline
+$\Delta_{T1}$   & -36.33 *** & 2.15  \\ \hline 
+$\Delta_{T2}$   & -56.23 *** & 2.77   \\ \hline
+$\Delta_{T3}$   & -11.95 *** & 2.86 \\ \hline
 \label{ASS_Clothing}
@@
                 & Value  &  $\sigma$ \ \\ \hline
-$\Delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
-$\Delta_{T1}$   & -38.70 & 1.91   \\ \hline
-$\Delta_{T2}$   & -63.21 & 2.47  \\ \hline
-$\Delta_{T3}$   & -17.61 & 2.54  \\ \hline
+$\Delta$ Slope before T1 & -0.18 * & 0.08  \\ \hline
+$\Delta_{T1}$   & -38.70 *** & 1.91   \\ \hline
+$\Delta_{T2}$   & -63.21 ***  & 2.47  \\ \hline
+$\Delta_{T3}$   & -17.61 *** & 2.54  \\ \hline
 \label{ASS_Footwear}
@@
 $\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
-$\Delta_{T1}$   & -19.21 & 3.10   \\ \hline
-$\Delta_{T2}$   & -26.23 & 4.00  \\ \hline
+$\Delta_{T1}$   & -19.21 *** & 3.10   \\ \hline
+$\Delta_{T2}$   & -26.23 *** & 4.00  \\ \hline
 $\Delta_{T3}$   & -2.37 & 4.12  \\ \hline
@@
                 & Value  & $\sigma$ \\ \hline
-$\Delta$ Slope before T1 & -0.40  & 0.07 \\ \hline
-$\Delta_{T1}$   & -29.94 & 2.73   \\ \hline
-$\Delta_{T2}$   & -48.11 & 3.52  \\ \hline
+$\Delta$ Slope before T1 & -0.40 ***  & 0.07 \\ \hline
+$\Delta_{T1}$   & -29.94 *** & 2.73   \\ \hline
+$\Delta_{T2}$   & -48.11 *** & 3.52  \\ \hline
 $\Delta_{T3}$   & -2.93 & 3.63 \\ \hline
@@
                 & Value  & $\sigma$ \\ \hline
-$\Delta$ Slope before T1 & -0.16  & 0.04  \\ \hline
-$\Delta_{T1}$   & -10.51 & 1.55  \\ \hline
-$\Delta_{T2}$   & -19.00 & 2.14  \\ \hline
+$\Delta$ Slope before T1 & -0.16 ** & 0.04  \\ \hline
+$\Delta_{T1}$   & -10.51 *** & 1.55  \\ \hline
+$\Delta_{T2}$   & -19.00 *** & 2.14  \\ \hline
 $\Delta_{T3}$   & -3.61 & 2.14 \\ \hline
@@
                 & Value  & $\sigma$ \\ \hline
-$\Delta$ Slope before T1 & -0.21 & 0.05  \\ \hline
-$\Delta_{T1}$   & -13.02 & 3.53 \\ \hline
-$\Delta_{T2}$   & -30.23 & 4.88  \\ \hline
+$\Delta$ Slope before T1 & -0.21 *** & 0.05  \\ \hline
+$\Delta_{T1}$   & -13.02 *** & 3.53 \\ \hline
+$\Delta_{T2}$   & -30.23 ** & 4.88  \\ \hline
 $\Delta_{T3}$   & 2.33 & 4.88 \\ \hline
@@
                 & Value  & $\sigma$ \\ \hline
-$\Delta$ Slope before T1 & -0.37 & 0.10 \\ \hline
-$\Delta_{T1}$   & -27.56 & 3.63 \\ \hline
-$\Delta_{T2}$   & -64.31 & 5.01  \\ \hline
+$\Delta$ Slope before T1 & -0.37 ** & 0.10 \\ \hline
+$\Delta_{T1}$   & -27.56 *** & 3.63 \\ \hline
+$\Delta_{T2}$   & -64.31 *** & 5.01  \\ \hline
 $\Delta_{T3}$   & 0.27 & 5.01\\ \hline
@@
 & $\alpha $&   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
-{\color[HTML]{3531FF} Clothing}        & 102.88 & 0.42  & 240.20 & -3.66 & 0.60  & -6.05 & 1.47 & 1.96 & 0.75  \\ \hline
-{\color[HTML]{009901} Footwear}        & 102.88 & 0.37  & 278.66 & -2.05 & 0.52  & -3.93 & 1.47 & 1.69 & 0.87 \\ \hline
-{\color[HTML]{F56B00} Appliances}      & 102.88 & 0.53  & 192.78 & 1.71 & 0.75  & 2.27 & 1.47  & 2.44  & 0.60  \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & 102.88  & 0.54  &  189.22 & -7.69 & 0.76 & -10.00 & 1.47  & 2.49  & 0.59 \\ \hline
-{\color[HTML]{6200C9} Household kids}   & 102.88  & 0.32  & 320.61  & -5.14 & 0.45  & -11.33  & 1.47  & 1.47  & 1.00  \\ \hline
-{\color[HTML]{00D2CB} Household tools} & 102.88 & 0.75  & 137.25 & -2.21 & 1.06  & -2.08    & 1.47   & 3.43 & 0.43  \\ \hline
-{\color[HTML]{FFC9FD} Games}             & 102.88 & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 &  1.47 &  3.39 & 0.43
+{\color[HTML]{3531FF} Clothing}        & 102.88 *** & 0.42  & 240.20 & -3.66 *** & 0.60  & -6.05 & 1.47 & 1.96 & 0.75  \\ \hline
+{\color[HTML]{009901} Footwear}        & 102.88 *** & 0.37  & 278.66 & -2.05 *** & 0.52  & -3.93 & 1.47 & 1.69 & 0.87 \\ \hline
+{\color[HTML]{F56B00} Appliances}      & 102.88 *** & 0.53  & 192.78 & 1.71 * & 0.75  & 2.27 & 1.47  & 2.44  & 0.60  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & 102.88 ***  & 0.54  &  189.22 & -7.69 *** & 0.76 & -10.00 & 1.47  & 2.49  & 0.59 \\ \hline
+{\color[HTML]{6200C9} Household kids}   & 102.88 *** & 0.32  & 320.61  & -5.14 *** & 0.45  & -11.33  & 1.47  & 1.47  & 1.00  \\ \hline
+{\color[HTML]{00D2CB} Household tools} & 102.88 *** & 0.75  & 137.25 & -2.21 * & 1.06  & -2.08    & 1.47   & 3.43 & 0.43  \\ \hline
+{\color[HTML]{FFC9FD} Games}             & 102.88 *** & 0.74 & 138.93 & 1.20 &  1.04 & 1.15 &  1.47 &  3.39 & 0.43
 \end{tabular}
@@
                                        & $\alpha$ &   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
-{\color[HTML]{343434} Total}        & 4.75   &  0.47   & 10.04  & 3.90    &  0.66    & 5.84  & -2.46   &  2.50    & -0.98  \\ \hline
-{\color[HTML]{343434} Manufacture}  & 3.72   &  0.41    & 8.95  & 2.59    &  0.59    & 4.40 & -2.00   & 2.20     & -0.91   \\ \hline
-{\color[HTML]{343434} Trade}        & 0.23   & 0.03  & 7.13  & -0. 16  & 0.05  & -3.36  & -0.15  & 0.17  & -0.83 \\ \hline
-{\color[HTML]{343434} Construction} & 0.06    & 0.11  & 0.53 & 1.97     & 0.16  & 11.91 &  -0.06    & 0.62  &  -0.095  \\ \hline
+{\color[HTML]{343434} Total}        & 4.75 *** &  0.47   & 10.04  & 3.90 ***  &  0.66    & 5.84  & -2.46   &  2.50    & -0.98  \\ \hline
+{\color[HTML]{343434} Manufacture}  & 3.72  ***  &  0.41  & 8.95 & 2.59 ***   &  0.59    & 4.40 & -2.00   & 2.20     & -0.91   \\ \hline
+{\color[HTML]{343434} Trade}        & 0.23 ***  & 0.03  & 7.13  & -0.16 **  & 0.05  & -3.36  & -0.15  & 0.17  & -0.83 \\ \hline
+{\color[HTML]{343434} Construction} & 0.06  & 0.11  & 0.53 & 1.97  ***   & 0.16  & 11.91 &  -0.06    & 0.62  &  -0.095  \\ \hline
 \label{CIG_DID_coef_I}

### 2021-03-16 Manuscript/manuscript.tex
PUB

@@
 Among the very large number of compartmental model available in the literature \cite{vynnycky2010introduction} we considered,  as the simulator of the epidemic diffusion the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
-Our choice is motivated by the fact that this relative simple model provides the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters \footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
+Our choice is motivated by the fact that this relative simple model provides the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters\footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
 in Ref.
@@
 Note that in this last case the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)}).
-The SIRD model,first proposed by Kermack and McKendrick in 1927 \cite{kermack1927contribution},  is given by the following set of differential equations\cite{vynnycky2010introduction}:
+The SIRD model, first proposed by Kermack and McKendrick in 1927 \cite{kermack1927contribution},  is given by the following set of differential equations\cite{vynnycky2010introduction}:
 \begin{equation} 
@@
 where S is the number of people that are still susceptible, I the number of people that are infected and R people that are recovered while D are people that are death.
-N denotes the total population,  that for the timing of this paper,  it will be considered fixed \footnote{Othervise, if longer horizontal timing is considered,  it is necessary to consider also a source term for the births and a well term for the natural deaths.
+N denotes the total population, that for the timing of this paper,  it will be considered fixed\footnote{Othervise, if longer horizontal timing is considered, it is necessary to consider also a source term for the births and a well term for the natural deaths.
 For further details see \cite{vynnycky2010introduction}}.
@@
 \ref{selling_DID_table_delta} (the estimation of the other parameters is given in Supporting Information D).
-As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is almost two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
+As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is up to two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
 As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.
@@
 \caption{Comparison between the subsides effects for the scenarios where an active vs lazy PM is considered.
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (divided by 4).
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (scaled in order to obtain the week value).
 The error bars, although are visible because are too reduced,  were calculated by considering the error propagation}

### 2021-03-17 Manuscript/manuscript.tex
PUb

@@
 The overall population $N$ was set to 60M,  in order to simulate Italian population.
-Within the daily temporal evolution of this model,  that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package,  we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM impose laws that multiply the $\beta$ factor by $0.7$,  if the normalized infected people are more than 10 the previous threshold he/she will impose with a certain probability restrictions that multiply $\beta$ starting $\beta$ factor by $0.25$;  finally,  if the  threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that multiply $\beta$ by $0.025$.
+Within the daily temporal evolution of this model,  that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces the $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$), if the normalized infected people are more than 10 the previous threshold he/she will impose with a certain probability restrictions that reduce the $\beta$ factor by a multiplicative factor of $0.25$; finally, if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce the $\beta$ a multiplicative factor equal to $0.025$.
 These attenuation parameters were adjusted taking in consideration results of Marziano et al.
@@
 Therefore such trigger make the  R$_{0}$ parameter time dependent,  although in to a discrete way.
-As we said the PM acts with a certain probability,  more formally stochastically: each week a random number (from zero to one) is extracted: if this is higher than a certain threshold,  the relative restrictive decision is taken, otherwise not.
+As we said the PM acts with a certain probability,  more formally stochastically; each week a random number (from zero to one) is extracted: if this is higher than a certain threshold,  the relative restrictive decision is taken, otherwise not.
 The threshold value captures the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one.
@@
 It is worth nothing that here as lock-down we considered only the national one that was applied in the first wave of the epidemics: from March 2020 to June 2020.
-This choice is motivated by the fact that modelling a unique system is more simpler with respect to modelling an ensemble of a communicating clusters that represent regions or provinces: therefore,  if one is interested to model the second wave of pandemics such approach should be undertaken.
-Moreover in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at regional or province level,  and as far as the authors know,  such data are not available.
+This choice is motivated by the fact that modelling a unique system is easier with respect to modelling an ensemble of a communicating clusters that represent regions or provinces: therefore, if one is interested to model the second wave of pandemics such approach should be undertaken.
+Moreover in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at regional or province level,  and as far as the authors know,such data are not available.
 For these reasons here the modelling will be always referred to national data and national lock-downs,  therefore the period after June when starting from October regional lock-down were imposed,  will be not considered.
@@
 It is interesting to point out that the change between the scenarios develops in a discontinuous way as showed in Fig.
-\ref{Phase_transition},   as the reactivity of the PM is changed,  we can consider this as a phase transition of a physical system (it is interesting to point out the closness with respect to the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
+\ref{Phase_transition}, as the reactivity of the PM is changed, we can consider this as a phase transition of a physical system (e.g.
+consider the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
 This explains our choice to consider only two scenarios: indeed we considered only a sample for each phase.

### 2021-03-17 Manuscript/manuscript.tex
PUB

@@
 Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper these categories will be referred as the part of the name labelled in blue.
-}: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, \textcolor{blue}{Appliances}/radios/televisions and
+}: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, Household \textcolor{blue}{Appliances}/radios/televisions and
 tape recorders,\textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
-\textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Household kinds}, \textcolor{blue}{Household tools} and hardware,  \textcolor{blue}{Games}/toys/sports and camping articles.
+\textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Homeware}, \textcolor{blue}{Household tools} and hardware tools, \textcolor{blue}{Games}/toys/sports and camping articles.
 The choice to use sales as a parameter for the evaluation of the lock-down lies on the fact that with them  is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa).
@@
          \includegraphics[width=\textwidth]{Figures/Mobili.pdf}}
-         \caption{\textcolor{OliveGreen}{Household kids} (Orchid)}
+         \caption{\textcolor{OliveGreen}{Homeware} (Orchid)}
          \label{fig:three sin x}
@@
 {\color[HTML]{00009B} Photo-optics}    & -34.14 *** & 2.55  & -13.38 & -52.32 ***  & 3.52  & -14.84 & -7.86 *  & 3.52  & -2.23 \\ \hline
-{\color[HTML]{6200C9} Household kids}   & -10.51 *** & 1.50  & -6.98  & -18.99 ***  & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
+{\color[HTML]{6200C9} Homeware}   & -10.51 *** & 1.50  & -6.98  & -18.99 ***  & 2.07  & -9.13  & -3.61  & 2.07  & -1.74 \\ \hline
 {\color[HTML]{00D2CB} Household tools} & -13.02  *** & 3.51  & -3.70 & -30.23 *** & 4.85  & -6.23    & 2.33   & 4.85  & 0.48  \\ \hline
@@
 {\color[HTML]{00009B} Photo-optics}    & -33.68 ***  & 2.55 & -13.21 & -51.59 ***  & 3.52 & -14.64 & -6.91 & 3.52  & -1.96 \\ \hline
-{\color[HTML]{6200C9} Household kids}   & -10.06  *** & 1.50  & -6.68  & -18.26 *** & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
+{\color[HTML]{6200C9} Homeware}   & -10.06  *** & 1.50  & -6.68  & -18.26 *** & 2.07  & -8.75  & -2.67  & 2.07  & -1.28 \\ \hline
 {\color[HTML]{00D2CB} Household tools} & -12.57 *** & 3.51 & -3.57 & -29.50 ***  & 4.85  & -6.07   & 3.28   & 4.85  & 0.67  \\ \hline
@@
 {\color[HTML]{00009B} Photo-optics}    & 1.71 & 15.18  & 0.11 & 0.84 & 10.99 & 0.07 & 0.70  & 15.18  & 0.11  \\ \hline
-{\color[HTML]{6200C9} Household kids}   & 1.23 & 5.15  & 0.24 & -0.07 & 3.72  & -0.018  & -0.86  & 5.15 & -0.17 \\ \hline
+{\color[HTML]{6200C9} Homeware}   & 1.23 & 5.15  & 0.24 & -0.07 & 3.72  & -0.018  & -0.86  & 5.15 & -0.17 \\ \hline
 {\color[HTML]{00D2CB} Household tools} & 0.26  & 8.78  & 0.03 & -0.21 & 6.36  & -0.03   & 0.14  & 8.79  & 0.97  \\ \hline
@@
 {\color[HTML]{00009B} Photo-optics}    & 102.88 ***  & 0.54  &  189.22 & -7.69 *** & 0.76 & -10.00 & 1.47  & 2.49  & 0.59 \\ \hline
-{\color[HTML]{6200C9} Household kids}   & 102.88 *** & 0.32  & 320.61  & -5.14 *** & 0.45  & -11.33  & 1.47  & 1.47  & 1.00  \\ \hline
+{\color[HTML]{6200C9} Homeware}   & 102.88 *** & 0.32  & 320.61  & -5.14 *** & 0.45  & -11.33  & 1.47  & 1.47  & 1.00  \\ \hline
 {\color[HTML]{00D2CB} Household tools} & 102.88 *** & 0.75  & 137.25 & -2.21 * & 1.06  & -2.08    & 1.47   & 3.43 & 0.43  \\ \hline
@@
 {\color[HTML]{00009B} Photo-optics}    & 1.20 & 1.80  & 0.66 & 1.69 & 2.49 & 0.68  \\ \hline
-{\color[HTML]{6200C9} Household kids}   & 1.20  & 1.06 & 1.12  & 1.69 & 1.47  & 1.15    \\ \hline
+{\color[HTML]{6200C9} Homeware}   & 1.20  & 1.06 & 1.12  & 1.69 & 1.47  & 1.15    \\ \hline
 {\color[HTML]{00D2CB} Household tools} & 1.20 & 2.48  & 0.48 &  1.69  & 3.43  & 0.49   \\ \hline
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Casalinghi.pdf}
-\caption{de-seasoning components  for household kids sales } 
+\caption{de-seasoning components  for Homeware sales } 
 \label{Phase_transition}

### 2021-03-18 Manuscript/manuscript.tex
PUb

@@
 
-Within a standard compartmental model for the description of the dynamic of an epidemics (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically different types of lock-downs.
-The probability that tune this stochastic process reflects his/her different attitude to face an epidemics (e.g.
-\textit{laissez-faire} vs very strict).
-In order to simulate not only an epidemiological scenario but also an economic one we estimated , via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales and on subsidies (\textit{Cassa Integrazione}).
-We found that,  by modifying with continuity the PM attitude  to impose the lock-down a phase transition (as defined for  a physical system) is obtained.
-The comparison of these two scenarios and their impact provide provide a bird's-eye view on the socio-economic consequences of the PM attitude
+Within a standard compartmental model for describing the dynamics of epidemics (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically different types of lock-downs.
+The probability that tunes this stochastic process reflects his/her different attitude to face an epidemics (e.g., \textit{laissez-faire} vs.
+very strict).
+In order to simulate not only an epidemiological scenario but also an economic one, we estimated, via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales and on subsidies (\textit{Cassa Integrazione}).
+We found that by modifying with continuity, the PM attitude to impose the lock-down a phase transition (as defined for a physical system) is obtained.
+The comparison of these two scenarios and their impact provides a bird's-eye view of the socio-economic consequences of the PM attitude
 
@@
 
-The recent pandemic due to the spread of SARS-CoV-2 virus,  opened a highly debated issue about what it would be the best approach of the policy maker to face the epidemic.
-Differently from the past pandemics and in particular of the XX century (e.g.
-Spanish Flu,  Asiatic Flu and Hong-Kong Flu),  for this pandemic a very large amount of data are easily accessible.
-As a consequence not only the modelling of the virus diffusion but also the effect on socio-economic texture for different countries can be investigated with a finer resolution.
-Among the different scientific challenges that can come up in this context,  an interesting one involves socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally the reproduction number, as described in Supporting Information).
-Indeed the policy maker can adopt, at a first approximation,  a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
-In the first extreme,  the spread of virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods are stopped.
-On the other side,  if no lock-down measures are taken by the PM the toll to be paid will not only be the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
-In practice the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion with respect to other (for this purpose a very fine analysis was provided by Li et al.
+The recent pandemic due to the spread of the SARS-CoV-2 virus opened a highly debated issue about the best approach for the policy-maker to face the epidemic.
+Unlike the past pandemics and the XX century (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
+Consequently, the modeling of the virus diffusion and the effect on socio-economic texture for different countries can be investigated with a more satisfactory resolution.
+Among the different scientific challenges that can come up in this context,  an interesting one involves socio-economic effects of the attitude of the policy-maker (PM) to block the circulation of people (lock-down) in order to reduce the contagion rate (more formally, the reproduction number, as described in Supporting Information).
+Indeed the policy-maker can adopt, at a first approximation,  a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
+In the first extreme,  the spread of the virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods is stopped.
+On the other side,  if the PM takes no lock-down measures, the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
+In practice, the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion to others (for this purpose, an excellent analysis was provided by Li et al.
 in  \cite{li2021temporal} and by Brauner et al.
 in \cite{brauner2021inferring}).
-As consequence the lock-down efficacy,  within certain limits,  can be tuned.
-In the literature different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.
-In particular for the model in Ref.
-\cite{kabir2020evolutionary} it is assumed that the policy-maker knows perfectly the consequences of his/her choices and that he/she can act without delay to impose the optimal choice; finally it is assumed that the PM can impose a continuous factor for the lock-down while for different countries such factor seems to be much more discrete.
-It can be argued that most of these drawbacks of this last formidable research, are entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy maker.
-On this basis we would propose here an alternative way to model the decision of the policy maker that is based on a stochastic model instead of on a deterministic one.
-Furthermore,  differently with respect to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at microeconomic level: in particular,  by means of difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
-Thus, the final output of the model will be not only the cumulative deaths,  but also the economic damage for each selling sector.
-Moreover here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary} but there is also average cost for each infected person (referring to Italian data),  because a consistent part of them may be recovered or even should take the intensive therapy.
-As we will show by varying with continuity the probabilistic parameter by which the PM impose the lock-down,  a discontinuity in the SIRD model and in the days of the lock-down was obtained.
-Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.
-For each phase we will discuss the result of the simulation and then we will compare them in order to get a general insight.
+As a consequence, the lock-down efficacy,  within certain limits,  can be tuned.
+In the literature, different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.
+In particular, for the model in Ref.
+\cite{kabir2020evolutionary} it is assumed that the policy-maker knows the consequences of his/her choices ideally and that he/she can act without delay to impose the optimal choice; finally, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range).
+In contrast, for different countries, such a factor seems to be much more discrete (e.g., the PM can reduce the daily contacts only by choosing definite values).
+It can be argued that most of these drawbacks of this last formidable research are entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy-maker.
+On this basis, we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.
+Furthermore,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
+Thus, the final output of the model will be the cumulative deaths and the economic damage for each selling sector.
+Moreover, here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them may be recovered or even should take the intensive therapy.
+As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the SIRD model and the lock-down days was obtained.
+Such behavior belongs to a class of phenomena that, in physical sciences, is called a phase transition.
+For each phase, we will discuss the result of the simulation, and then we will compare them to get a general insight.
 
@@
 
-The model of the present study is composed by an epidemiological part that shapes the diffusion of the virus and then its output is used by the economic model to quantify the damage.
+The model of the present study is composed of an epidemiological part that shapes the diffusion of the virus.
+Then its output is used by the economic model to quantify the damage.
 Thus we will discuss the epidemiological part and then the economic one
@@
 
-Among the very large number of compartmental model available in the literature \cite{vynnycky2010introduction} we considered,  as the simulator of the epidemic diffusion the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
-Our choice is motivated by the fact that this relative simple model provides the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relative small number of parameters\footnote{One in principle can consider a SIRD model,in which the parameters that are time-dependent, as done by Ferrari et al.
+Among the vast number of compartmental models available in the literature \cite{vynnycky2010introduction} we considered,  as the simulator of the epidemic diffusion, the simplest one: the Susceptible-Infectious-Recovered-Dead (SIRD).
+Our choice is motivated by the fact that this relatively simple model provides the gross features of an epidemic \cite{fernandez2020estimating,al2020forecasting} with a relatively small number of parameters\footnote{One in principle can consider a SIRD model, in which the time-dependent parameters, as done by Ferrari et al.
 in Ref.
-\cite{ferrari2020modelling} for the description of Italian situation.
+\cite{ferrari2020modelling} for the description of the Italian situation.
 On the other side it is possible to increase the complexity of the model with other compartments as done in the following paper \cite{giordano2020modelling} by Giordano et al.
-Note that in this last case the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)}).
+Note that in this last case, the resolution of 9 differential equation is required (accompanied by the estimation of a large number of parameters)}.
 The SIRD model, first proposed by Kermack and McKendrick in 1927 \cite{kermack1927contribution},  is given by the following set of differential equations\cite{vynnycky2010introduction}:
@@
 \end{equation}
-where S is the number of people that are still susceptible, I the number of people that are infected and R people that are recovered while D are people that are death.
-N denotes the total population, that for the timing of this paper,  it will be considered fixed\footnote{Othervise, if longer horizontal timing is considered, it is necessary to consider also a source term for the births and a well term for the natural deaths.
+where S is the number of people that are still susceptible, I the number of people that are infected, and R people that are recovered, while D are people that are dead.
+N denotes the total population that for the timing of this paper it will be considered fixed\footnote{Othervise if longer horizontal timing is considered, it is necessary to consider a source term for the births and a well term for the natural deaths.
 For further details see \cite{vynnycky2010introduction}}.
-On the other side $\beta$,$\gamma$ and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality defined  as the probability to die conditionally to be ill).
-Usually epidemiologist are interested in the ratio:
+On the other side, $\beta$,$\gamma$, and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular, $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality defined as the probability to die conditionally to be ill).
+Usually, epidemiologist is interested in the ratio:
 \begin{equation} 
@@
 known as the basic reproduction factor.
-This number is the average number of people that are infected by a single individual and describes if the epidemic is in a negative feedback (R$_{0}$<1),  stationary (R$_{0}$=1),  or in a positive feedback (R$_{0}$>1).
-As consequence if the epidemic is in a negative feedback will be dissipate, while if it is in positive feedback will grow.
-Note that in this simple model, since the parameters are not time dependent this factor is constant.
+This number is the average number of people that a single individual infects and describes if the epidemic is in negative feedback (R$_{0}$<1),  stationary (R$_{0}$=1),  or in positive feedback (R$_{0}$>1).
+As a consequence, if the epidemic is within a negative feedback will be dissipated, while if it is in positive feedback will grow.
+Note that in this simple model, since the parameters are not time-dependent, this factor is constant.
 As performed by Ferrari et al.
-\cite{ferrari2020modelling},  when time dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ become time depended: thus scholar rename it as $R_{t}$.
-For the present work,  we limited to constant parameters: in particular we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
-The $\mu$ was set in order to keep in to account the calculated lethality for Italy: 1 \% \cite{fernandez2020estimating} (see also the very fine analysis made by the Institute for International Political Studies (ISPI) \cite{ISPI})\footnote{The authors are aware that this ratio is far from being homogeneus for the the different ages of population: however if this factor is taken into account,  it requires the solution of a system of partial derivative equations.
-In this case the numerical calculations become much more complicated}.
-The overall population $N$ was set to 60M,  in order to simulate Italian population.
-Within the daily temporal evolution of this model,  that was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every 7 days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces the $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$), if the normalized infected people are more than 10 the previous threshold he/she will impose with a certain probability restrictions that reduce the $\beta$ factor by a multiplicative factor of $0.25$; finally, if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce the $\beta$ a multiplicative factor equal to $0.025$.
-These attenuation parameters were adjusted taking in consideration results of Marziano et al.
+\cite{ferrari2020modelling},  when time-dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ become time depended: thus scholar rename it as $R_{t}$.
+For the present work,  we limited to constant parameters.
+In particular, we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
+The $\mu$ was set in order to keep in to account the calculated lethality for Italy: 1 \% \cite{fernandez2020estimating} (see also the excellent analysis made by the Institute for International Political Studies (ISPI) \cite{ISPI})\footnote{The authors are aware that this ratio is far from being homogeneous for the different ages of the population: however if this factor is taken into account,  it requires the solution of a system of partial derivative equations.
+In this case, the numerical calculations become much more complicated}.
+The overall population $N$ was set to 60M to simulate the Italian population.
+Within the daily temporal evolution of this model, which was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every seven days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces the $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$) if the normalized infected people are more than ten the previous threshold he/she will impose with certain probability restrictions that reduce the $\beta$ factor by a multiplicative factor of $0.25$; finally if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce the $\beta$ a multiplicative factor equal to $0.025$.
+These attenuation parameters were adjusted, considering the results of Marziano et al.
 in Ref.
 \cite{marziano2021retrospective}.
-Therefore such trigger make the  R$_{0}$ parameter time dependent,  although in to a discrete way.
-As we said the PM acts with a certain probability,  more formally stochastically; each week a random number (from zero to one) is extracted: if this is higher than a certain threshold,  the relative restrictive decision is taken, otherwise not.
-The threshold value captures the PM attitude to impose the lock-down: lower values model a careful PM, hight value a lazy one.
-In this way the model is able to simulate different scenarios for the different PM attitude: as we will see this can produce two very different results.
-At the end of the simulation,  beside the values given by the standard SIRD model (recovered and deaths),  the algorithm also provide the number of weeks in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
-It is worth nothing that here as lock-down we considered only the national one that was applied in the first wave of the epidemics: from March 2020 to June 2020.
-This choice is motivated by the fact that modelling a unique system is easier with respect to modelling an ensemble of a communicating clusters that represent regions or provinces: therefore, if one is interested to model the second wave of pandemics such approach should be undertaken.
-Moreover in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at regional or province level,  and as far as the authors know,such data are not available.
-For these reasons here the modelling will be always referred to national data and national lock-downs,  therefore the period after June when starting from October regional lock-down were imposed,  will be not considered.
-Another point that is it is worth mentioning,  is that in this model, on the contrary with respect to the SIS one, individual can not re-infect: concerning the COVID-19 the possibility of reinfection is still discussed among scholars \cite{ledford2020covid,iwasaki2021reinfections}.
-Basically to the know of author it is established that the immunity last at least 8 months  \cite{dan2021immunological} and very few cases of reinfection are reported.
-Thus the immunity considered in the model,  for an interval of one year seems almost  a realistic approximation.
+Therefore such a trigger makes the  R$_{0}$ parameter time-dependent,  although in a discrete way.
+As we said, the PM acts with a certain probability,  more formally stochastically; each week, a random number (from zero to one) is extracted: if this is higher than a certain threshold,  the relative restrictive decision is taken, otherwise not.
+The threshold value captures the PM attitude to impose the lock-down: lower values model a careful PM, high value a lazy one.
+In this way, the model can simulate different scenarios for the different PM attitudes: as we will see, this can produce two very different results.
+At the end of the simulation, besides the values given by the standard SIRD model (recovered and deaths),  the algorithm also provides the number of weeks in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
+It is worth noting that here as lock-down, we considered only the national one applied in the first wave of the epidemics: from March 2020 to June 2020.
+This choice is motivated by the fact that modeling a unique system is easier concerning modeling an ensemble of communicating clusters that represent regions or provinces: therefore, if one is interested in modeling the second wave of pandemics, such an approach should be undertaken.
+Moreover, in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at the regional or province level,  and as far as the authors know, such data are not available.
+For these reasons here the modeling will always be referred to as national data and national lock-downs.
+Therefore, the period after June, when starting from October, regional lock-down, will not be considered.
+Another point that is worth mentioning is that in this model, on the contrary concerning the SIS one, individuals can not re-infect: concerning the COVID-19, the possibility of reinfection is still discussed among scholars \cite{ledford2020covid,iwasaki2021reinfections}.
+As far as the authors know, it is established that the immunity lasts at least eight months  \cite{dan2021immunological} and very few reinfection cases are reported.
+Thus the immunity considered in the model for one year seems almost a realistic approximation.
 
@@
 
-The economic impact for each epidemiological scenario is shaped as follow: a first set of parameters,  as the economic value of a death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on selling for different areas and on the unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
+The economic impact for each epidemiological scenario is shaped as follow: the first set of parameters,  as the economic value of death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on selling for different areas and on unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
 Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
-This choice is based on the idea that,  if the PM acts improperly,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and than,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is keep into account.
-In this case however a system of partial differential equation should be solved making the calculation and the computational cost incredibly high.}.
-Beside this impact,  there is also the cost associated to the medical care of each ill people,  for this we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another import health-care impact due to the fact that the ill people for COVID-19 saturate the health system thus making it unreachable for other diseases.
-This spillover translates in to more death and more ill people with respect to the baseline situation where there isn't an pandemic: however,  by now,  this effect is difficult to quantify and so we did not included in to the present model}.
-Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper these categories will be referred as the part of the name labelled in blue.
+This choice is based on the idea that,  if the PM misbehaves,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and then,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is taken into account.
+However, a partial differential equations system should be solved, making the calculation and the computational cost incredibly high.}.
+Besides this impact,  there is also the cost associated with the medical care of each ill people.
+For this, we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another import health-care impact because the ill people for COVID-19 saturate the health system thus making it unreachable for other diseases.
+This spillover translates into more death and more ill people for the baseline situation where there is not a pandemic: however,  by now,  this effect is difficult to quantify, and so we did not include it in the present model}.
+Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper, these categories will be referred to as the part of the name labeled in blue.
 }: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, Household \textcolor{blue}{Appliances}/radios/televisions and
@@
 \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Homeware}, \textcolor{blue}{Household tools} and hardware tools, \textcolor{blue}{Games}/toys/sports and camping articles.
-The choice to use sales as a parameter for the evaluation of the lock-down lies on the fact that with them  is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can be also considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also a fixed taxation (accisa).
+The choice to use sales as a parameter for the evaluation of the lock-down lies in the fact that with them is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can also be considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also fixed taxation (accisa).
 Such calculation may be considered as a future outlook of this work}.
 Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
-In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the government for the firms that were damaged the lock-down restrictions.
-For the empirical evaluation of the impact on selling and unemployment benefit we performed a multiple time Difference in Difference as presented in Refs.
+In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the Government for the firms that were damaged by the lock-down restrictions.
+For the empirical evaluation of the impact on selling and unemployment benefit, we performed a multiple time Difference in Difference as presented in Refs.
 \cite{draca2011panic},  \cite{imbens2009recent} and \cite{wooldridge2012introductory}.
@@
 \end{equation}
-where $Y$ is the selcted outcome, $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group and $\epsilon$ a error term.
-As control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless with respect to the lock-down\footnote{Although it is true that a slight increase of food sales during the lock-down is present in the plots in Fig.
+where $Y$ is the selected outcome (sales or subsidies), $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group, and $\epsilon$ an error term.
+As a control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless for the lock-down\footnote{Although it is true that a slight increase of food sales during the lock-down is present in the plots in Fig.
 \ref{Selling_plots} \ref{Selling_plots_II},  it must be stressed the fact that, as proven numerically in the Supporting Info A, this change does not significantly affect the DID estimations }.
 On the other side,  for subsidies \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
-This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labour cost but at same time guaranteeing to the workers part of their original salary \footnote{It is worth nothing that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
-However in the present study we consider,for simplicity,  only the sectors covered by Cassa Integrazione Ordinaria.
+This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labor cost but at the same time guaranteeing to the workers part of their original salary \footnote{It is worth noting that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact, there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
+However, in the present study, we consider, for simplicity,  only the sectors covered by Cassa Integrazione Ordinaria.
 }.
-During the first months of the pandemic firms,  following the rules stated by the Italian Governament (Decreto Cura Italia \cite{curaitalia}),  firms that would reduce their labour cost,  first forced the employees to use their holiday budget and than,  after it was run out,  they put the employees in to the Cassa Integrazione Ordinaria.
-Thus the Cassa Integrazione Straordinaria-Solidarietà can be considered as not treated by the first wave of the lock-down while the ordinary one the treated.
-The DID considered here has three different times for the national lock-down:  for the sales we considered,  as  done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down and June 2020 as weak lock-down.
-On the other side concerning the subsidies,  we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the subsidies for workers was slightly delayed basically due to the fact that firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as consequence,  because of this buffer effect,  in the month of March there is no significant effect of this subsidies although there is a significant reduction of hours worked (see e.g.
-\cite{istat_lavoro}).
-Performing the DID we estimated the coefficients for the effect of each intensity of lock-down on sales and subsidies,  then we we rescaled them for a week.
-Finally we multiplied the number obtained from the previous calculation by the number of lock-down weeks,  with the respective intensity,  in each scenario simulated via the epidemiological model described before.
-As consequence we obtained,  for each scenario,  an economics simulation based on parameters obtained from an empirical evaluation.
+During the first months of the pandemic,  following the rules stated by the Italian Government (Decreto Cura Italia \cite{curaitalia}),  firms that would reduce their labor cost first forced the employees to use their holiday budget and then,  after it was run out,  they put the employees into the Cassa Integrazione Ordinaria.
+Thus the Cassa Integrazione Straordinaria-Solidarietà can be considered as not treated by the first wave of the lock-down, while the ordinary one treated.
+The DID consider here has three different times for the national lock-down:  for the sales, we considered,  as done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
+On the other side concerning the subsidies,  we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the subsidies for workers was slightly delayed because firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as a consequence,  because of this buffer effect,  in March there is no significant effect of this subsidies although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
+Performing the DID, we estimated the coefficients for each intensity of lock-down on sales and subsidies.
+Then these were rescaled in order to obtain a weekly value.
+Finally, we multiplied the number obtained from the previous calculation by the number of lock-down weeks,  with the respective intensity,  in each scenario simulated via the epidemiological model described before.
+As a consequence, we obtained,  for each scenario,  an economics simulation based on parameters obtained from an empirical evaluation.
 
@@
 The monthly sales data were retrieved from the National Institute of Statistics website \cite{istat}.
-In particular we considered the period starting from 2018 up to June 2020.
-The choice to not consider the months after June and in particular the last part of the year lies on the fact that in the latter lock-downs were imposed at regional level and not to national level \footnote{With the only exception of Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for regional cluster.
-Moreover if regional cluster were considered it was necessary to model an ensemble of SIRD model that communicate each other with a defined rate (that change also with respect to the lock-down restriction).
-This make the model much more complicated.
-However if all the data that are necessary for performing the analysis will become available the author may consider, as an outlook, to extend the present analysis to regional clusters}.
-As discussed in Supporting Information,  these data were not de-seasoned: thus we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
+In particular, we considered the period starting from 2018 up to June 2020.
+The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not to national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
+Moreover, if regional clusters were considered, it was necessary to model an ensemble of SIRD models that communicate with a defined rate (that change also with respect to the lock-down restriction).
+This makes the model much more complicated.
+However, if all the necessary data for performing the analysis will become available, the author may consider, as an outlook, extending the present analysis to regional clusters}.
+As discussed in Supporting Information,  these data were not de-seasoned.
+Thus, we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
 The decomposition results are reported in the Supporting Info E.
-Concerning subsidies we retried the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
-It is worth nothing that here we considered only the authorized subsidies and not the asked one .
-Furthermore these data,  differently with respect to the sales one were not affected by seasonality noise,  and thus no de-seasoning was necessary.
-We checked also if any significant effect on DID coefficient was obtained for sales and for subsidies by adding one and two year before 2018 (e.g.
-2016 and 2017): no significant effect was found.
+Concerning subsidies we retrieved the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+It is worth noting that we considered only the authorized subsidies and not the asked ones.
+Furthermore,  differently for the sales, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
+We also checked if any significant effect on the DID coefficient was obtained for sales and subsidies by adding one and two years before 2018 (e.g., 2016 and 2017): no significant effect was found.
 
@@
 
-As done for the section Model and methods we will divide the discussion of the results in the following way: first the outcomes of the economic model will be presented,  then basing on this result,  we will discuss the  scenarios obtained with them via the epidemiological model.
-Finally we will discuss the overall results.
+As done for the section Model and methods, we will divide the discussion of the results in the following way: first, the outcomes of the economic model will be presented,  then basing on this result,  we will discuss the scenarios obtained with them via the epidemiological model.
+Finally, we will discuss the overall results.
 
@@
 \ref{selling_DID_table_delta} (the estimation of the other parameters is given in Supporting Information D).
-As one can point out from the plots,  it is true that there is a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is up to two order of magnitude lesser with respect to the slope in the lock-down T$_{1}$ and $T_{2}$.
-As consequence this pre-trend,  compared to the lock-down effect,  can be considered negligible.
-In order to make a further control,  a placebo test was performed by choosing timing before the pandemic of COVID19.
-As illustrated in the Supporting Info C,  this test was successful.
-On the other side,  concerning $T_{3}$  (low lock-down),  only the effect for clothing and footwear can be considered significant,  also by considering the pre-trend slope as discussed in the Supporting Information.
-Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations,  only the clothing and footwear sectors.
+As one can point out from the plots, there is indeed a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is up to two orders of magnitude lesser for the slope in the lock-down T$_{1}$ and $T_{2}$.
+Consequently, this pre-trend,  compared to the lock-down effect,  can be considered negligible.
+As a further check,  a placebo test was performed by choosing timing before the pandemic of COVID19.
+As illustrated in Supporting Info C,  this test was successful.
+On the other side,  concerning $T_{3}$  (low lock-down),  only the effect for clothing and footwear can be considered significant.
+Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations,  only the clothing, and footwear sectors.
 By inspecting the Tab.
-\ref{selling_DID_table_delta} we see that the most severe damage of lock-down hit the clothing,  and the footwear.
-On the other side the Household kids and the Household tools seems lesser affected by the lock-down.
-The same DID regression was used  for the subsidies,  using as control group the extraordinary solidarity subsidies (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
-\ref{CIG_sector_plots} and in Tab \ref{CIG_DID}.
+\ref{selling_DID_table_delta} we see that the most severe lock-down damage hit the clothing and the footwear.
+On the other side, the Household kids and the Household tools seem lesser affected by the lock-down.
+The same DID regression was used for the subsidies,  using as the control group the extraordinary solidarity subsidies (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
+\ref{CIG_sector_plots} and Tab \ref{CIG_DID}.
 Also in this case the placebo tests were successfully performed.
-An interesting insight is also provided by the inspection of the extraordinary subsidies for renovation ( \textit{cassa integrazione ristrutturazione}): these subsidies,  as compared to the solidarity ones,  seems much more sensitive with respect to external shock in particular for trade sector.
+An interesting insight is also provided by the inspection of the extraordinary subsidies for renovation ( \textit{cassa integrazione ristrutturazione}): these subsidies, compared to the solidarity ones, seem much more sensitive for an external shock in particular for the trade sector.
 
@@
 
-Now that we have the parameters for the economic impact given by the lock-downs,  we are ready to discuss the simulations that output the epidemiological and economic consequences of the attitude of PM.
+Now that we have the parameters for the economic impact given by the lock-downs,  we are ready to discuss the simulations that output the epidemiological and economic consequences of PM's attitude.
 In Tab.
@@
 \ref{Selling_sector_effects} and \ref{CIG_sector_effects}.
-In order to assure the \textit{ceteris pariubus} condition we used for both scenario the same set of random numbers.
-First,  we see that where the PM is more reactive we have small different waves of epidemics,  while if the PM is poorly reactive only one intense wave is present,  indeed in the latter scenario the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: when the PM acts is too late,  as shown in Fig.
-\ref{SIRD_scenario}, since the pandemics has almost hit the large part of the population.
+To assure the \textit{ceteris pariubus} condition, we used the same set of random numbers for both scenarios.
+First,  we see that where the PM is more reactive, we have different small epidemics waves.
+In contrast, if the PM is poorly reactive, only one intense wave is present,  indeed in the latter scenario, the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: when the PM acts is too late,  as shown in Fig.
+\ref{SIRD_scenario}, since the pandemic has almost hit the large part of the population.
 This can be pointed out in Fig.
-\ref{R_t_scenarios} by noting that that the reproduction factor remains at its maximum level for large number of weeks after the beginning of the pandemic.
-This also explains why in the second half of the scenario the lock-downs are so week: the remaining part of the population is immune.,  an thus no further action is required.
-On the contrary in the first scenario the PM is able,  using the lock-downs to transform the SIRD peak in to small waves (Fig.
+\ref{R_t_scenarios} by noting that that the reproduction factor remains at its maximum level for a large number of weeks after the beginning of the pandemic.
+This also explains why the lock-downs are so week in the second half of the scenario: the remaining part of the population is immune.
+Thus, no further action is required.
+On the contrary, in the first scenario, the PM can use the lock-downs to transform the SIRD peak into small waves (Fig.
 \ref{SIRD_scenario}).
@@
 \ref{R_t_scenarios} this result is basically obtained by keeping the reproduction factor in the value of medium lock-down value.
-These two theoretical model correspond,  in practice,  for the lazy PM to the one considered by the PMs that aimed to heard immunity,  while,  concerning the active-PM,  to the PMs that would not saturate the saturate the health system and aimed to reduce the death at the minimum.
-It is interesting to point out that the change between the scenarios develops in a discontinuous way as showed in Fig.
-\ref{Phase_transition}, as the reactivity of the PM is changed, we can consider this as a phase transition of a physical system (e.g.
-consider the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
-This explains our choice to consider only two scenarios: indeed we considered only a sample for each phase.
-It is worth nothing that a similar result,  within a different epidemiological model,  was obtained by Balcan and Vespignani in Ref.
+These two theoretical models correspond,  in practice,  for the lazy PM to the one considered by the PMs that aimed to herd immunity.
+At the same time,  concerning the active-PM,  to the PMs that would not saturate the health system and aimed to reduce the death at the minimum.
+It is interesting to point out that the change between the scenarios develops in a discontinuous way as shown in Fig.
+\ref{Phase_transition}, as the reactivity of the PM is changed, we can consider this as a phase transition of a physical system (e.g., consider the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
+This explains our choice to consider only two scenarios: indeed, we considered only a sample for each phase.
+It is worth noting that a similar result,  within a different epidemiological model,  was obtained by Balcan and Vespignani in Ref.
 \cite{Vespignani}.
-The explanation of this similar behaviour is that both model have a stochastic component,  that as pointed out by Balcan and Vespignani,  give the phase transition: indeed while in their model this was directly related to the contagion probability,  here this is indirectly made stochastically by the decision of PM that modify the $\beta$ parameter and so the transmission rate.
-Moving to the socio-economic outcome of the model used we see, from Tab.
-\ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost},  that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by a consistent use of the confinement.
+The explanation of this similar behavior is that both models have a stochastic component,  that as pointed out by Balcan and Vespignani, gives the phase transition.
+While in their model, this was directly related to the contagion probability, this is indirectly made stochastically by PM's decision that modifies the $\beta$ parameter and so the transmission rate.
+Moving to the socio-economic outcome of the model used, we see, from Tab.
+\ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost},  that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by consistent use of the confinement.
 This has an immediate drawback on the economic data: as shown in Fig.
-\ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the loses for selling and the use of subsidies are widely large with respect to the one-wave scenario.
-In principle one can be attempted to find the PM attitude that minimize the overall cost (deaths,  infected,  selling and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for a life in terms of compensation,  the actual criminal law does not consider an amount of money comparable to a money sum,  on contrary it gives a value ex post not ex ante.
-For this reason here we considered the epidemiological consequences separated with respect to the economic ones.
-A more intriguing issue is come up when the economic cost is causally associated to an number indirect of deaths (for instance if people does not have the money for food or other first necessity goods ),  in this case the two factor (epidemiological and economic) can be,  in principle,  summed.
-We say in principle because the jurisprudence is here very reduced or totally missing since the pandemics are rare events.
-For the present study these indirect deaths are,  by now,  not easily to quantify and thus we did not considered this option.
+\ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the losses for selling and the use of subsidies are widely large concerning the one-wave scenario.
+In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  selling, and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante.
+For this reason, here, we considered the epidemiological consequences separated from the economic ones.
+A more intriguing issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle,  summed.
+We say in principle because the jurisprudence is significantly reduced or missing since the pandemics are rare.
+For the present study, these indirect deaths are,  by now,  not easy to quantify, and thus, we did not consider this option.
 
@@
 
-We have obtained a model that combines the epidemiological aspects as well the economic ones within a stochastic approach.
-This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales sector as well on the subsidies dedicated to firms that would reduce the labour cost.
-Furthermore we show numerically that,  within a stochastic approach,  the PM attitude to impose the lock-downs is critical,  as this attitude,  within a \textit{ceteris paribus} condition,  decide the phase of the outcome scenario and thus the economic and social effects.
+We have obtained a model that combines the epidemiological aspects and the economic ones within a stochastic approach.
+This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales sectors and the subsidies dedicated to firms that would reduce the labor cost.
+Furthermore, we show numerically that,  within a stochastic approach,  the PM attitude to impose the lock-downs is critical.
+Within a \textit{ceteris paribus} condition, this attitude decides the phase of the outcome scenario and thus the economic and social effects.
 
@@
      \end{subfigure}
-\caption{Selling data (I), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
-The timing for each lock-down is marked with a dashed line: red for high, orange medium and green for low.
-Note that despite there is a pre-trend this is negligible with respect to the slope of medium and high lock-down slopes}
+\caption{Sales data (I), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+The timing for each lock-down is marked with a dashed line: red for high, orange medium, and green for low.
+Note that despite there is a pre-trend, this is negligible for the slope of medium and high lock-down slopes}
 \label{Selling_plots}
@@
 \caption{Selling data (II), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
-The timing for each lock-down is marked with a dashed line: red for high, orange medium and green for low.
-Note that despite there is a pre-trend this is negligible with respect to the slope of medium and high lock-down slopes}
+Each lock-down timing is marked with a dashed line: red for high, orange medium, and green for low.
+Note that despite there is a pre-trend, this is negligible for the slope of medium and high lock-down slopes}
 \label{Selling_plots_II}
@@
 \begin{flushleft}
-$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
+$\delta$ coefficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
 The values of the intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Info.
@@
      \end{subfigure}
-\caption{Comparison between the ordinary subsides (blue)   vs the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total.
-The dashed lines represent the different timing  and intensity for the lock-down:  red for high, orange medium and green for low.
+\caption{Comparison between the ordinary subsidies (blue)   vs.
+the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total.
+The dashed lines represent the different timing and intensity for the lock-down:  red for high, orange medium, and green for low.
 }
@@
  \includegraphics[width=0.5\textwidth]{Figures/Phase_transition.pdf}
-\caption{The number of deaths of SIRD scenario with stochasic lockdown as obtained by chaing the PM attitute to active the lockdown (e.g.
-by modifying the probability parameter by which the lock-down is imposed).
-As the PM attitude is near 1.3 a sharp discontinuity is present in the overall death: thus a different phase is obtained.
-It is worth nothing the similarity of this plot with the gold-standard one of phase transition: the Ising model (see \cite{Ising} or \cite{Ising_2} for a more deep analysis)}
+\caption{The number of deaths of SIRD scenario with stochastic lockdown as obtained by changing the PM attitude to active the lockdown (e.g., by modifying the probability parameter by which the lockdown is imposed).
+As the PM attitude is near 1.3, a sharp discontinuity is present in the overall death: thus, a different phase is obtained.
+It is worth noting the similarity of this plot with the gold-standard one of phase transition: the Ising model (see \cite{Ising} or \cite{Ising_2} for a more profound analysis)}
 \label{Phase_transition}
@@
      \end{subfigure}
-\caption{Comparison between the reproduction number (calculated as effective the $\frac{\beta}{\gamma+\mu}$ ratio when the lock-down is applied) for a highly reactive PM vs to the one of a poorly reactive one.
-It can be noted that while in the former the PM reactivity almost allows him/her to control this factor in to a stable medium lock-down,  in the second one the reproduction number (and thus the epidemic) is almost out of control of the PM since it remains,  for most of weeks at its maximum level.
-In particular in the second scenario,  the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: when the PM act is too late since the pandemics has almost hit the large part of the population.
-This also explain why in the second half of the scenario the lock-downs are so week: the remaining part of the population is immune.
-On the contrary in the first scenario the PM is able,  using the lockdown to transform the sharp SIRD peak in to small waves.
-Note that the levels of reproduction number are discrete,  as marked by the dashed lines (green low,  orange medium,  red high) since the lock-down is the only way to change this number.
-On the contrary if a time dependent SIRD was considered as done by \cite{ferrari2020modelling},  a continuous form of R(t) would be obtained}
+\caption{Comparison between the reproduction number (calculated as effective the $\frac{\beta}{\gamma+\mu}$ ratio when the lock-down is applied) for a highly reactive PM vs.
+to the one of a poorly reactive one.
+It can be noted that while in the former the PM reactivity almost allows him/her to control this factor into a stable medium lock-down,  in the second one, the reproduction number (and thus the epidemic) is almost out of control of the PM since it remains,  for most of the weeks at its maximum level.
+In particular, in the second scenario, PM's laziness to apply the lock-down in the first weeks produces the full infection peak of the standard SIRD model: when the PM act is too late since the pandemics have almost hit a large part of the population.
+This also explains why the lock-downs are so week in the second half of the scenario: the remaining part of the population is immune.
+On the contrary, in the first scenario, the PM can use the lock-down to transform the sharp SIRD peak into small waves.
+Note that the reproduction number levels are discrete,  as marked by the dashed lines (green low,  orange medium,  red high) since the lock-down is the only way to change this number.
+On the contrary, if a time-dependent SIRD were considered as done by \cite{ferrari2020modelling},  a continuous form of R(t) would be obtained
+}
 \label{R_t_scenarios}
@@
 \caption{Comparison between the epidemiological scenarios obtained via a SIRD model (Susceptible-Infectious-Recovered-Dead) where the PM impose stochastically the different levels of the lock-down.
-In the left panel an active PM is considered: this is modelled by making more likeable that the PM impose the lock-down as the number of infected goes over the different thresholds.
-On the contrary,  in the left panel a lazy PM that prefer the \textit{laissez-faire} approach is considered: in this case,  differently with respect to the previous scenario, the probability that the PM impose the lock-down  is less likely.
+In the left panel, an active PM is considered: this is modeled by making it more likable that the PM imposes the lock-down as the number of infected goes over the different thresholds.
+On the contrary,  in the left panel, a lazy PM that prefers the \textit{laissez-faire} approach is considered: in this case,  differently from the previous scenario, the probability that the PM imposes the lock-down is less likely.
 }
@@
 \caption{Comparison between the sales effects for the scenarios where an active vs lazy PM is considered.
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (divided by 4).
-The error bars were calculated by considering the error propagation  }
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
+The error bars were calculated by considering the error propagation
+ }
 \label{Selling_sector_effects}
@@
      \end{subfigure}
-\caption{Comparison between the subsides effects for the scenarios where an active vs lazy PM is considered.
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks, obtianed from the SIRD scenario ,with the coefficients obtained from the DID (scaled in order to obtain the week value).
-The error bars, although are visible because are too reduced,  were calculated by considering the error propagation}
+\caption{Comparison between the subsides effects for the scenarios where an active vs.
+lazy PM is considered.
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
+The error bars, although they are visible because they are too reduced,  were calculated by considering the error propagation}
 \label{CIG_sector_effects}
@@
 In order to check if any significant effect is obtained on the coefficients of Tab.
-\ref{selling_DID_table_delta_phantom} by the slight increase of food consumption during the lockdown,  we considered an hypothetical scenario were this increase did not happened (e.g.
+\ref{selling_DID_table_delta_phantom} by the slight increase of food consumption during the lockdown,  we considered a hypothetical scenario where this increase did not happen (e.g.
 the selling for March to June were identical to February): as one can point out by comparing the Tab.
 \ref{selling_DID_table_delta_phantom} with Tab, \ref{selling_DID_table_delta} no significant difference can be found.
-Thus since the real scenario where this increase happened (real one), and the scenario where this did not happened (hypothetical one) are indistinguishable,  we can consider this increase negligible for the estimation of the DID $\delta$ coefficients
+Thus since the real scenario where this increase happened (the real one) and the scenario where this did not happen (hypothetical one) are indistinguishable,  we can consider this increase negligible for the estimation of the DID $\delta$ coefficients
 
@@
 \begin{flushleft}
-$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} for the different lock-down timings where the food selling are modified in order to have,  during the lockdown timings, the same constant value of February.
-Note that no significant difference can be found with respect to the coeffient obtained in Tab \ref{selling_DID_table_delta}.
+$\delta$ coefficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} for the different lock-down timings where the food selling are modified in order to have,  during the lock-down timings, the same constant value of February.
+Note that no significant difference can be found with respect to the coefficient obtained in Tab \ref{selling_DID_table_delta}.
 \end{flushleft}

### 2021-03-18 Manuscript/manuscript.tex
PUB

@@
 }: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, Household \textcolor{blue}{Appliances}/radios/televisions and
-tape recorders,\textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
+tape recorders, \textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
 \textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Homeware}, \textcolor{blue}{Household tools} and hardware tools, \textcolor{blue}{Games}/toys/sports and camping articles.
@@
 Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
+Furthermore also the total value (considering also other sectors that were not analysed here).
 In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the Government for the firms that were damaged by the lock-down restrictions.
@@
 The monthly sales data were retrieved from the National Institute of Statistics website \cite{istat}.
-In particular, we considered the period starting from 2018 up to June 2020.
+In particular, we considered the period starting from June 2018 up to June 2020 for the eight categories described in the previous section .
 The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not to national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
@@
 The decomposition results are reported in the Supporting Info E.
-Concerning subsidies we retrieved the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+Concerning monthly subsidies paid we retrieved the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+Here the period considered also starts from June 2018 up to June 2020 for the four categories described in the previous section.
 It is worth noting that we considered only the authorized subsidies and not the asked ones.
 Furthermore,  differently for the sales, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
-We also checked if any significant effect on the DID coefficient was obtained for sales and subsidies by adding one and two years before 2018 (e.g., 2016 and 2017): no significant effect was found.
 
@@
                                        & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
-{\color[HTML]{343434} Total}        & 706 ***   & 3     & 199.5  & 217  ***  & 3     & 61.48 & 144  ***  & 3     & 40.72 \\ \hline
-{\color[HTML]{343434} Manufacture}  & 494  ***  & 3     & 158.56 & 162  ***  & 3     & 52    & 111   *** & 3     & 35.7  \\ \hline
-{\color[HTML]{343434} Trade}        & 16.4  *** & 0.24  & 66.10  & 3.72 ***  & 0.24  & 15.00 & 2.92  *** & 0.24  & 11.78 \\ \hline
-{\color[HTML]{343434} Construction} & 134  ***   & 0.87  & 153.10 & 29  ***   & 0.87  & 33.13 & 14   ***  & 0.87  & 16.41 \\ \hline
+{\color[HTML]{343434} Total}        & 706 ***   & 3.8     & 181  & 217  ***  & 3.8     & 55.98 & 144  ***  & 3.88     & 37.07 \\ \hline
+{\color[HTML]{343434} Manufacture}  & 494  ***  & 3.4     & 143 & 162  ***  & 3.4     & 46.91    & 111   *** & 3.4     & 32.17  \\ \hline
+{\color[HTML]{343434} Trade}        & 16.4  *** & 0.21  & 75.35  & 3.68 ***  & 0.21  & 16.9 & 2.88  *** & 0.21  & 13.27 \\ \hline
+{\color[HTML]{343434} Construction} & 134  ***   & 0.54  & 249 & 29  ***   & 0.54  & 54.45 & 14   ***  & 0.54  & 27.28 \\ \hline
 \label{CIG_DID}

### 2021-03-18 Analisi_vendite/Test vari/DID_files/DID_code_dest.R

@@ -1,11 +1,16 @@
 library(readxl)
 
 Dati_Abbigliamento <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Abbigliamento")
+Dati_Abbigliamento_long <- read_excel("Dati_destagionalizzati_DID_full.xlsx", sheet = "Abbigliamento")
 Dati_Abbigliamento_phantom <- read_excel("Dati_destagionalizzati_DID_phantom.xlsx", sheet = "Abbigliamento")
 
 
 Abbigliamento <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Abbigliamento )
 summary(Abbigliamento)
+
+
+Abbigliamento_long <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Abbigliamento_long )
+summary(Abbigliamento_long)
 
 Abbigliamento_phantom <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Abbigliamento_phantom )
 summary(Abbigliamento_phantom)
@@ -15,10 +20,15 @@ summary(Abbigliamento_placebo)
 
 
 Dati_Calzature <- read_excel("Dati_destagionalizzati_DID.xlsx", sheet = "Calzature")
+Dati_Calzature_long <- read_excel("Dati_destagionalizzati_DID_full.xlsx", sheet = "Calzature")
 Dati_Calzature_phantom <- read_excel("Dati_destagionalizzati_DID_phantom.xlsx", sheet = "Calzature")
 
 Calzature <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Calzature)
 summary(Calzature)
+
+
+Calzature_long <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Calzature_long)
+summary(Calzature_long)
 
 Calzature_phantom <-lm(Outcome ~  C + T1 + T2+T3 + C*T1 +C*T2+C*T3, data = Dati_Calzature_phantom)
 summary(Calzature_phantom)
@@ -28,10 +38,15 @@ summary(Calzature_placebo)
 
 
[…]

### 2021-03-18 Analisi_vendite/Test vari/Destag_Full_check.R

@@ -1,6 +1,7 @@
 library(readxl)
 library(ggplot2)
 Data <- read_excel("Dati_destagionalizzati.xlsx")
+Data2 <- read_excel("Dati_destagionalizzati_FULL_2016.xlsx")
 
 Controllo_abbigliamento<-lm(Data$Abbigliamento[1:19]-Data$Alimentari[1:19]~Data$Time[1:19])
 summary(Controllo_abbigliamento)
@@ -131,15 +132,24 @@ summary(reg10)
 
 
 
-
+Data2
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
+  labs(title="Abbigliamento")
+
+ggplot(data=Data2,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
   labs(title="Abbigliamento")
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Calzature),color = "darkgreen")+ 
   labs(title="Calzature")
 
+ggplot(data=Data2,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Calzature),color = "darkgreen")+ 
+  labs(title="Calzature")
+
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Elettrodomestici),color = "orange")+ 
+  labs(title="Elettrodomestici")
+
+ggplot(data=Data2,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Elettrodomestici),color = "orange")+ 
   labs(title="Elettrodomestici")
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Mobili),color = "purple")+ 
@@ -151,13 +161,22 @@ ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_
[…]

### 2021-03-18 Analisi_vendite/Test vari/tentativo_destagionalizzazione.R

@@ -292,22 +292,6 @@ plot(decompose_beer)
 
 
 
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
 ggplot(data=Produzione,aes(x=Data,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Data,y=Legno_carta),color = "blue")+geom_line(size=2,aes(x=Data,y=Gomma),color = "green")+geom_line(size=2,aes(x=Data,y=Computer),color = "orange")+geom_line(size=2,aes(x=Data,y=ElettronicaM),color = "purple")+geom_line(size=2,aes(x=Data,y=Calzature),color = "darkgreen")+geom_line(size=2,aes(x=Data,y=Farmaceutici),color = "black")+ylim(0, 150)
 
 
@@ -353,6 +337,278 @@ summary(test_calzature)
 
 
 
+
+
+
+
+Destagionalizzazione <- read_excel("Destagionalizzazione_2016.xlsx")
+
+TS_Alimentare = ts(Destagionalizzazione$alimentare,frequency = 12)
+
+TS_Alimentare_dec<-decompose(TS_Alimentare,type="additive")
+TS_Alimentare_dec$random[1:60]=0
+
+TS_Alimentare_dec$trend=TS_Alimentare_dec$x-TS_Alimentare_dec$random-TS_Alimentare_dec$seasonal
+
+
+
+autoplot(TS_Alimentare_dec)+labs(colour = NULL)
+
+
+TS_Abbigliamento = ts(Destagionalizzazione$Abbigliamento,frequency = 12)
+
+TS_Abbigliamento_dec<-decompose(TS_Abbigliamento,type="additive")
+
+#TS_Abbigliamento_dec$trend[30:48]=TS_Abbigliamento_dec$trend[30:48]+TS_Abbigliamento_dec$random[30:48]
+
+TS_Abbigliamento_dec$random[42:60]=0
+
+TS_Abbigliamento_dec$trend=TS_Abbigliamento_dec$x-TS_Abbigliamento_dec$random-TS_Abbigliamento_dec$seasonal
+
+autoplot(TS_Abbigliamento_dec)
+
+
+autoplot(log10(TS_Abbigliamento_dec$trend))
+
+
+
+TS_Calzature = ts(Destagionalizzazione$Calzature,frequency = 12)
+
[…]

### 2021-03-19 Manuscript/manuscript.tex
PUB

@@
      \centering
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}{0.45\textwidth}
          \centering
@@
      \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}{0.45\textwidth}
          \centering
          \includegraphics[width=\textwidth]{Figures/Calzature.pdf}
-         \caption{\textcolor{OliveGreen}{Footwear} (green)}
+         \caption{\textcolor{OliveGreen}{Footwear} (Green)}
          \label{fig:three sin x}
      \end{subfigure}
-          \begin{subfigure}[b]{0.45\textwidth}
+          \begin{subfigure}{0.45\textwidth}
          \centering
          \includegraphics[width=\textwidth]{Figures/Elettrodomestici.pdf}
-         \caption{ \textcolor{Orange}{Appliances} (orange)}
+         \caption{ \textcolor{Orange}{Appliances} (Orange)}
          \label{fig:y equals x}
@@
      \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}{0.45\textwidth}
          \centering
          \includegraphics[width=\textwidth]{Figures/Fotoottica.pdf}}
-          \caption{\textcolor{Blue}{Photo-optics} (blue)}
+          \caption{\textcolor{Blue}{Photo-optics} (Blue)}
          \label{fig:three sin x}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Casalinghi.pdf}}
+         \caption{\textcolor{Purple}{Homeware} (Purple)}
+         \label{fig:three sin x}
+     \end{subfigure}
+       \hfill
+        \begin{subfigure}{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{Figures/Utilenseria.pdf}
+         \caption{\textcolor{Orange}{Household tools} (L green)}
+         \label{fig:y equals x}
      \end{subfigure}
@@
 \centering
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{Figures/Mobili.pdf}}
-         \caption{\textcolor{OliveGreen}{Homeware} (Orchid)}
-         \label{fig:three sin x}
-     \end{subfigure}
-        \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{Figures/Utilenseria.pdf}
-         \caption{ \textcolor{Orange}{Household tools} (Light green)}
-         \label{fig:y equals x}
-     \end{subfigure}
-             \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{Figures/Giocattoli.pdf}
+\includegraphics[width=0.45\textwidth]{Figures/Giocattoli.pdf}
 \caption{ \textcolor{Thistle}{Games} (Thistle)}
   \label{fig:y equals x}
-     \end{subfigure}
 \caption{Selling data (II), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
@@
                                        & $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{4} $ & $\sigma_{\delta_{4}$ & t      &  $\delta_{5}$ & $\sigma_{\delta_{5}$  & t     \\ \hline
-{\color[HTML]{343434} Total}        & -36   & 144    &  -0.26  & -36   & 144   & -0.25 & -36  & 144    & -0.25 \\ \hline
-{\color[HTML]{343434} Manufacture}  & -26   & 101    &  -0.25  & -26   & 101   & -0.26 & -26  & 101     & -0.25   \\ \hline
-{\color[HTML]{343434} Trade}        & -0.88   & 3.2  & -0.27  & -0.60   & 3.2  & -0.18 & -0.70   & 3.2  & -0.21 \\ \hline
-{\color[HTML]{343434} Construction} & -6.7   & 26  &  -0.25 &  -5.8    & 26  & -0.22 & -6.5    & 26 & -0.25 \\ \hline
+{\color[HTML]{343434} Total}        & -48   & 163    &  -0.30  & -47   & 163   & -0.29 & -47  & 163    & -0.29 \\ \hline
+{\color[HTML]{343434} Manufacture}  & -34   & 114    &  -0.30  & -35   & 114   & -0.30 & -34  & 114     & -0.30   \\ \hline
+{\color[HTML]{343434} Trade}        & -1.2   & 3  & -0.31  & -0.9   & 3.7  & -0.23 & -0.9   & 3.7  & -0.26 \\ \hline
+{\color[HTML]{343434} Construction} & -8.3   & 30  &  -0.27 &  -7.4    & 30  & -2.44 & -8.10    & 30 & -2.67 \\ \hline
 \label{sub_DID_placebo}
@@
 \begin{flushleft}
-$\alpha$ , $\beta_{0}$ and $\beta_{1}$ obtained by the DID regression,  for subsidies  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\alpha$ , $\beta_{0}$ and $\beta_{1}$, expressed in millions, as obtained by the DID regression,  for subsidies  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
@@
                                        & $\alpha$ &   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
-{\color[HTML]{343434} Total}        & 4.75 *** &  0.47   & 10.04  & 3.90 ***  &  0.66    & 5.84  & -2.46   &  2.50    & -0.98  \\ \hline
-{\color[HTML]{343434} Manufacture}  & 3.72  ***  &  0.41  & 8.95 & 2.59 ***   &  0.59    & 4.40 & -2.00   & 2.20     & -0.91   \\ \hline
-{\color[HTML]{343434} Trade}        & 0.23 ***  & 0.03  & 7.13  & -0.16 **  & 0.05  & -3.36  & -0.15  & 0.17  & -0.83 \\ \hline
-{\color[HTML]{343434} Construction} & 0.06  & 0.11  & 0.53 & 1.97  ***   & 0.16  & 11.91 &  -0.06    & 0.62  &  -0.095  \\ \hline
+{\color[HTML]{343434} Total}        & 4.43 *** &  0.58   & 7.56  & 4.03 ***  &  0.83 & 4.87  & -2.14   &  2.74    & -0.78  \\ \hline
+{\color[HTML]{343434} Manufacture}  & 3.47  ***  &  0.52  & 6.67 & 3.02 ***   &  0.73    & 4.10 & -1.75   & 2.44     & -0.72   \\ \hline
+{\color[HTML]{343434} Trade}        & 0.19 ***  & 0.03  & 5.73  & -0.11 **  & 0.05  & -2.48  & -0.09  & 0.15  & -0.63 \\ \hline
+{\color[HTML]{343434} Construction} & 0.06  & 0.08  & 0.77 & 1.62  ***   & 0.11  & 14.15 &  -0.06    & 0.38  &  -0.16  \\ \hline
 \label{CIG_DID_coef_I}
@@
 & $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
-{\color[HTML]{343434} Total}        & -2.39   &  2.50   & -0.95  & -3.17    &  2.50    & -1.26  \\ \hline
-{\color[HTML]{343434} Manufacture}  & -2.72   &  2.20    & -1.23  & -3.33    &  2.20    & -1.50   \\ \hline
-{\color[HTML]{343434} Trade}        & -0.12   & 0.17  & -0.68  & -0.07  & 0.17  & -0.39   \\ \hline
-{\color[HTML]{343434} Construction} & -0.06    & 0.62 & -0.096  & 0.06     & 0.62  & 0.10  
+{\color[HTML]{343434} Total}        & -2.06   &  2.74   & -0.75  & -2.85    &  2.74    & -1.04  \\ \hline
+{\color[HTML]{343434} Manufacture}  & -2.46   &  2.44    & -0.72  & -3.05    &  2.44    & -1.25   \\ \hline
+{\color[HTML]{343434} Trade}        & -0.07   & 0.15   & -0.46  & 0.02  & -0.15 & -0.13  \\ \hline
+{\color[HTML]{343434} Construction} & -0.06    & 0.38 & -0.16 & 0.06     & 0.38  & -0.16  
 \label{CIG_DID_coef_II}

### 2021-03-19 Analisi_vendite/Test vari/Plotter_destag.R

@@ -43,7 +43,7 @@ ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+theme_bw()+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
 
-ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Casalinghi),color = "cyan")+ 
+ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Casalinghi),color = "purple")+ 
   geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 

### 2021-03-19 Manuscript/manuscript.tex
PUB
PUb

@@
 The recent pandemic due to the spread of the SARS-CoV-2 virus opened a highly debated issue about the best approach for the policy-maker to face the epidemic.
-Unlike the past pandemics and the XX century (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
+Unlike the past pandemics of XX century (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
 Consequently, the modeling of the virus diffusion and the effect on socio-economic texture for different countries can be investigated with a more satisfactory resolution.
@@
 In particular, for the model in Ref.
-\cite{kabir2020evolutionary} it is assumed that the policy-maker knows the consequences of his/her choices ideally and that he/she can act without delay to impose the optimal choice; finally, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range).
+\cite{kabir2020evolutionary} it is assumed that the policy-maker perfectly knows the consequences of his/her choices and that he/she can act without delay to impose the optimal choice; finally, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range).
 In contrast, for different countries, such a factor seems to be much more discrete (e.g., the PM can reduce the daily contacts only by choosing definite values).
@@
 Furthermore,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
-Thus, the final output of the model will be the cumulative deaths and the economic damage for each selling sector.
+Thus, the final output of the model will be the cumulative deaths, the economic damage for each selling sector and the the increase of subsidies paid.
 Moreover, here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them may be recovered or even should take the intensive therapy.
 As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the SIRD model and the lock-down days was obtained.
-Such behavior belongs to a class of phenomena that, in physical sciences, is called a phase transition.
+Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.
 For each phase, we will discuss the result of the simulation, and then we will compare them to get a general insight.
@@
 For further details see \cite{vynnycky2010introduction}}.
-On the other side, $\beta$,$\gamma$, and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular, $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality defined as the probability to die conditionally to be ill).
+On the other side, $\beta$,$\gamma$, and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular, $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality defined as the probability to die given to be ill).
 Usually, epidemiologist is interested in the ratio:
@@
 This spillover translates into more death and more ill people for the baseline situation where there is not a pandemic: however,  by now,  this effect is difficult to quantify, and so we did not include it in the present model}.
-Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the selling for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper, these categories will be referred to as the part of the name labeled in blue.
+Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the sales for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper, these categories will be referred to as the part of the name labeled in blue.
 }: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, Household \textcolor{blue}{Appliances}/radios/televisions and
@@
 The monthly sales data were retrieved from the National Institute of Statistics website \cite{istat}.
-In particular, we considered the period starting from June 2018 up to June 2020 for the eight categories described in the previous section .
+In particular, we considered the period starting from June 2018 up to June 2020 for the eight sales categories described in the previous section .
 The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not to national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
@@
 Here the period considered also starts from June 2018 up to June 2020 for the four categories described in the previous section.
-It is worth noting that we considered only the authorized subsidies and not the asked ones.
+It is worth noting that we considered only the authorized (paid) subsidies and not the asked ones.
 Furthermore,  differently for the sales, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
@@
 \ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the losses for selling and the use of subsidies are widely large concerning the one-wave scenario.
-In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  selling, and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option: although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante.
+In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  selling, and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option (e.g.
+art.
+452 Codice Penale): although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante.
 For this reason, here, we considered the epidemiological consequences separated from the economic ones.
@@
 \caption{Comparison between the ordinary subsidies (blue)   vs.
-the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total.
+the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total (including other sectors that were not analysed here).
 The dashed lines represent the different timing and intensity for the lock-down:  red for high, orange medium, and green for low.

### 2021-03-20 Manuscript/manuscript.tex
PUb

@@
 very strict).
-In order to simulate not only an epidemiological scenario but also an economic one, we estimated, via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales and on subsidies (\textit{Cassa Integrazione}).
+In order to simulate not only an epidemiological scenario but also an economic one, we estimated, via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales value and redundancy funds (\textit{Cassa Integrazione}).
 We found that by modifying with continuity, the PM attitude to impose the lock-down a phase transition (as defined for a physical system) is obtained.
@@
 On this basis, we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.
-Furthermore,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on subsidies (\textit{Cassa Integrazione Ordinaria}) in Italy.
-Thus, the final output of the model will be the cumulative deaths, the economic damage for each selling sector and the the increase of subsidies paid.
+Furthermore,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.
+Thus, the final output of the model will be the cumulative deaths, the economic damage for each sales sector and the the increase of redundancy funds paid.
 Moreover, here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them may be recovered or even should take the intensive therapy.
@@
 
-The economic impact for each epidemiological scenario is shaped as follow: the first set of parameters,  as the economic value of death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on selling for different areas and on unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
+The economic impact for each epidemiological scenario is shaped as follow: the first set of parameters,  as the economic value of death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on sales for different areas and on unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
 Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
@@
 Besides this impact,  there is also the cost associated with the medical care of each ill people.
-For this, we considered the average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another import health-care impact because the ill people for COVID-19 saturate the health system thus making it unreachable for other diseases.
+For this, we considered the national average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another import health-care impact because the ill people for COVID-19 saturate the health system thus making it unreachable for other diseases.
 This spillover translates into more death and more ill people for the baseline situation where there is not a pandemic: however,  by now,  this effect is difficult to quantify, and so we did not include it in the present model}.
-Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the sales for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper, these categories will be referred to as the part of the name labeled in blue.
+Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the sales value for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper, these categories will be referred to as the part of the name labeled in blue.
 }: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, Household \textcolor{blue}{Appliances}/radios/televisions and
-tape recorders, \textcolor{blue}{Furniture}/textile articles/furnishings for the home, 
-\textcolor{blue}{Photo-optics}/films/compact discs/ audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Homeware}, \textcolor{blue}{Household tools} and hardware tools, \textcolor{blue}{Games}/toys/sports and camping articles.
-The choice to use sales as a parameter for the evaluation of the lock-down lies in the fact that with them is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can also be considered is the contraction of fuel selling, due to the reduced mobility, where in addition to the VAT there is also fixed taxation (accisa).
+tape recorders, 
+\textcolor{blue}{Photo-optics}/films/compact discs/audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Homeware}, \textcolor{blue}{Household tools} and hardware tools, \textcolor{blue}{Games}/toys/sports and camping articles.
+The choice to use sales value as a parameter for the evaluation of the lock-down lies in the fact that with them is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can also be considered is the contraction of fuel sales value, due to the reduced mobility, where in addition to the VAT there is also fixed taxation (accisa).
 Such calculation may be considered as a future outlook of this work}.
-Beside the selling we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
+Beside the sales value we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
 Furthermore also the total value (considering also other sectors that were not analysed here).
 In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the Government for the firms that were damaged by the lock-down restrictions.
-For the empirical evaluation of the impact on selling and unemployment benefit, we performed a multiple time Difference in Difference as presented in Refs.
+For the empirical evaluation of the impact on sales value and unemployment benefit, we performed a multiple time Difference in Difference as presented in Refs.
 \cite{draca2011panic},  \cite{imbens2009recent} and \cite{wooldridge2012introductory}.
@@
 \end{equation}
-where $Y$ is the selected outcome (sales or subsidies), $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group, and $\epsilon$ an error term.
-As a control group for the sales,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless for the lock-down\footnote{Although it is true that a slight increase of food sales during the lock-down is present in the plots in Fig.
+where $Y$ is the selected outcome (sales value or redundancy funds), $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group, and $\epsilon$ an error term.
+As a control group for the sales value,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless for the lock-down\footnote{Although it is true that a slight increase of food sales value during the lock-down is present in the plots in Fig.
 \ref{Selling_plots} \ref{Selling_plots_II},  it must be stressed the fact that, as proven numerically in the Supporting Info A, this change does not significantly affect the DID estimations }.
-On the other side,  for subsidies \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
+On the other side,  for redundancy funds \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
 This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labor cost but at the same time guaranteeing to the workers part of their original salary \footnote{It is worth noting that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact, there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
@@
 Thus the Cassa Integrazione Straordinaria-Solidarietà can be considered as not treated by the first wave of the lock-down, while the ordinary one treated.
-The DID consider here has three different times for the national lock-down:  for the sales, we considered,  as done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
-On the other side concerning the subsidies,  we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the subsidies for workers was slightly delayed because firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as a consequence,  because of this buffer effect,  in March there is no significant effect of this subsidies although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
-Performing the DID, we estimated the coefficients for each intensity of lock-down on sales and subsidies.
+The DID consider here has three different times for the national lock-down:  for the sales value, we considered,  as done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
+On the other side concerning the redundancy funds,  we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the redundancy funds for workers was slightly delayed because firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as a consequence,  because of this buffer effect,  in March there is no significant effect of this redundancy funds although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
+Performing the DID, we estimated the coefficients for each intensity of lock-down on sales value and redundancy funds.
 Then these were rescaled in order to obtain a weekly value.
-Finally, we multiplied the number obtained from the previous calculation by the number of lock-down weeks,  with the respective intensity,  in each scenario simulated via the epidemiological model described before.
+Finally, we multiplied the coefficients obtained from the DID (scaled from months to weeks) by the number of lock-down weeks,  with the respective intensity,  in each scenario simulated via the epidemiological model described before.
 As a consequence, we obtained,  for each scenario,  an economics simulation based on parameters obtained from an empirical evaluation.
@@
 
-The monthly sales data were retrieved from the National Institute of Statistics website \cite{istat}.
-In particular, we considered the period starting from June 2018 up to June 2020 for the eight sales categories described in the previous section .
+The monthly sales value data (with the baseline $100=2015$) were retrieved from the National Institute of Statistics website \cite{istat}.
+In particular, we considered the period starting from June 2018 up to June 2020 for the eight sales value categories described in the previous section .
 The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not to national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
@@
 The decomposition results are reported in the Supporting Info E.
-Concerning monthly subsidies paid we retrieved the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+Concerning monthly redundancy funds paid we retrieved the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
 Here the period considered also starts from June 2018 up to June 2020 for the four categories described in the previous section.
-It is worth noting that we considered only the authorized (paid) subsidies and not the asked ones.
-Furthermore,  differently for the sales, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
+It is worth noting that we considered only the authorized (paid) redundancy funds and not the asked ones.
+Furthermore,  differently for the sales value, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
 
@@
 
-For each sales category we run the regression reported in the Eq.
+For each sales value category we run the regression reported in the Eq.
 \ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots} and \ref{Selling_plots_II}.
@@
 On the other side, the Household kids and the Household tools seem lesser affected by the lock-down.
-The same DID regression was used for the subsidies,  using as the control group the extraordinary solidarity subsidies (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
+The same DID regression was used for the redundancy funds,  using as the control group the extraordinary solidarity redundancy funds (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
 \ref{CIG_sector_plots} and Tab \ref{CIG_DID}.
 Also in this case the placebo tests were successfully performed.
-An interesting insight is also provided by the inspection of the extraordinary subsidies for renovation ( \textit{cassa integrazione ristrutturazione}): these subsidies, compared to the solidarity ones, seem much more sensitive for an external shock in particular for the trade sector.
+An interesting insight is also provided by the inspection of the extraordinary redundancy funds for renovation ( \textit{cassa integrazione ristrutturazione}): these redundancy funds, compared to the solidarity ones, seem much more sensitive for an external shock in particular for the trade sector.
 
@@
 \ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost}  the outcomes of the epidemiological model are given,  while the SIRD curves for the scenarios are provided in Fig.
-\ref{SIRD_scenario}; on the other side the effect on selling and subsidies for both scenarios are given in Fig.
+\ref{SIRD_scenario}; on the other side the effect on sales value and redundancy funds for both scenarios are given in Fig.
 \ref{Selling_sector_effects} and \ref{CIG_sector_effects}.
@@
 This has an immediate drawback on the economic data: as shown in Fig.
-\ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the losses for selling and the use of subsidies are widely large concerning the one-wave scenario.
-In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  selling, and subsidies): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option (e.g.
+\ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the losses for sales value and the use of redundancy funds are widely large concerning the one-wave scenario.
+In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  sales value, and redundancy funds): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option (e.g.
 art.
@@
 We have obtained a model that combines the epidemiological aspects and the economic ones within a stochastic approach.
-This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales sectors and the subsidies dedicated to firms that would reduce the labor cost.
+This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales value sectors and the redundancy funds dedicated to firms that would reduce the labor cost.
 Furthermore, we show numerically that,  within a stochastic approach,  the PM attitude to impose the lock-downs is critical.
@@
      \end{subfigure}
-\caption{Sales data (I), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+\caption{Sales value data (I), with the baseline $100=2015$,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
 The timing for each lock-down is marked with a dashed line: red for high, orange medium, and green for low.
@@
   \label{fig:y equals x}
-\caption{Selling data (II), with baseline of 2015,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+\caption{Sales value data (II), with the baseline $100=2015$,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
 Each lock-down timing is marked with a dashed line: red for high, orange medium, and green for low.
@@
 \begin{flushleft}
-$\delta$ coefficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
+$\delta$ coefficients as obtained by the DID  regression, for sales value data (with the baseline $100=2015$) de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
 The values of the intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Info.
@@
          \includegraphics[width=\textwidth]{Figures/CIG_Manifattura.pdf}
-         \caption{Subsidies paid for manufacture} 
+         \caption{Redundancy funds paid for manufacture} 
      \end{subfigure}
@@
          \includegraphics[width=\textwidth]{Figures/CIG_Commercio.pdf}}
-         \caption{Subsidies paid for trade}
+         \caption{Redundancy funds paid for trade}
      \end{subfigure}
@@
      \end{subfigure}
-\caption{Comparison between the ordinary subsidies (blue)   vs.
+\caption{Comparison between the ordinary redundancy funds (blue)   vs.
 the extraordinary ones (renovation red and purple solidarity) for a selected set of sectors and the overall total (including other sectors that were not analysed here).
@@
 \begin{flushleft}
-$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for the different lock-down timings.
+$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for redundancy funds (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for the different lock-down timings.
 The values of the  intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Information D.
@@
      \end{subfigure}
-\caption{Comparison between the sales effects for the scenarios where an active vs lazy PM is considered.
+\caption{Comparison between the sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
@@
      \end{subfigure}
-\caption{Comparison between the subsides effects for the scenarios where an active vs.
+\caption{Comparison between the subsides effects (in terms of hours paid) for the scenarios where an active vs.
 lazy PM is considered.
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
-The error bars, although they are visible because they are too reduced,  were calculated by considering the error propagation}
+The error bars, although they are not clearly visible because they are too reduced,  were calculated by considering the error propagation}
 \label{CIG_sector_effects}
@@
 In order to check if any significant effect is obtained on the coefficients of Tab.
-\ref{selling_DID_table_delta_phantom} by the slight increase of food consumption during the lockdown,  we considered a hypothetical scenario where this increase did not happen (e.g.
-the selling for March to June were identical to February): as one can point out by comparing the Tab.
+\ref{selling_DID_table_delta_phantom} by the slight increase of food consumption during the lockdown,  we considered a hypothetical scenario where this increase did not happen (e.g sales value for March to June were identical to February): as one can point out by comparing the Tab.
 \ref{selling_DID_table_delta_phantom} with Tab, \ref{selling_DID_table_delta} no significant difference can be found.
@@
 In order to perform a further assessment on the credibility of the DID coefficients obtained in Tab.
-\ref{selling_DID_table_delta} we make a comparison between the trends of the difference of food sales and the other sectors, before ($\Delta$ Slope before $T_{T1}$) and after the three lock-down at $T_{T1}$,$T_{T2}$ and $T_{T3}$.
+\ref{selling_DID_table_delta} we make a comparison between the trends of the difference of food sales value and the other sectors, before ($\Delta$ Slope before $T_{T1}$) and after the three lock-down at $T_{T1}$,$T_{T2}$ and $T_{T3}$.
 As can be seen from the following tables (Tab.
@@
 \includegraphics[width=0.5\textwidth]{Figures/DID_selling_placebo.pdf}
-\caption{Timing for placebo test for food vs clothing sales: $T_{4}$ is placed at $T=-4$ and $T=-2$,  $T_{5}$ at $T=-3$ and  $T_{6}$ at $T=-1$).
-For the other sales sector the placebo timing is identical}
+\caption{Timing for placebo test for food vs clothing sales value: $T_{4}$ is placed at $T=-4$ and $T=-2$,  $T_{5}$ at $T=-3$ and  $T_{6}$ at $T=-1$).
+For the other sales value sector the placebo timing is identical}
 \label{DID_selling_placebo}
@@
 \begin{flushleft}
-$\delta$ cofficients as obtained by the DID  regression, for the selling data de-seasoned,  according to equation \ref{DID-eq} \\ for a placebo timings as showed in Fig.  \ref{DID_selling_placebo}
+$\delta$ cofficients as obtained by the DID  regression, for sales value data de-seasoned,  according to equation \ref{DID-eq} \\ for a placebo timings as showed in Fig.  \ref{DID_selling_placebo}
 \end{flushleft}
@@
 \includegraphics[width=0.5\textwidth]{Figures/DID_subsidies_placebo.pdf}
-\caption{Timing for placebo test for the total subsidies paid (in hour) \textit{Cassa integrazione Ordinaria} (blue) vs  \textit{Cassa integrazione Straordinaria Solidarietà} (purple)  sales: $T_{4}$ is placed at $T=-2$,  $T_{5}$ at $T=-1$ and  $T_{6}$ at $T=0$).
+\caption{Timing for placebo test for the total redundancy funds paid (in hour) \textit{Cassa integrazione Ordinaria} (blue) vs  \textit{Cassa integrazione Straordinaria Solidarietà} (purple)  sales value: $T_{4}$ is placed at $T=-2$,  $T_{5}$ at $T=-1$ and  $T_{6}$ at $T=0$).
 For the other categories the placebo timing is identical}
@@
 \begin{flushleft}
-$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for subsidies (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for a placebo timings as showed in Fig.
+$\delta$ cofficients, expressed in millions as obtained by the DID  regression, for redundancy funds (controlling the extraordinary solidarity) \\ according to equation \ref{DID-eq} for a placebo timings as showed in Fig.
 \ref{DID_subsidies_placebo}
@@
 
-Here we report the estimation of the other parameters,  obtained in the DID regression for sales and subsidies,  that were not put in to the main text
+Here we report the estimation of the other parameters,  obtained in the DID regression for sales value and redundancy funds,  that were not put in to the main text
 
@@
 \begin{flushleft}
-$\alpha$ , $\beta_{0}$ and $\beta_{1}$  obtained by the DID regression,  for sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\alpha$ , $\beta_{0}$ and $\beta_{1}$  obtained by the DID regression,  for sales value data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
@@
 \begin{flushleft}
-$\beta_{2}$ and $\beta_{3}$ obtained by the DID regression,  for  sales data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\beta_{2}$ and $\beta_{3}$ obtained by the DID regression,  for  sales value data de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
@@
 \begin{flushleft}
-$\alpha$ , $\beta_{0}$ and $\beta_{1}$, expressed in millions, as obtained by the DID regression,  for subsidies  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\alpha$ , $\beta_{0}$ and $\beta_{1}$, expressed in millions, as obtained by the DID regression,  for redundancy funds  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
@@
 \begin{flushleft}
-$\beta_{2}$ and $\beta_{3}$ obtained by the DID regression,  for subsidies  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
+$\beta_{2}$ and $\beta_{3}$ obtained by the DID regression,  for redundancy funds  according to equation \ref{DID-eq} \\ for the different lock-down timings. 
 \end{flushleft}
@@
 
-In this section of we report the results of the de-seasoning for raw sales data taken from ISTAT \cite{istat}.
+In this section of we report the results of the de-seasoning for raw sales value data taken from ISTAT \cite{istat}.
 The first panel refer to the raw data (data)  the third to the seasonal component that is perfectly periodical (seasonal),  the forth one to the seasonal component that is not perfectly periodical (remainder) and the second one the trend extracted (trend).
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Alimentare.pdf}
-\caption{De-seasoning components for food sales} 
+\caption{De-seasoning components for food sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Abbigliamento.pdf}
-\caption{De-seasoning component for clothing sales} 
+\caption{De-seasoning component for clothing sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Calzature.pdf}
-\caption{De-seasoning components for footwear sales} 
+\caption{De-seasoning components for footwear sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Elettrodomestici.pdf}
-\caption{De-seasoning components for appliances sales} 
+\caption{De-seasoning components for appliances sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Fotoottica.pdf}
-\caption{De-seasoning components for photo-optics sales} 
+\caption{De-seasoning components for photo-optics sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Casalinghi.pdf}
-\caption{de-seasoning components  for Homeware sales } 
+\caption{de-seasoning components  for Homeware sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Utilenseria.pdf}
-\caption{De-seasoning components for household tools sales} 
+\caption{De-seasoning components for household tools sales value} 
 \label{Phase_transition}
@@
  \includegraphics[width=\textwidth]{Figures/Deseasoning/Giocattoli.pdf}
-\caption{De-seasoning components for games sales } 
+\caption{De-seasoning components for games sales value } 
 \label{Phase_transition}

### 2021-03-21 Manuscript/manuscript.tex
PUb

@@
 In order to simulate not only an epidemiological scenario but also an economic one, we estimated, via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales value and redundancy funds (\textit{Cassa Integrazione}).
-We found that by modifying with continuity, the PM attitude to impose the lock-down a phase transition (as defined for a physical system) is obtained.
+We found that by modifying with continuity the PM attitude to impose the lock-down, a phase transition (as defined for a physical system) is obtained.
 The comparison of these two scenarios and their impact provides a bird's-eye view of the socio-economic consequences of the PM attitude
@@
 This choice is based on the idea that,  if the PM misbehaves,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and then,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is taken into account.
-However, a partial differential equations system should be solved, making the calculation and the computational cost incredibly high.}.
+However, as said before, a partial differential equations system should be solved, making the calculation and the computational cost incredibly high.}.
 Besides this impact,  there is also the cost associated with the medical care of each ill people.
@@
 \ref{selling_DID_table_delta} we see that the most severe lock-down damage hit the clothing and the footwear.
-On the other side, the Household kids and the Household tools seem lesser affected by the lock-down.
 The same DID regression was used for the redundancy funds,  using as the control group the extraordinary solidarity redundancy funds (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
@@
 art.
-452 Codice Penale): although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante.
-For this reason, here, we considered the epidemiological consequences separated from the economic ones.
-A more intriguing issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle,  summed.
+452 Codice Penale) although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante.
+This point is also based on the different rulings of the Italian Constitutional Court that declared the right of life as "the essence of the supreme values ​​on which the Italian Constitution is based" \cite{cort_cost}.
+Note that this interpretation is the legal basis for which the lock-down can be adopted since it limits the constitutional rights contained in the Art.
+13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.)\footnote{An interesting analysis about this point is provided here \cite{cost_discussion}}
+For this reasons, here, we considered the epidemiological consequences separated from the economic ones.
+A more complex issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle,  summed.
 We say in principle because the jurisprudence is significantly reduced or missing since the pandemics are rare.

### 2021-03-21 Manuscript/manuscript.tex
PUb

@@
 Note that this interpretation is the legal basis for which the lock-down can be adopted since it limits the constitutional rights contained in the Art.
-13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.)\footnote{An interesting analysis about this point is provided here \cite{cost_discussion}}
-For this reasons, here, we considered the epidemiological consequences separated from the economic ones.
+13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.)\footnote{An interesting analysis about this point is provided here \cite{cost_discussion}}.
 A more complex issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle,  summed.
@@
 {\color[HTML]{009901} Footwear}        & -38.70 *** & 1.73  & -22.35 & -65.78 *** & 2.39  & -27.49 & -20.62 *** & 2.39  & -8.62 \\ \hline
-{\color[HTML]{F56B00} Appliances}      & -20.32 *** & 2.50  & -8.11  & -27.34 *** & 3.45  & -7.90  & -3.68  & 3.45  & 1.06  \\ \hline
+{\color[HTML]{F56B00} Appliances}      & -20.32 *** & 2.50  & -8.11  & -27.34 *** & 3.45  & -7.90  & -3.68  & 3.45  & -1.06  \\ \hline
 {\color[HTML]{00009B} Photo-optics}    & -34.14 *** & 2.55  & -13.38 & -52.32 ***  & 3.52  & -14.84 & -7.86 *  & 3.52  & -2.23 \\ \hline

### 2021-03-22 Manuscript/manuscript.tex
PUB

@@
 In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the Government for the firms that were damaged by the lock-down restrictions.
-For the empirical evaluation of the impact on sales value and unemployment benefit, we performed a multiple time Difference in Difference as presented in Refs.
+For the empirical evaluation of the impact on sales value and redundancy funds, we performed a multiple time Difference in Difference as presented in Refs.
 \cite{draca2011panic},  \cite{imbens2009recent} and \cite{wooldridge2012introductory}.
@@
 Thus the Cassa Integrazione Straordinaria-Solidarietà can be considered as not treated by the first wave of the lock-down, while the ordinary one treated.
-The DID consider here has three different times for the national lock-down:  for the sales value, we considered,  as done for the epidemiological model,  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
-On the other side concerning the redundancy funds,  we considered as medium lock-down only May 2020: such choice was motivated by the fact that the effect of firms to use the redundancy funds for workers was slightly delayed because firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as a consequence,  because of this buffer effect,  in March there is no significant effect of this redundancy funds although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
+The DID consider here has three different times for the national lock-down:  for the sales value, we considered  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
+On the other side concerning the redundancy funds,  we considered as medium lock-down only May 2020 while for the high and low lock-down the timing were identical to the sales value.
+Such choice was motivated by the fact that the effect of firms to use the redundancy funds for workers was slightly delayed because in March 2020 firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as a consequence,  because of this buffer effect,  in March there is no significant effect of this redundancy funds although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
 Performing the DID, we estimated the coefficients for each intensity of lock-down on sales value and redundancy funds.
@@
 Moreover, if regional clusters were considered, it was necessary to model an ensemble of SIRD models that communicate with a defined rate (that change also with respect to the lock-down restriction).
-This makes the model much more complicated.
-However, if all the necessary data for performing the analysis will become available, the author may consider, as an outlook, extending the present analysis to regional clusters}.
+This makes the model much more complicated}.
 As discussed in Supporting Information,  these data were not de-seasoned.
@@
 As shown in Fig.
-\ref{R_t_scenarios} this result is basically obtained by keeping the reproduction factor in the value of medium lock-down value.
-These two theoretical models correspond,  in practice,  for the lazy PM to the one considered by the PMs that aimed to herd immunity.
-At the same time,  concerning the active-PM,  to the PMs that would not saturate the health system and aimed to reduce the death at the minimum.
-It is interesting to point out that the change between the scenarios develops in a discontinuous way as shown in Fig.
+\ref{R_t_scenarios} this result is basically obtained by keeping the reproduction factor in the value of medium lock-down value \footnote{These two theoretical models correspond,  in practice,  for the lazy PM to the one considered by the PMs that aimed to herd immunity.
+At the same time,  concerning the active-PM,  to the PMs that would not saturate the health system and aimed to reduce the death at the minimum.} It is interesting to point out that the change between the scenarios develops in a discontinuous way as shown in Fig.
 \ref{Phase_transition}, as the reactivity of the PM is changed, we can consider this as a phase transition of a physical system (e.g., consider the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
@@
 While in their model, this was directly related to the contagion probability, this is indirectly made stochastically by PM's decision that modifies the $\beta$ parameter and so the transmission rate.
+The phase transition discussed here shows that even though the PM can tune within a specific limit the contagion ratio, as said in the introduction, the outcomes due to his/her reactivity are binary due to the collective behavior of individuals in the SIRD model with the stochastic lockdown.
+It is worth mentioning that this does not mean that only two outcomes are available in the present model.
+For instance, within the same reactivity of a PM, one can tune the infected threshold or the reduction factor of beta coefficients obtaining different scenarios within the same phase.
 Moving to the socio-economic outcome of the model used, we see, from Tab.
@@
 art.
-452 Codice Penale) although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante.
-This point is also based on the different rulings of the Italian Constitutional Court that declared the right of life as "the essence of the supreme values ​​on which the Italian Constitution is based" \cite{cort_cost}.
+452 Codice Penale) although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante \footnote{This point is also based on the different rulings of the Italian Constitutional Court that declared the right of life as "the essence of the supreme values ​​on which the Italian Constitution is based" \cite{cort_cost}.
 Note that this interpretation is the legal basis for which the lock-down can be adopted since it limits the constitutional rights contained in the Art.
-13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.)\footnote{An interesting analysis about this point is provided here \cite{cost_discussion}}.
-A more complex issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle,  summed.
-We say in principle because the jurisprudence is significantly reduced or missing since the pandemics are rare.
+13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.) (see also \cite{cost_discussion}}).
+A more complex issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle, summed \footnote{We say in principle because the jurisprudence is significantly reduced or missing since the pandemics are rare}.
 For the present study, these indirect deaths are,  by now,  not easy to quantify, and thus, we did not consider this option.

### 2021-03-22 Analisi_cassa_integrazione/Cassa_integrazione.R
PUb

@@ -106,6 +106,17 @@ summary(did_Full_placebo)
 ggplot(data=Dati_cassa_integrazione_Full  ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
   geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
   geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
+  geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
+  geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+
+  labs(y = "Hours Paid ")+ labs(x = "Time (months)")+
+  theme_bw(base_size = 18) 
+
+
+
+ggplot(data=Dati_cassa_integrazione_Full  ,aes(x=Time,y=CIG_S))+geom_line(size=2,color = "red")+
+  geom_line(size=2,color = "blue",aes(x=Time,y=CIG_O))+
+  geom_line(size=2,color = "purple",aes(x=Time,y=CIG_SL))+
   geom_vline(xintercept = -2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = -1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 0, linetype="dashed", color = "darkgreen", size=1)+

### 2021-03-22 Manuscript/manuscript.tex
PUb
PUB

@@
 Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations,  only the clothing, and footwear sectors.
-By inspecting the Tab.
-\ref{selling_DID_table_delta} we see that the most severe lock-down damage hit the clothing and the footwear.
 The same DID regression was used for the redundancy funds,  using as the control group the extraordinary solidarity redundancy funds (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
@@
 This has an immediate drawback on the economic data: as shown in Fig.
-\ref{Selling_sector_effects} and \ref{CIG_sector_effects}, the losses for sales value and the use of redundancy funds are widely large concerning the one-wave scenario.
+\ref{Selling_sector_effects} and \ref{CIG_sector_effects} (and in Tab.
+\ref{Selling_sector_effects_TAB} and \ref{CIG_sector_effects_TAB}) the losses for sales value and the use of redundancy funds are widely large concerning the one-wave scenario.
 In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  sales value, and redundancy funds): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option (e.g.
@@
 The timing for each lock-down is marked with a dashed line: red for high, orange medium, and green for low.
-Note that despite there is a pre-trend, this is negligible for the slope of medium and high lock-down slopes}
+Note that despite there is a pre-trend, this is negligible for the slope of medium and high lock-down slopes (and also for low lock-down concerning clothing and footwear)}
 \label{Selling_plots}
@@
          \includegraphics[width=\textwidth]{Figures/CIG_Manifattura.pdf}
-         \caption{Redundancy funds paid for manufacture} 
+         \caption{Manufacture} 
      \end{subfigure}
@@
          \includegraphics[width=\textwidth]{Figures/CIG_Commercio.pdf}}
-         \caption{Redundancy funds paid for trade}
+         \caption{Trade}
      \end{subfigure}
@@
      \end{subfigure}
-\caption{Comparison between the sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
+\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
@@
      \end{subfigure}
-\caption{Comparison between the subsides effects (in terms of hours paid) for the scenarios where an active vs.
+\caption{Redundancy funds variation(in terms of hours paid) for the scenarios where an active vs.
 lazy PM is considered.
@@
 \label{Table_Epidemiological_cost}
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[]
+\begin{center}
+\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
+The errors were calculated by considering the error propagation}
+\begin{tabular}{l|l|l|l|l}
+                & Active & \sigma   & Lazy &  \sigma \\ \hline
+Clothing        & -481   & 26 & -45  & 9 \\ \hline
+Footwear        & -264   & 23 & -49  & 8 \\ \hline
+Appliances      & -242   & 29 & -20  & 2 \\ \hline
+Photo-optics    & -410   & 30 & -39  & 3 \\ \hline
+Homeware        & -127   & 18 & -14  & 1 \\ \hline
+Household tools & -161   & 42 & -22  & 4 \\ \hline
+Games           & -342   & 41 & -48  & 3
+\label{Selling_sector_effects_TAB}
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[]
+\begin{center}
+\caption{Redundancy funds variation(in terms of hours paid) for the scenarios where an active vs.
+lazy PM is considered.
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
+The errors  were calculated by considering the error propagation.}
+\begin{tabular}{l|l|l|l|l}
+             & Active &  \sigma  & Lazy &   \sigma  \\ \hline
+Total        & 2938   & 38 & 889  & 9.7 \\ \hline
+Manufacture  & 2180   & 38 & 648  & 9.7 \\ \hline
+Trade        & 52     & 3  & 19   & 0.8 \\ \hline
+Construction & 407    & 11 & 135  & 2.8
+\label{CIG_sector_effects_TAB}
 \end{tabular}

### 2021-03-22 Manuscript/manuscript.tex
PUB

@@
 
-In all tables the following significance code will be used:  *** for 0.001,  ** for 0.01 and * for 0.05
+In all tables the following significance code will be used:  *** for 0.001,  ** for 0.01 and * for 0.05. SE stands for Standard Error
 
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
+                                       & $\delta_{1} $&   $ SE_{\delta_{1}}$   & t      & $\delta_{2} $ & $SE_{\delta_{2}$ & t      &  $\delta_{3}$ & $ SE_{\delta_{3}$  & t     \\ \hline
 {\color[HTML]{3531FF} Clothing}        & -40.16 *** & 2.01  & -19.99 & -60.07 *** & 2.77  & -21.64 & -16.45 *** & 2.77  & -5.92 \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
+                                       & $\delta_{1} $&   $ SE_{\delta_{1}}$   & t      & $\delta_{2} $ & $SE_{\delta_{2}$ & t      &  $\delta_{3}$ & $SE_{\delta_{3}$  & t     \\ \hline
 {\color[HTML]{343434} Total}        & 706 ***   & 3.8     & 181  & 217  ***  & 3.8     & 55.98 & 144  ***  & 3.88     & 37.07 \\ \hline
@@
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
-The error bars were calculated by considering the error propagation
+The standard error bars were calculated by considering the error propagation
  }
@@
      \end{subfigure}
-\caption{Redundancy funds variation(in terms of hours paid) for the scenarios where an active vs.
+\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs.
 lazy PM is considered.
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
-The error bars, although they are not clearly visible because they are too reduced,  were calculated by considering the error propagation}
+The standard error bars, although they are not clearly visible because they are too reduced,  were calculated by considering the error propagation}
 \label{CIG_sector_effects}
@@
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
-The errors were calculated by considering the error propagation}
+The standard errors were calculated by considering the error propagation}
 \begin{tabular}{l|l|l|l|l}
-                & Active & \sigma   & Lazy &  \sigma \\ \hline
+                & Active & SE   & Lazy &  SE \\ \hline
 Clothing        & -481   & 26 & -45  & 9 \\ \hline
@@
 \begin{center}
-\caption{Redundancy funds variation(in terms of hours paid) for the scenarios where an active vs.
+\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs.
 lazy PM is considered.
 These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
-The errors  were calculated by considering the error propagation.}
+The standard errors were calculated by considering the error propagation.}
 \begin{tabular}{l|l|l|l|l}
-             & Active &  \sigma  & Lazy &   \sigma  \\ \hline
+             & Active &  SE  & Lazy &   SE  \\ \hline
 Total        & 2938   & 38 & 889  & 9.7 \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-                                       & $\delta_{1} $&   $ \sigma_{\delta_{1}}$   & t      & $\delta_{2} $ & $\sigma_{\delta_{2}$ & t      &  $\delta_{3}$ & $\sigma_{\delta_{3}$  & t     \\ \hline
+                                       & $\delta_{1} $&   $ SE_{\delta_{1}}$   & t      & $\delta_{2} $ & $SE_{\delta_{2}$ & t      &  $\delta_{3}$ & $SE_{\delta_{3}$  & t     \\ \hline
 {\color[HTML]{3531FF} Clothing}        & -39.71 ***  & 2.00  & -19.76 & -59.34 *** & 2.77  & -21.37 & -15.50  *** & 2.77 & -5.58 \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & $\sigma$ \\ \hline
+                & Value  & $SE$ \\ \hline
 $\Delta$ Slope before T1 & -0.33  *** & 0.08  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  &  $\sigma$ \ \\ \hline
+                & Value  &  $SE$ \ \\ \hline
 $\Delta$ Slope before T1 & -0.18 * & 0.08  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & $\sigma$ \\ \hline
+                & Value  & $SE$ \\ \hline
 $\Delta$ Slope before T1 & -0.12  & 0. 07 \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & $\sigma$ \\ \hline
+                & Value  & $SE$ \\ \hline
 $\Delta$ Slope before T1 & -0.40 ***  & 0.07 \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & $\sigma$ \\ \hline
+                & Value  & $SE$ \\ \hline
 $\Delta$ Slope before T1 & -0.16 ** & 0.04  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & $\sigma$ \\ \hline
+                & Value  & $SE$ \\ \hline
 $\Delta$ Slope before T1 & -0.21 *** & 0.05  \\ \hline
@@
 \begin{tabular}{l|l|l}
-                & Value  & $\sigma$ \\ \hline
+                & Value  & $SE$ \\ \hline
 $\Delta$ Slope before T1 & -0.37 ** & 0.10 \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-& $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{5} $ & $\sigma_{\delta_{5}$ & t      &  $\delta_{6}$ & $\sigma_{\delta_{6}$  & t     \\ \hline
+& $\delta_{4} $&   $ SE_{\delta_{4}}$   & t      & $\delta_{5} $ & $SE_{\delta_{5}$ & t      &  $\delta_{6}$ & $SE_{\delta_{6}$  & t     \\ \hline
 {\color[HTML]{3531FF} Clothing}        & 4.87  & 17.47  & 0.28 & 3.94 & 12.65 & 0.31 & 0.70 & 17.48  & 0.04 \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-                                       & $\delta_{4} $&   $ \sigma_{\delta_{4}}$   & t      & $\delta_{4} $ & $\sigma_{\delta_{4}$ & t      &  $\delta_{5}$ & $\sigma_{\delta_{5}$  & t     \\ \hline
+                                       & $\delta_{4} $&   $ SE_{\delta_{4}}$   & t      & $\delta_{4} $ & $SE_{\delta_{4}$ & t      &  $\delta_{5}$ & $SE_{\delta_{5}}$  & t     \\ \hline
 {\color[HTML]{343434} Total}        & -48   & 163    &  -0.30  & -47   & 163   & -0.29 & -47  & 163    & -0.29 \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-& $\alpha $&   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
+& $\alpha $&   $ SE_{\alpha}$   & t      & $\beta_{0}$ & $SE_{\beta_{0}}$ & t      &  $\beta_{1}$ & $SE_{\beta_{1}$  & t     \\ \hline
 {\color[HTML]{3531FF} Clothing}        & 102.88 *** & 0.42  & 240.20 & -3.66 *** & 0.60  & -6.05 & 1.47 & 1.96 & 0.75  \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l}
-& $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
+& $\beta_{2}$ &   $ SE_{\beta_{2}}$   & t      & $\beta_{3}$ & $ SE_{\beta_{3}}$ & t         \\ \hline
 {\color[HTML]{3531FF} Clothing}        & 1.2012  & 1.4206  & 0.84 & 1.69 & 1.96  & 0.86 \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l}
-                                       & $\alpha$ &   $ \sigma_{\alpha}$   & t      & $\beta_{0}$ & $\sigma_{\beta_{0}}$ & t      &  $\beta_{1}$ & $\sigma_{\beta_{1}$  & t     \\ \hline
+                                       & $\alpha$ &   $ SE_{\alpha}$   & t      & $\beta_{0}$ & $SE_{\beta_{0}}$ & t      &  $\beta_{1}$ & $SE_{\beta_{1}$  & t     \\ \hline
 {\color[HTML]{343434} Total}        & 4.43 *** &  0.58   & 7.56  & 4.03 ***  &  0.83 & 4.87  & -2.14   &  2.74    & -0.78  \\ \hline
@@
 \begin{tabular}{l|l|l|l|l|l|l}
-& $\beta_{2}$ &   $ \sigma_{\beta_{2}}$   & t      & $\beta_{3}$ & $ \sigma_{\beta_{3}}$ & t         \\ \hline
+& $\beta_{2}$ &   $ SE_{\beta_{2}}$   & t      & $\beta_{3}$ & $ SE_{\beta_{3}}$ & t         \\ \hline
 {\color[HTML]{343434} Total}        & -2.06   &  2.74   & -0.75  & -2.85    &  2.74    & -1.04  \\ \hline

### 2021-03-23 Manuscript/manuscript.tex
PUb

@@
 In particular, for the model in Ref.
-\cite{kabir2020evolutionary} it is assumed that the policy-maker perfectly knows the consequences of his/her choices and that he/she can act without delay to impose the optimal choice; finally, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range).
+\cite{kabir2020evolutionary}, it is assumed that the PM can impose a continuous factor for the lock-down (e.g., he/she can reduce the daily number of contacts between people by choosing each value between a definite range).
 In contrast, for different countries, such a factor seems to be much more discrete (e.g., the PM can reduce the daily contacts only by choosing definite values).
-It can be argued that most of these drawbacks of this last formidable research are entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy-maker.
-On this basis, we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.
-Furthermore,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.
+Moreover it is assumed that the policy-maker perfectly knows the consequences of his/her choices and that he/she can act without delay to impose the optimal choice: this feature is entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy-maker.
+Here we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.
+Moreover we will consider a discrete intensity for the lock-down.
+Finally,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.
 Thus, the final output of the model will be the cumulative deaths, the economic damage for each sales sector and the the increase of redundancy funds paid.
-Moreover, here we also considered that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them may be recovered or even should take the intensive therapy.
+Here we will also consider that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them should assisted by the national health system.
 As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the SIRD model and the lock-down days was obtained.
@@
 Clothing        & -481   & 26 & -45  & 9 \\ \hline
-Footwear        & -264   & 23 & -49  & 8 \\ \hline
+Footwear        & -468   & 23 & -49  & 8 \\ \hline
 Appliances      & -242   & 29 & -20  & 2 \\ \hline
@@
 Homeware        & -127   & 18 & -14  & 1 \\ \hline
-Household tools & -161   & 42 & -22  & 4 \\ \hline
+Household tools & -161   & 42 & -23  & 4 \\ \hline
 Games           & -342   & 41 & -48  & 3
@@
              & Active &  SE  & Lazy &   SE  \\ \hline
-Total        & 2938   & 38 & 889  & 9.7 \\ \hline
-Manufacture  & 2180   & 38 & 648  & 9.7 \\ \hline
-Trade        & 52     & 3  & 19   & 0.8 \\ \hline
-Construction & 407    & 11 & 135  & 2.8
+Total        & 2938   & 48 & 889  & 12.5 \\ \hline
+Manufacture  & 2180   & 43 & 648  & 11 \\ \hline
+Trade        & 52     & 3  & 19   & 0.6 \\ \hline
+Construction & 407    & 6.8 & 135  & 1.7
 \label{CIG_sector_effects_TAB}

### 2021-03-23 Project_script_Stochastic.R

@@ -7,6 +7,7 @@ library(readxl)
 
 
 
+
 buffer<-data.frame(matrix(ncol = 5))
 soft_lockdown_weeks<- 0
 medium_lockdown_weeks<- 0
@@ -19,9 +20,9 @@ CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-#k<-c(1,1,1)
+k<-c(1,1,1)
 #k<-c(0.9,0.9,0.9)
-k<-c(1.5,1.5,1.5)
+#k<-c(1.5,1.5,1.5)
 #k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.00000007
 rate_infection_threshold<-0.000007

### 2021-03-23 Manuscript/manuscript.tex
PUb

@@
 
-Within a standard compartmental model for describing the dynamics of epidemics (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically different types of lock-downs.
+Within a standard compartmental model for describing the dynamics of epidemic (Susceptible-Infectious-Recovered-Dead),  we considered a policy-maker (PM) that imposes stochastically different types of lock-downs.
 The probability that tunes this stochastic process reflects his/her different attitude to face an epidemics (e.g., \textit{laissez-faire} vs.
@@
 The recent pandemic due to the spread of the SARS-CoV-2 virus opened a highly debated issue about the best approach for the policy-maker to face the epidemic.
-Unlike the past pandemics of XX century (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
+Unlike the past pandemics (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
 Consequently, the modeling of the virus diffusion and the effect on socio-economic texture for different countries can be investigated with a more satisfactory resolution.
@@
 Indeed the policy-maker can adopt, at a first approximation,  a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
-In the first extreme,  the spread of the virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of the primary goods is stopped.
+In the first extreme,  the spread of the virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of many primary goods is stopped.
 On the other side,  if the PM takes no lock-down measures, the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
@@
 Here we will also consider that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them should assisted by the national health system.
-As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the SIRD model and the lock-down days was obtained.
+As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the epidemiological model was obtained.
 Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.
@@
 \end{equation}
-where S is the number of people that are still susceptible, I the number of people that are infected, and R people that are recovered, while D are people that are dead.
-N denotes the total population that for the timing of this paper it will be considered fixed\footnote{Othervise if longer horizontal timing is considered, it is necessary to consider a source term for the births and a well term for the natural deaths.
+where S is the number of people that are still susceptible, I the number of people that are infected, R people that are recovered, and D are people that are dead.
+N denotes the total population that for the timing of this paper it will be considered fixed\footnote{Otherwise if longer horizontal timing is considered, it is necessary to consider a source term for the births and a well term for the natural deaths.
 For further details see \cite{vynnycky2010introduction}}.
-On the other side, $\beta$,$\gamma$, and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular, $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality defined as the probability to die given to be ill).
+On the other side, $\beta$,$\gamma$, and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular, $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality that is defined as the probability to die given to be ill).
 Usually, epidemiologist is interested in the ratio:
@@
 As performed by Ferrari et al.
-\cite{ferrari2020modelling},  when time-dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ become time depended: thus scholar rename it as $R_{t}$.
+\cite{ferrari2020modelling},  when time-dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ becomes time depending: thus scholar rename it as $R_{t}$.
 For the present work,  we limited to constant parameters.
@@
 The overall population $N$ was set to 60M to simulate the Italian population.
-Within the daily temporal evolution of this model, which was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every seven days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces the $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$) if the normalized infected people are more than ten the previous threshold he/she will impose with certain probability restrictions that reduce the $\beta$ factor by a multiplicative factor of $0.25$; finally if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce the $\beta$ a multiplicative factor equal to $0.025$.
+Within the daily temporal evolution of this model, which was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every seven days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces the $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$) if the normalized infected people are more than ten times the previous threshold he/she will impose with certain probability restrictions that reduce the $\beta$ factor by a multiplicative factor of $0.25$; finally if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce the $\beta$ a multiplicative factor equal to $0.025$.
 These attenuation parameters were adjusted, considering the results of Marziano et al.
@@
 For these reasons here the modeling will always be referred to as national data and national lock-downs.
-Therefore, the period after June, when starting from October, regional lock-down, will not be considered.
+Therefore the lock-down that were applied starting October were not considered, while in the months of July, August and September the restriction were so weak that can be considered negligible for our model.
 Another point that is worth mentioning is that in this model, on the contrary concerning the SIS one, individuals can not re-infect: concerning the COVID-19, the possibility of reinfection is still discussed among scholars \cite{ledford2020covid,iwasaki2021reinfections}.
@@
 Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
-This choice is based on the idea that,  if the PM misbehaves,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and then,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle require an epidemiological model in which also the age of people is taken into account.
+This choice is based on the idea that,  if the PM misbehaves,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and then,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle requires an epidemiological model in which also the age of people is taken into account.
 However, as said before, a partial differential equations system should be solved, making the calculation and the computational cost incredibly high.}.
@@
 where $Y$ is the selected outcome (sales value or redundancy funds), $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group, and $\epsilon$ an error term.
-As a control group for the sales value,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless for the lock-down\footnote{Although it is true that a slight increase of food sales value during the lock-down is present in the plots in Fig.
+As a control group for the sales value,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless of the lock-down\footnote{Although it is true that a slight increase of food sales value during the lock-down is present in the plots in Fig.
 \ref{Selling_plots} \ref{Selling_plots_II},  it must be stressed the fact that, as proven numerically in the Supporting Info A, this change does not significantly affect the DID estimations }.
-On the other side,  for redundancy funds \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarità as the control group (note that this subsidy is different with respect Cassa Integrazione Solidarità that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
+On the other side,  for redundancy funds \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarietà as the control group (note that this subsidy is different respect respect Cassa Integrazione Solidarietà that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
 This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labor cost but at the same time guaranteeing to the workers part of their original salary \footnote{It is worth noting that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact, there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
@@
 In particular, we considered the period starting from June 2018 up to June 2020 for the eight sales value categories described in the previous section .
-The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not to national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
+The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not at national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
 Moreover, if regional clusters were considered, it was necessary to model an ensemble of SIRD models that communicate with a defined rate (that change also with respect to the lock-down restriction).
@@
 As discussed in Supporting Information,  these data were not de-seasoned.
-Thus, we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transform  \cite{huang1998empirical} for the decomposition of a time series data.
+Thus, we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transformation \cite{huang1998empirical} for the decomposition of a time series data.
 The decomposition results are reported in the Supporting Info E.

### 2021-03-24 Manuscript/manuscript.tex
PUB

@@
 very strict).
-In order to simulate not only an epidemiological scenario but also an economic one, we estimated, via a Difference-in-Difference regression,  the impact of national lock-downs applied during the first wave of COVID19 in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales value and redundancy funds (\textit{Cassa Integrazione}).
+In order to simulate not only an epidemiological scenario but also an economic one, we estimated, via a Difference-in-Difference regression,  the impact of national lock-downs applied during the COVID19 first wave in Italy from March 2020 to June 2020,  on two microeconomic sectors: sales values and redundancy funds (\textit{Cassa Integrazione}).
 We found that by modifying with continuity the PM attitude to impose the lock-down, a phase transition (as defined for a physical system) is obtained.
@@
 The recent pandemic due to the spread of the SARS-CoV-2 virus opened a highly debated issue about the best approach for the policy-maker to face the epidemic.
-Unlike the past pandemics (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
+Unlike past pandemics of XX century (e.g., Spanish Flu,  Asiatic Flu, and Hong-Kong Flu), a massive amount of data are easily accessible for this pandemic.
 Consequently, the modeling of the virus diffusion and the effect on socio-economic texture for different countries can be investigated with a more satisfactory resolution.
@@
 Indeed the policy-maker can adopt, at a first approximation,  a linear combination between these two extreme approaches: forcing all people to stay at home or to \textit{laissez-faire}.
-In the first extreme,  the spread of the virus is,  of course, stopped but,  on the other side,  the toll for such approach is that not only the economic activity (and so the income of people/firms) but also that the furniture of many primary goods is stopped.
+In the first extreme there is a slowdown in the spread of the virus but with a consequence not only on economic activity (and so income of people/firms) but also that the furniture of many primary goods is stopped.
 On the other side,  if the PM takes no lock-down measures, the toll to be paid will be not only the high number of deaths but also the economic damage produced by the very high number of deaths \cite{Correia2020,karlsson2014impact}.
-In practice, the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion to others (for this purpose, an excellent analysis was provided by Li et al.
+In practice, the PM can adopt intermediate approaches that shut down activities that contribute much more to diffusion than others (for this purpose, an excellent analysis was provided by Li et al.
 in  \cite{li2021temporal} and by Brauner et al.
 in \cite{brauner2021inferring}).
-As a consequence, the lock-down efficacy,  within certain limits,  can be tuned.
+As a consequence, the lock-down efficacy,  within certain limits,  can be regulated.
 In the literature, different scholars \cite{kabir2020evolutionary,rowthorn2020cost} challenged the issue of finding the optimal lock-down policy for minimizing the economic impact as well as the deaths.
@@
 Moreover it is assumed that the policy-maker perfectly knows the consequences of his/her choices and that he/she can act without delay to impose the optimal choice: this feature is entangled with the fact that a deterministic approach was considered for the activation of the lock-downs by the policy-maker.
-Here we would propose here an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.
+Here we would propose an alternative way to model the decision of the policy-maker that is based on a stochastic model instead of on a deterministic one.
 Moreover we will consider a discrete intensity for the lock-down.
-Finally,  differently to the previous researches that focused basically on macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level: in particular, through the difference in difference,  we evaluated the effect of the different levels of lock-down on different sales sector as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.
-Thus, the final output of the model will be the cumulative deaths, the economic damage for each sales sector and the the increase of redundancy funds paid.
-Here we will also consider that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also average cost for each infected person (referring to Italian data) because a consistent part of them should assisted by the national health system.
+Finally,  differently to previous researches that focused basically on a macroeconomic impact,  here we estimated and put in the model the impact of the different lock-downs at the microeconomic level.
+In particular, through difference in difference (DID) ,  we evaluated the effect of the different levels of lock-down on different sales sectors as well as on redundancy funds (\textit{Cassa Integrazione Ordinaria}) in Italy.
+Thus, the final output of the model will be the cumulative deaths, the economic damage for each sale sector and the increase of redundancy funds paid.
+Here we will also consider that there is not only an economic cost for each death as done by \cite{kabir2020evolutionary}, but there is also an average cost for each infected person (referring to Italian data) because a consistent part of them should be assisted by the national health system.
 As we will show by varying with continuity the probabilistic parameter by which the PM imposes the lock-down,  a discontinuity in the epidemiological model was obtained.
 Such behaviour belongs to a class of phenomena that, in physical sciences, is called a phase transition.
-For each phase, we will discuss the result of the simulation, and then we will compare them to get a general insight.
+For each phase, we will first discuss the result of the simulation, then we will compare them to get a general insight.
 
-\section{Model and methods}
+\section{Models and methods}
 
-The model of the present study is composed of an epidemiological part that shapes the diffusion of the virus.
-Then its output is used by the economic model to quantify the damage.
+The model of this study is composed of an epidemiological part that shapes the diffusion of the virus.
+Its output is then used by the economic model to quantify the damage.
 Thus we will discuss the epidemiological part and then the economic one
@@
 \end{equation}
-where S is the number of people that are still susceptible, I the number of people that are infected, R people that are recovered, and D are people that are dead.
-N denotes the total population that for the timing of this paper it will be considered fixed\footnote{Otherwise if longer horizontal timing is considered, it is necessary to consider a source term for the births and a well term for the natural deaths.
+where S is the number of people that are still susceptible, I the number of people that are infected, R people that are recovered, and D people that are dead.
+N denotes the total population that for the timing of this paper will be considered fixed\footnote{Otherwise if longer horizontal timing is considered, it is necessary to consider a source term for the births and a well term for the natural deaths.
 For further details see \cite{vynnycky2010introduction}}.
 On the other side, $\beta$,$\gamma$, and $\mu$ are the parameters that shape the probability by which one individual in the model moves from a compartment to another: in particular, $\beta$ is the probability to be infected, $\gamma $ the probability to recover and $\mu$ the probability to die (basically the lethality that is defined as the probability to die given to be ill).
-Usually, epidemiologist is interested in the ratio:
+Usually, epidemiologists are interested in the ratio:
 \begin{equation} 
@@
 As performed by Ferrari et al.
-\cite{ferrari2020modelling},  when time-dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ becomes time depending: thus scholar rename it as $R_{t}$.
+\cite{ferrari2020modelling},  when time-dependent parameters $\beta$ and $\gamma$ are taken in to account the reproduction factor R$_{0}$ becomes time dependent: thus scholar rename it as $R_{t}$.
 For the present work,  we limited to constant parameters.
 In particular, we considered the parameter estimation for Lombardy provided by Neves and Guerrero in Ref \cite{neves2020predicting}: $\beta$ was set equal to 0.55 while $\gamma$ equal to $\frac{1}{7}$.
-The $\mu$ was set in order to keep in to account the calculated lethality for Italy: 1 \% \cite{fernandez2020estimating} (see also the excellent analysis made by the Institute for International Political Studies (ISPI) \cite{ISPI})\footnote{The authors are aware that this ratio is far from being homogeneous for the different ages of the population: however if this factor is taken into account,  it requires the solution of a system of partial derivative equations.
+$\mu$ was set in order to keep into account the calculated lethality for Italy: 1 \% \cite{fernandez2020estimating} (see also the excellent analysis made by the Institute for International Political Studies (ISPI) \cite{ISPI})\footnote{The authors are aware that this ratio is far from being homogeneous for the different ages of the population: however if this factor is taken into account,  it requires the solution of a system of partial derivative equations.
 In this case, the numerical calculations become much more complicated}.
 The overall population $N$ was set to 60M to simulate the Italian population.
-Within the daily temporal evolution of this model, which was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every seven days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces the $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$) if the normalized infected people are more than ten times the previous threshold he/she will impose with certain probability restrictions that reduce the $\beta$ factor by a multiplicative factor of $0.25$; finally if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce the $\beta$ a multiplicative factor equal to $0.025$.
-These attenuation parameters were adjusted, considering the results of Marziano et al.
+Within the daily temporal evolution of this model, which was obtained by numerically solving the differential equation above via the \textit{DeSolve} package, we considered a trigger activated by the PM every seven days: if the number of infected people normalized by the overall population is more than $1\times 10^{-7}$,  there is a probability that the PM imposes laws that reduces $\beta$ factor by a multiplicative factor equal to $0.7$ (and thus the reproduction factor $R_{0}$).
+If the normalized infected people are more than ten times the previous threshold he/she will impose with certain probability restrictions that reduce $\beta$ factor by a multiplicative factor of $0.25$; finally if the threshold is exceeded more than 50 times, the PM will impose with a certain probability restrictive measures that reduce $\beta$ to a multiplicative factor equal to $0.025$.
+These attenuation parameters were adjusted, considering results of Marziano et al.
 in Ref.
@@
 As we said, the PM acts with a certain probability,  more formally stochastically; each week, a random number (from zero to one) is extracted: if this is higher than a certain threshold,  the relative restrictive decision is taken, otherwise not.
-The threshold value captures the PM attitude to impose the lock-down: lower values model a careful PM, high value a lazy one.
+The threshold value captures the PM attitude to impose the lock-down: lower values model a careful PM, high values a lazy one.
 In this way, the model can simulate different scenarios for the different PM attitudes: as we will see, this can produce two very different results.
-At the end of the simulation, besides the values given by the standard SIRD model (recovered and deaths),  the algorithm also provides the number of weeks in which each restriction was active: these values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
+At the end of the simulation, besides the values given by the standard SIRD model (recovered and deaths),  the algorithm also provides the number of weeks in which each restriction was active.
+These values are then used for the economic model in order to evaluate the economic effect due to the restrictions and PM strategy.
 It is worth noting that here as lock-down, we considered only the national one applied in the first wave of the epidemics: from March 2020 to June 2020.
-This choice is motivated by the fact that modeling a unique system is easier concerning modeling an ensemble of communicating clusters that represent regions or provinces: therefore, if one is interested in modeling the second wave of pandemics, such an approach should be undertaken.
-Moreover, in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at the regional or province level,  and as far as the authors know, such data are not available.
+This choice is motivated by the fact that modeling a unique system is easier with respect to modeling an ensemble of communicating clusters that represent regions or provinces: therefore, if one is interested in modeling the second wave of pandemics, such an approach should be undertaken.
+Moreover, in this latter case,  as a further degree of complexity,  the economic data described in the next subsection must be at the regional or province level and as far as the authors know, such data are not available.
 For these reasons here the modeling will always be referred to as national data and national lock-downs.
-Therefore the lock-down that were applied starting October were not considered, while in the months of July, August and September the restriction were so weak that can be considered negligible for our model.
-Another point that is worth mentioning is that in this model, on the contrary concerning the SIS one, individuals can not re-infect: concerning the COVID-19, the possibility of reinfection is still discussed among scholars \cite{ledford2020covid,iwasaki2021reinfections}.
-As far as the authors know, it is established that the immunity lasts at least eight months  \cite{dan2021immunological} and very few reinfection cases are reported.
-Thus the immunity considered in the model for one year seems almost a realistic approximation.
+Therefore the lock-down that were applied starting October were not considered, while in the months of July, August and September the restrictions were so weak that can be considered negligible for our model.
+Contrary to the SIS (susceptible-infected-susceptible) one, individuals can not re-infect: concerning the COVID-19, the possibility of reinfection is still discussed among scholars \cite{ledford2020covid,iwasaki2021reinfections}.
+As far as the authors know, it is established that immunity lasts at least eight months  \cite{dan2021immunological} and very few reinfection cases are reported.
+Thus the year immunity considered in the model seems almost a realistic approximation.
 
@@
 
-The economic impact for each epidemiological scenario is shaped as follow: the first set of parameters,  as the economic value of death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on sales for different areas and on unemployment benefit (Cassa Integrazione Guadagni) were evaluated with empirical approaches from raw data.
-Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (300k EUR).
-This choice is based on the idea that,  if the PM misbehaves,  can be incriminated for manslaughter (with the consent of parliament that has to validate the incrimination) and then,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keep into account the age of the deaths: this in principle requires an epidemiological model in which also the age of people is taken into account.
+The economic impact for each epidemiological scenario is shaped as follow: the first set of parameters,  as the economic value of death and of being infected by COVID-19, was taken directly from the reports/documentation of official sources; other parameters as the effect on sales for different areas and on redundancy funds (Cassa Integrazione Guadagni), were evaluated with empirical approaches from raw data.
+Concerning the first set,  the number of deaths is multiplied by the maximum compensation value provided by the Court of Milan \cite{tribunaleMilano} for manslaughter (332k EUR).
+This choice is based on the idea that,  if the PM misbehaves,  can be incriminated for manslaughter (with the consent of the parliament that has to validate the incrimination) and then,  if judged guilty,  charged by this amount for each death\footnote{In principle the judge also keeps into account the age of the deaths: this in principle requires an epidemiological model in which also the age of people is taken into account.
 However, as said before, a partial differential equations system should be solved, making the calculation and the computational cost incredibly high.}.
 Besides this impact,  there is also the cost associated with the medical care of each ill people.
-For this, we considered the national average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another import health-care impact because the ill people for COVID-19 saturate the health system thus making it unreachable for other diseases.
-This spillover translates into more death and more ill people for the baseline situation where there is not a pandemic: however,  by now,  this effect is difficult to quantify, and so we did not include it in the present model}.
-Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the sales value for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the rest part of the paper, these categories will be referred to as the part of the name labeled in blue.
+For this we considered the national average value calculated by National Anti-Corruption Authority (ANAC) \cite{Anac}: 28.180 kEUR \footnote{It is worth noting that,  in principle,  there is also another important health-care impact because COVID-19 ill people saturate the health system making it unreachable for other diseases.
+This spillover translates into more deaths and more ill people for the baseline situation where there is not a pandemic: however,  by now,  this effect is difficult to quantify and so we did not include it in the present model}.
+Among the different sectors affected by the pandemic and the consequent lock-down,  we focused on the sales values for the following ATECO-2007 \cite{Ateco2007} categories \footnote{In the remaining part of the paper, these categories will be referred to as part of the name labelled in blue.
 }: \textcolor{blue}{Food}, \textcolor{blue}{Clothing} and furs, \textcolor{blue}{Footwear}/leather and travel articles, Household \textcolor{blue}{Appliances}/radios/televisions and
@@
 \textcolor{blue}{Photo-optics}/films/compact discs/audio-video cassettes and musical instruments, Durable and non-durable \textcolor{blue}{Homeware}, \textcolor{blue}{Household tools} and hardware tools, \textcolor{blue}{Games}/toys/sports and camping articles.
-The choice to use sales value as a parameter for the evaluation of the lock-down lies in the fact that with them is possible to capture not only the contraction for each sector but also the loss for the public treasury due to to the reduced incomes from the VAT\footnote{For this purpose another sector that in principle can also be considered is the contraction of fuel sales value, due to the reduced mobility, where in addition to the VAT there is also fixed taxation (accisa).
+The choice to use sales values as a parameter for the evaluation of the lock-down lies in the fact that with them is possible to capture not only the contraction for each sector but also the loss for the public treasury due to the reduced incomes from the VAT\footnote{For this purpose another sector that can also be considered is the contraction of fuel sales values, due to the reduced mobility, where in addition to the VAT there is also fixed taxation (accisa).
 Such calculation may be considered as a future outlook of this work}.
-Beside the sales value we also considered the unemployment benefit for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
-Furthermore also the total value (considering also other sectors that were not analysed here).
-In this case,  the choice to use also this parameter is based on the fact that this is the first aid provided by the Government for the firms that were damaged by the lock-down restrictions.
-For the empirical evaluation of the impact on sales value and redundancy funds, we performed a multiple time Difference in Difference as presented in Refs.
+Beside the sales values we also considered the redundancy funds for the following ATECO sectors: \textcolor{blue}{Manufacturing} activities, \textcolor{blue}{Construction} , \textcolor{blue}{Wholesale} and retail trade/ repair of motor vehicles-motorcycles and personal and household goods.
+Furthermore, also the total value was included (its value is given also by the sum of other sectors that were not analysed here).
+In this case, the choice to consider the redundancy funds is based on the fact that this is the first aid provided by the Government for firms that were damaged by lock-down restrictions.
+For the empirical evaluation of the impact on sales values and redundancy funds, we performed a multiple time Difference in Difference as presented in Refs.
 \cite{draca2011panic},  \cite{imbens2009recent} and \cite{wooldridge2012introductory}.
@@
 \end{equation}
-where $Y$ is the selected outcome (sales value or redundancy funds), $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group, and $\epsilon$ an error term.
-As a control group for the sales value,  we considered the food ones since,  in principle,  people can be considered to use almost the same amount of food regardless of the lock-down\footnote{Although it is true that a slight increase of food sales value during the lock-down is present in the plots in Fig.
+where $Y$ is the selected outcome (sales values or redundancy funds), $\alpha$ the intercept, $T_{i}$ a dummy variable for the lock-down timing i,  $C$ a dummy for the treated group, and $\epsilon$ an error term.
+As a control group for sales values we considered food since people almost consumed the same amount despite the lock-down\footnote{Although it is true that a slight increase of food sales values during the lock-down is present in the plots in Fig.
 \ref{Selling_plots} \ref{Selling_plots_II},  it must be stressed the fact that, as proven numerically in the Supporting Info A, this change does not significantly affect the DID estimations }.
-On the other side,  for redundancy funds \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarietà as the control group (note that this subsidy is different respect respect Cassa Integrazione Solidarietà that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
-This subsidy can be used by firms,  damaged by the pandemics and by the lock-downs,  in order to reduce their labor cost but at the same time guaranteeing to the workers part of their original salary \footnote{It is worth noting that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact, there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
+On the other side,  for redundancy funds \textit{Cassa integrazione},  we considered the Cassa Integrazione Straordinaria - Solidarietà as control group (note that this subsidy is different respect respect Cassa Integrazione Solidarietà that was dedicated to sectors not covered by Cassa Integrazione Ordinaria).
+This subsidy can be used by firms damaged by the pandemics and by the lock-downs  in order to reduce their labor cost but at the same time guaranteeing to the workers part of their original salary \footnote{It is worth noting that the \textit{Cassa Integrazione Ordinaria} considered here is not the only one contribution that was provided by Italian Government: in fact, there was also, for instance,  the \textit{Cassa Integrazione in Deroga} that was dedicated to the firms not covered by the \textit{Ordinaria}.
 However, in the present study, we consider, for simplicity,  only the sectors covered by Cassa Integrazione Ordinaria.
 }.
-During the first months of the pandemic,  following the rules stated by the Italian Government (Decreto Cura Italia \cite{curaitalia}),  firms that would reduce their labor cost first forced the employees to use their holiday budget and then,  after it was run out,  they put the employees into the Cassa Integrazione Ordinaria.
+During the first few months of the pandemic,  following the rules stated by the Italian Government (Decreto Cura Italia \cite{curaitalia}),  firms that reduces their labor cost first forcing the employees to use their holiday budget and then,  after consuming it all,  they put the employees into Cassa Integrazione Ordinaria.
 Thus the Cassa Integrazione Straordinaria-Solidarietà can be considered as not treated by the first wave of the lock-down, while the ordinary one treated.
-The DID consider here has three different times for the national lock-down:  for the sales value, we considered  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
-On the other side concerning the redundancy funds,  we considered as medium lock-down only May 2020 while for the high and low lock-down the timing were identical to the sales value.
-Such choice was motivated by the fact that the effect of firms to use the redundancy funds for workers was slightly delayed because in March 2020 firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}: as a consequence,  because of this buffer effect,  in March there is no significant effect of this redundancy funds although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
-Performing the DID, we estimated the coefficients for each intensity of lock-down on sales value and redundancy funds.
-Then these were rescaled in order to obtain a weekly value.
-Finally, we multiplied the coefficients obtained from the DID (scaled from months to weeks) by the number of lock-down weeks,  with the respective intensity,  in each scenario simulated via the epidemiological model described before.
-As a consequence, we obtained,  for each scenario,  an economics simulation based on parameters obtained from an empirical evaluation.
+DID considered here has three different time period for the national lock-down:  for the sales values, we considered  the months of March 2020 and May 2020 as medium lock-down, the month of April 2020 as high lock-down, and June 2020 as low lock-down.
+On the other side concerning redundancy funds we considered as medium lock-down only May 2020 while for the high and low lock-down the timing were identical to the sales values.
+Such choice was motivated by the fact that the effect of firms to use the redundancy funds for workers was slightly delayed because in March 2020 firms forced their employees first to use their holiday and then the \textit{Cassa Integrazione Ordinaria}.
+As a consequence,  because of this buffer effect,  in March there is no significant effect of this redundancy funds although there is a significant reduction of hours worked (see, e.g., \cite{istat_lavoro}).
+Performing the DID we estimated the coefficients for each intensity of lock-down on sales values and redundancy funds.
+These values were then rescaled in order to obtain weekly value.
+Finally, we multiplied the coefficients obtained from the DID (scaled from months to weeks) by the number of lock-down weeks,  with the respective intensity, for each scenario simulated via the epidemiological model described before.
+As a consequence we obtained,  for each scenario,  an economics simulation based on parameters obtained from an empirical evaluation.
 
@@
 
-The monthly sales value data (with the baseline $100=2015$) were retrieved from the National Institute of Statistics website \cite{istat}.
-In particular, we considered the period starting from June 2018 up to June 2020 for the eight sales value categories described in the previous section .
-The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at the regional level and not at national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed on regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
+The monthly sales values data (with the baseline $100=2015$) were retrieved from the National Institute of Statistics website \cite{istat}.
+In particular, we considered the period starting from June 2018 up to June 2020 for the eight sales values categories described in the previous section .
+The choice to not consider the months after June and, in particular, the last part of the year lies in the fact that in the latter lock-downs were imposed at a regional level and not at a national level \footnote{With the only exception of the Christmas holiday}  \footnote{In principle one may ask why the present analysis was not performed at a regional cluster making it more flexible: unfortunately the economic data used here, as far as the author knows,  were not available,  at all for a regional cluster.
 Moreover, if regional clusters were considered, it was necessary to model an ensemble of SIRD models that communicate with a defined rate (that change also with respect to the lock-down restriction).
@@
 Thus, we performed a de-seasoning via the \textit{Forecast} R package \cite{forecast} that uses a Hilbert-Huang transformation \cite{huang1998empirical} for the decomposition of a time series data.
-The decomposition results are reported in the Supporting Info E.
-Concerning monthly redundancy funds paid we retrieved the data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
+Decomposition results are reported in the Supporting Info E.
+Concerning monthly redundancy funds paid we retrieved data from the \textit{Osservatorio Cassa integrazione guadagni e fondi di solidarietà} on the \textit{Istituto nazionale della previdenza sociale} webpage \cite{inps}.
 Here the period considered also starts from June 2018 up to June 2020 for the four categories described in the previous section.
 It is worth noting that we considered only the authorized (paid) redundancy funds and not the asked ones.
-Furthermore,  differently for the sales value, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
+Furthermore,  differently from the sales values, these data were not affected by seasonality noise,  and thus no de-seasoning was necessary.
 
@@
 
-As done for the section Model and methods, we will divide the discussion of the results in the following way: first, the outcomes of the economic model will be presented,  then basing on this result,  we will discuss the scenarios obtained with them via the epidemiological model.
+As done for the section \textit{Model and methods}, we will divide  discussion of the results in the following way: first, the outcomes of the economic model will be presented then, based on this result,  we will discuss the scenarios obtained with them via the epidemiological model.
 Finally, we will discuss the overall results.
@@
 
-For each sales value category we run the regression reported in the Eq.
+For each sales values category we run the regression reported in Eq.
 \ref{DID-eq} on de-seasoned data reported in Fig \ref{Selling_plots} and \ref{Selling_plots_II}.
 The coefficients obtained are reported in Tab.
-\ref{selling_DID_table_delta} (the estimation of the other parameters is given in Supporting Information D).
+\ref{selling_DID_table_delta} (estimation of the other parameters is given in Supporting Information D).
 As one can point out from the plots, there is indeed a pre-trend in the data before the event,  however as proved numerically in the Supporting Info B,  the slope of this pre-trend is up to two orders of magnitude lesser for the slope in the lock-down T$_{1}$ and $T_{2}$.
 Consequently, this pre-trend,  compared to the lock-down effect,  can be considered negligible.
-As a further check,  a placebo test was performed by choosing timing before the pandemic of COVID19.
+As further check, placebo test was performed by choosing timing before the COVID19 pandemic.
 As illustrated in Supporting Info C,  this test was successful.
 On the other side,  concerning $T_{3}$  (low lock-down),  only the effect for clothing and footwear can be considered significant.
-Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations,  only the clothing, and footwear sectors.
-The same DID regression was used for the redundancy funds,  using as the control group the extraordinary solidarity redundancy funds (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
+Thus,  concerning $T_{3}$,  we considered not null,  in the scenario simulations,  only clothing and footwear sectors.
+The same DID regression was used for the redundancy funds,  using as control group the extraordinary solidarity redundancy funds (cassa integrazione straordinaria solidarietà): the plot of the data and the DID coefficients are reported in Fig.
 \ref{CIG_sector_plots} and Tab \ref{CIG_DID}.
 Also in this case the placebo tests were successfully performed.
-An interesting insight is also provided by the inspection of the extraordinary redundancy funds for renovation ( \textit{cassa integrazione ristrutturazione}): these redundancy funds, compared to the solidarity ones, seem much more sensitive for an external shock in particular for the trade sector.
+An interesting insight is also provided by the inspection of the extraordinary redundancy funds for renovation ( \textit{cassa integrazione ristrutturazione}): these redundancy funds, compared to the solidarity ones, seem much more sensitive for an external shock and in particular for the trade sector.
 
@@
 \ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost}  the outcomes of the epidemiological model are given,  while the SIRD curves for the scenarios are provided in Fig.
-\ref{SIRD_scenario}; on the other side the effect on sales value and redundancy funds for both scenarios are given in Fig.
+\ref{SIRD_scenario}; on the other side the effect on sales values and redundancy funds for both scenarios are given in Fig.
 \ref{Selling_sector_effects} and \ref{CIG_sector_effects}.
@@
 First,  we see that where the PM is more reactive, we have different small epidemics waves.
-In contrast, if the PM is poorly reactive, only one intense wave is present,  indeed in the latter scenario, the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: when the PM acts is too late,  as shown in Fig.
+In contrast, if the PM is poorly reactive, only one intense wave is present.
+Indeed, in the latter scenario, the laziness of PM to apply the lock-down in the first weeks produce the full infection peak of the standard SIRD model: in this case the PM acts too late, as shown in Fig.
 \ref{SIRD_scenario}, since the pandemic has almost hit the large part of the population.
@@
 \ref{R_t_scenarios} this result is basically obtained by keeping the reproduction factor in the value of medium lock-down value \footnote{These two theoretical models correspond,  in practice,  for the lazy PM to the one considered by the PMs that aimed to herd immunity.
-At the same time,  concerning the active-PM,  to the PMs that would not saturate the health system and aimed to reduce the death at the minimum.} It is interesting to point out that the change between the scenarios develops in a discontinuous way as shown in Fig.
+At the same time the active-PM correspond to the PMs that would not saturate the health system and aimed to reduce the death at the minimum.}.
+It is interesting to point out that the change between the scenarios develops in a discontinuous way, as shown in Fig.
 \ref{Phase_transition}, as the reactivity of the PM is changed, we can consider this as a phase transition of a physical system (e.g., consider the gold-standard diagram of Ising model \cite{Ising,Ising_2}).
@@
 \cite{Vespignani}.
-The explanation of this similar behavior is that both models have a stochastic component,  that as pointed out by Balcan and Vespignani, gives the phase transition.
-While in their model, this was directly related to the contagion probability, this is indirectly made stochastically by PM's decision that modifies the $\beta$ parameter and so the transmission rate.
+The explanation for this similar behavior is that both models have a stochastic component,  that as pointed out by Balcan and Vespignani, gives the phase transition.
+While in their model this was directly related to the contagion probability, this is indirectly made stochastically by PM's decision that modifies the $\beta$ parameter and so the transmission rate.
 The phase transition discussed here shows that even though the PM can tune within a specific limit the contagion ratio, as said in the introduction, the outcomes due to his/her reactivity are binary due to the collective behavior of individuals in the SIRD model with the stochastic lockdown.
@@
 Moving to the socio-economic outcome of the model used, we see, from Tab.
-\ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost},  that in the small wave scenario,  the attitude of the PM largely reduce the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by consistent use of the confinement.
+\ref{Table_Epidemiological_effect} and \ref{Table_Epidemiological_cost},  that in the small wave scenario,  the attitude of the PM largely reduces the overall number of deaths and recovered (and so the cumulative cost for taking of patients) by a consistent use of the confinement.
 This has an immediate drawback on the economic data: as shown in Fig.
 \ref{Selling_sector_effects} and \ref{CIG_sector_effects} (and in Tab.
-\ref{Selling_sector_effects_TAB} and \ref{CIG_sector_effects_TAB}) the losses for sales value and the use of redundancy funds are widely large concerning the one-wave scenario.
-In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  sales value, and redundancy funds): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option (e.g.
+\ref{Selling_sector_effects_TAB} and \ref{CIG_sector_effects_TAB}) the losses for sales values and the use of redundancy funds are widely large concerning the one-wave scenario.
+In principle, one can be attempted to find the PM attitude that minimizes the overall cost (deaths,  infected,  sales values, and redundancy funds): in the authors view, this scenario is not realistic since,  actually,  the Italian (but also many other European) criminal law does not allow this option (e.g.
 art.
-452 Codice Penale) although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money compared to a money sum,  on contrary it gives a value ex-post, not ex-ante \footnote{This point is also based on the different rulings of the Italian Constitutional Court that declared the right of life as "the essence of the supreme values ​​on which the Italian Constitution is based" \cite{cort_cost}.
+452 Codice Penale).
+Although there is an economic cost for life in terms of compensation,  the actual criminal law does not consider an amount of money comparable to a life: indeed it gives a value ex-post, not ex-ante \footnote{This point is also based on the different rulings of the Italian Constitutional Court that declared the right of life as "the essence of the supreme values ​​on which the Italian Constitution is based" \cite{cort_cost}.
 Note that this interpretation is the legal basis for which the lock-down can be adopted since it limits the constitutional rights contained in the Art.
-13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.) (see also \cite{cost_discussion}}).
-A more complex issue come up when the economic cost is causally associated with a number indirect of deaths (for instance, if people does not have the money for food or other first necessity goods ),  in this case, the two factors (epidemiological and economic) can be,  in principle, summed \footnote{We say in principle because the jurisprudence is significantly reduced or missing since the pandemics are rare}.
-For the present study, these indirect deaths are,  by now,  not easy to quantify, and thus, we did not consider this option.
+13,16,17,18,19,24,27,33 and 34, in order to preserve the right of life and of health (Art 32.) (see also \cite{cost_discussion}}.
+A more complex issue arises when the economic cost is causally associated with a number indirect deaths (for instance, if people does not have the money for food or other first necessity goods ).
+In this case, the two factors (epidemiological and economic) can be,  in principle, summed \footnote{We say in principle because the jurisprudence is significantly reduced or missing since the pandemics are rare}.
+For the present study, these indirect deaths are,  by now,  not easy to quantify, and thus we did not consider this option.
 
@@
 We have obtained a model that combines the epidemiological aspects and the economic ones within a stochastic approach.
-This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales value sectors and the redundancy funds dedicated to firms that would reduce the labor cost.
+This was made possible by evaluating the effect of lock-downs, via a DID regression,  on different sales values sectors and the redundancy funds dedicated to firms that would reduce the labor cost.
 Furthermore, we show numerically that,  within a stochastic approach,  the PM attitude to impose the lock-downs is critical.
@@
      \end{subfigure}
-\caption{Sales value data (I), with the baseline $100=2015$,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+\caption{Sales values data (I), with the baseline $100=2015$,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
 The timing for each lock-down is marked with a dashed line: red for high, orange medium, and green for low.
@@
   \label{fig:y equals x}
-\caption{Sales value data (II), with the baseline $100=2015$,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
+\caption{Sales values data (II), with the baseline $100=2015$,  as provided by \cite{istat} de-seasoned via Forecast package \cite{forecast} for the categories  analysed in this paper compared with \textcolor{red}{food} (red) category.
 Each lock-down timing is marked with a dashed line: red for high, orange medium, and green for low.
@@
 \begin{flushleft}
-$\delta$ coefficients as obtained by the DID  regression, for sales value data (with the baseline $100=2015$) de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
+$\delta$ coefficients as obtained by the DID  regression, for sales values data (with the baseline $100=2015$) de-seasoned,  according to equation \ref{DID-eq} \\ for the different lock-down timings.
 The values of the intercept ($\alpha$), $\beta_{0}$ and $\beta_{i}$ are provided in the Supporting Info.
@@
 In the left panel, an active PM is considered: this is modeled by making it more likable that the PM imposes the lock-down as the number of infected goes over the different thresholds.
-On the contrary,  in the left panel, a lazy PM that prefers the \textit{laissez-faire} approach is considered: in this case,  differently from the previous scenario, the probability that the PM imposes the lock-down is less likely.
+On the contrary,  in the right panel, a lazy PM that prefers the \textit{laissez-faire} approach is considered: in this case,  differently from the previous scenario, the probability that the PM imposes the lock-down is less likely.
 }
@@
      \end{subfigure}
-\caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
+\caption{Sales values effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to provide weekly values).
 The standard error bars were calculated by considering the error propagation
@@
      \end{subfigure}
-\caption{Redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs.
+\caption{Ordinary redundancy funds variation (in terms of million of hours paid) for the scenarios where an active vs.
 lazy PM is considered.
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to provide weekly values).
 The standard error bars, although they are not clearly visible because they are too reduced,  were calculated by considering the error propagation}
@@
 \begin{center}
-\caption{Cost associated with deaths and infected people that need to be assisted in terms of $10^{9}$ EUR.
+\caption{Cost associated with deaths and infected people that need to be assisted in terms of $10^{6}$ kEUR.
 The  value of life correspond to the maximum compensation according to Milan court \cite{tribunaleMilano},  while the cost for infected people was taken from ANAC report \cite{Anac}}
@@
          & Active & Lazy \\ \hline
-Deaths   & 11     & 1170 \\ \hline
+Deaths   & 13     & 1295 \\ \hline
 Infected & 15     & 1538 \\ \hline
-Total    & 26     & 2708 \\ \hline
+Total    & 28     & 2833 \\ \hline
 \label{Table_Epidemiological_cost}
@@
 \caption{Sales value effects for the scenarios where an active vs lazy PM is considered (with the baseline $100=2015$).
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (divided by 4).
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to provide weekly values).
 The standard errors were calculated by considering the error propagation}
@@
 lazy PM is considered.
-These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to obtain the week value).
+These effects were calculated by running a DID regression for the different national lock-down imposed during March-June 2020 and then multiplying the number of lock-down weeks obtained from the SIRD scenario with the coefficients obtained from the DID (scaled in order to provide weekly values).
 The standard errors were calculated by considering the error propagation.}
@@
 {\color[HTML]{F56B00} Appliances}      & 4.64 & 8.66  & 0.54 & 1.14 & 6.26  & 0.18  & -0.81  & 8.66 & -0.09  \\ \hline
-{\color[HTML]{00009B} Photo-optics}    & 1.71 & 15.18  & 0.11 & 0.84 & 10.99 & 0.07 & 0.70  & 15.18  & 0.11  \\ \hline
+{\color[HTML]{00009B} Photo-optics}    & 1.71 & 15.18  & 0.11 & 0.84 & 10.99 & 0.07 & 0.70  & 15.18  & 0.05  \\ \hline
 {\color[HTML]{6200C9} Homeware}   & 1.23 & 5.15  & 0.24 & -0.07 & 3.72  & -0.018  & -0.86  & 5.15 & -0.17 \\ \hline

### 2021-03-24 Analisi_vendite/Test vari/Plotter_destag.R

@@ -6,14 +6,14 @@ ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_
   geom_vline(xintercept = -4, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = -3, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = -2, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = -1, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
+  geom_vline(xintercept = -1, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Sales value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
 
 
 ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_line(size=2,aes(x=Time,y=Abbigliamento),color = "blue")+ 
   geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
+  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Sales value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
 
 
 
@@ -22,49 +22,49 @@ ggplot(data=Data,aes(x=Time,y=Alimentari))+geom_line(size=2,color = "red")+geom_
   geom_vline(xintercept = 1, linetype="dashed", color = "orange", size=1)+ 
   geom_vline(xintercept = 2, linetype="dashed", color = "red", size=1)+
   geom_vline(xintercept = 3, linetype="dashed", color = "orange", size=1)+ 
-  geom_vline(xintercept = 4, linetype="dashed", color = "darkgreen", size=1)+ labs(y = "Selling value")+ labs(x = "Time (months)")+theme_bw(base_size = 18)
[…]

### 2021-03-24 Project_script_Stochastic.R

@@ -20,9 +20,9 @@ CIG_effect<-data.frame(matrix(ncol = 0,nrow=4))
 colnames(buffer) <- c("time", "S","I","R","D")
 pop_tot<-60000000
 delta_inf<-0
-k<-c(1,1,1)
+#k<-c(1,1,1)
 #k<-c(0.9,0.9,0.9)
-#k<-c(1.5,1.5,1.5)
+k<-c(1.5,1.5,1.5)
 #k<-c(0.1,0.1,0.1)
 #rate_infection_threshold<-0.00000007
 rate_infection_threshold<-0.000007
@@ -196,7 +196,7 @@ strong_lockdown_weeks
 lockdown_weeks
 buffer$D[370]
 print("Costo morti kEUR")
-buffer$D[370]*300
+buffer$D[370]*332
 print("Costo ricoveri kEUR")
 buffer$R[370]*28.180
 

### 2021-03-24 Risultati/Phase_transition_diagram.R

@@ -1,5 +1,5 @@
 library(readxl)
 library(ggplot2)
 
-Phase_transition <- read_excel("Risultati/Phase_transition.xlsx")
-ggplot(Phase_transition,aes(x=PM_attitute, y=Deaths),size=2,color = "red") + geom_line(color="red") +   geom_point(color="red") + labs(y = "Death ")+ labs(x = "PM attitute")+ theme_bw(base_size = 18) 
+Phase_transition <- read_excel("Phase_transition.xlsx")
+ggplot(Phase_transition,aes(x=PM_attitute, y=Deaths),size=2,color = "red") + geom_line(color="red") +   geom_point(color="red") + labs(y = "Deaths ")+ labs(x = "PM attitute")+ theme_bw(base_size = 18) 
